### 2015-07-16 presentation.tex
initial commit

\documentclass{beamer}

\usepackage[utf8]{inputenc}
\usepackage{default}
\usepackage{tikz}
\usepackage{color}

\begin{document}
\title{Fast Nearest Neighbour Classification}
\author{Gordon Lesti}
\date{17.07.2015}

\frame{\titlepage}
\frame{\frametitle{Inhaltsverzeichnis}\tableofcontents}

\section{Einleitung}

\subsection{Problem}
\begin{frame}
 \frametitle{Nearest-Neighbor Searching}
 \begin{block}{Gegeben}
   \begin{itemize}
    \item Menge $\mathbb{U}$
    \item Abstandsmaß $d$ auf $\mathbb{U}$, mit $d: \mathbb{U} \times \mathbb{U} \to \mathbb{R}$
    \item Menge $S \subset \mathbb{U}$ der Größe $n$
    \item Anfragepunkt $q \in \mathbb{U}$
  \end{itemize}
 \end{block}
 \begin{block}{Gesucht}
    \begin{itemize}
     \item $a \in S$, mit $d(q, a) \le d(q, x)$ f\"ur alle $x \in S$
    \end{itemize}
 \end{block}
\end{frame}

\subsection{Anwendung}
\begin{frame}
 \frametitle{Anwendung}
 \begin{itemize}
 \item density estimation
 \item pattern recognition
 \item object recognition
 \item data clustering
 \item function approximation
 \item vector quantization
\end{itemize}
\end{frame}

\section{L\"osungen}

\subsection{Vollsuche}
\begin{frame}
 \frametitle{Vollsuche}
 \begin{itemize}
  \item Berechne $d(q, x)$ f\"ur alle $x \in S$
  \item W\"ahle $a \in S$, mit $d(q, a) \le d(q, x)$ f\"ur alle $x \in S$
 \end{itemize}
\end{frame}

% Beispiel1 Datenpunkte
\begin{frame}
 \frametitle{Beispiel}
 \begin{columns}[T]
  \begin{column}{.3\textwidth}
    $\mathbb{U} = \mathbb{R}^2$
    \begin{block}{Datenpunkte}
      $x_1 = (3, 3)$\\
      $x_2 = (-1, 2)$\\
      $x_3 = (-4, -4)$\\
      $x_4 = (0, -1)$\\
      $x_5 = (4, -3)$
    \end{block}
    \begin{block}{Abstandsmaß}
     $d(x, y) = \left\Vert x-y \right\Vert_2$
    \end{block}
  \end{column}
  \begin{column}{.65\textwidth}
     \begin{tikzpicture}[%
      scale=0.6,
      ]
      \clip (-5.0,-5.0) rectangle (5.0,5.0);
      \draw [help lines] (0,0) grid (6,5);
      \draw [help lines] (-6,0) grid (0,5);
      \draw [help lines] (0,-6) grid (6,0);
      \draw [help lines] (-6,-6) grid (0,0);
      \draw [color=black,->] (-5.0,0) -- (5.0,0);
      \draw [color=black,->] (0,-5.0) -- (0,5.0);

      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );

      \node at (3.3,2.7) {$x_1$};
      \node at (-0.7,1.7) {$x_2$};
      \node at (-3.7,-4.3) {$x_3$};
      \node at (0.3,-1.3) {$x_4$};
      \node at (4.3,-3.3) {$x_5$};
      \end{tikzpicture}
  \end{column}
 \end{columns}
\end{frame}

% Beispiel1 Anfragepunkt
\begin{frame}
 \frametitle{Beispiel}
 \begin{columns}[T]
  \begin{column}{.3\textwidth}
    $\mathbb{U} = \mathbb{R}^2$
    \begin{block}{Datenpunkte}
      $x_1 = (3, 3)$\\
      $x_2 = (-1, 2)$\\
      $x_3 = (-4, -4)$\\
      $x_4 = (0, -1)$\\
      $x_5 = (4, -3)$
    \end{block}
    \begin{block}{Abstandsmaß}
     $d(x, y) = \left\Vert x-y \right\Vert_2$
    \end{block}
    \begin{block}{Anfragepunkt}
      $q = (2, 1)$
    \end{block}
  \end{column}
  \begin{column}{.65\textwidth}
     \begin{tikzpicture}[%
      scale=0.6,
      ]
      \clip (-5.0,-5.0) rectangle (5.0,5.0);
      \draw [help lines] (0,0) grid (6,5);
      \draw [help lines] (-6,0) grid (0,5);
      \draw [help lines] (0,-6) grid (6,0);
      \draw [help lines] (-6,-6) grid (0,0);
      \draw [color=black,->] (-5.0,0) -- (5.0,0);
      \draw [color=black,->] (0,-5.0) -- (0,5.0);

      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );

      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );

      \node at (3.3,2.7) {$x_1$};
      \node at (-0.7,1.7) {$x_2$};
      \node at (-3.7,-4.3) {$x_3$};
      \node at (0.3,-1.3) {$x_4$};
      \node at (4.3,-3.3) {$x_5$};

      \node at (2.3,0.7) {$q$};
      \end{tikzpicture}
  \end{column}
 \end{columns}
\end{frame}

% Beispiel1 Abstand x1
\begin{frame}
 \frametitle{Beispiel}
 \begin{columns}[T]
  \begin{column}{.3\textwidth}
    \begin{block}{Ergebnis}
      $d(q, x_1) \approx 2.236$
    \end{block}
  \end{column}
  \begin{column}{.65\textwidth}
     \begin{tikzpicture}[%
      scale=0.6,
      ]
      \clip (-5.0,-5.0) rectangle (5.0,5.0);
      \draw [help lines] (0,0) grid (6,5);
      \draw [help lines] (-6,0) grid (0,5);
      \draw [help lines] (0,-6) grid (6,0);
      \draw [help lines] (-6,-6) grid (0,0);
      \draw [color=black,->] (-5.0,0) -- (5.0,0);
      \draw [color=black,->] (0,-5.0) -- (0,5.0);

      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (3,3);

      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );

      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );

      \node at (3.3,2.7) {$x_1$};
      \node at (-0.7,1.7) {$x_2$};
      \node at (-3.7,-4.3) {$x_3$};
      \node at (0.3,-1.3) {$x_4$};
      \node at (4.3,-3.3) {$x_5$};

      \node at (2.3,0.7) {$q$};
      \end{tikzpicture}
  \end{column}
 \end{columns}
\end{frame}

% Beispiel1 Abstand x2
\begin{frame}
 \frametitle{Beispiel}
 \begin{columns}[T]
  \begin{column}{.3\textwidth}
    \begin{block}{Ergebnis}
      $d(q, x_1) \approx 2.236$\\
      $d(q, x_2) \approx 3.162$
    \end{block}
  \end{column}
  \begin{column}{.65\textwidth}
     \begin{tikzpicture}[%
      scale=0.6,
      ]
      \clip (-5.0,-5.0) rectangle (5.0,5.0);
      \draw [help lines] (0,0) grid (6,5);
      \draw [help lines] (-6,0) grid (0,5);
      \draw [help lines] (0,-6) grid (6,0);
      \draw [help lines] (-6,-6) grid (0,0);
      \draw [color=black,->] (-5.0,0) -- (5.0,0);
      \draw [color=black,->] (0,-5.0) -- (0,5.0);

      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (3,3);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-1,2);

      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );

      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );

      \node at (3.3,2.7) {$x_1$};
      \node at (-0.7,1.7) {$x_2$};
      \node at (-3.7,-4.3) {$x_3$};
      \node at (0.3,-1.3) {$x_4$};
      \node at (4.3,-3.3) {$x_5$};

      \node at (2.3,0.7) {$q$};
      \end{tikzpicture}
  \end{column}
 \end{columns}
\end{frame}

% Beispiel1 Abstand x3
\begin{frame}
 \frametitle{Beispiel}
 \begin{columns}[T]
  \begin{column}{.3\textwidth}
    \begin{block}{Ergebnis}
      $d(q, x_1) \approx 2.236$\\
      $d(q, x_2) \approx 3.162$\\
      $d(q, x_3) \approx 7.810$
    \end{block}
  \end{column}
  \begin{column}{.65\textwidth}
     \begin{tikzpicture}[%
      scale=0.6,
      ]
      \clip (-5.0,-5.0) rectangle (5.0,5.0);
      \draw [help lines] (0,0) grid (6,5);
      \draw [help lines] (-6,0) grid (0,5);
      \draw [help lines] (0,-6) grid (6,0);
      \draw [help lines] (-6,-6) grid (0,0);
      \draw [color=black,->] (-5.0,0) -- (5.0,0);
      \draw [color=black,->] (0,-5.0) -- (0,5.0);

      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (3,3);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-1,2);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-4,-4);

      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );

      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );

      \node at (3.3,2.7) {$x_1$};
      \node at (-0.7,1.7) {$x_2$};
      \node at (-3.7,-4.3) {$x_3$};
      \node at (0.3,-1.3) {$x_4$};
      \node at (4.3,-3.3) {$x_5$};

      \node at (2.3,0.7) {$q$};
      \end{tikzpicture}
  \end{column}
 \end{columns}
\end{frame}

% Beispiel1 Abstand x4
\begin{frame}
 \frametitle{Beispiel}
 \begin{columns}[T]
  \begin{column}{.3\textwidth}
    \begin{block}{Ergebnis}
      $d(q, x_1) \approx 2.236$\\
      $d(q, x_2) \approx 3.162$\\
      $d(q, x_3) \approx 7.810$\\
      $d(q, x_4) \approx 2.828$
    \end{block}
  \end{column}
  \begin{column}{.65\textwidth}
     \begin{tikzpicture}[%
      scale=0.6,
      ]
      \clip (-5.0,-5.0) rectangle (5.0,5.0);
      \draw [help lines] (0,0) grid (6,5);
      \draw [help lines] (-6,0) grid (0,5);
      \draw [help lines] (0,-6) grid (6,0);
      \draw [help lines] (-6,-6) grid (0,0);
      \draw [color=black,->] (-5.0,0) -- (5.0,0);
      \draw [color=black,->] (0,-5.0) -- (0,5.0);

      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (3,3);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-1,2);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-4,-4);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (0,-1);

      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );

      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );

      \node at (3.3,2.7) {$x_1$};
      \node at (-0.7,1.7) {$x_2$};
      \node at (-3.7,-4.3) {$x_3$};
      \node at (0.3,-1.3) {$x_4$};
      \node at (4.3,-3.3) {$x_5$};

      \node at (2.3,0.7) {$q$};
      \end{tikzpicture}
  \end{column}
 \end{columns}
\end{frame}

% Beispiel1 Abstand x5
\begin{frame}
 \frametitle{Beispiel}
 \begin{columns}[T]
  \begin{column}{.3\textwidth}
    \begin{block}{Ergebnis}
      $d(q, x_1) \approx 2.236$\\
      $d(q, x_2) \approx 3.162$\\
      $d(q, x_3) \approx 7.810$\\
      $d(q, x_4) \approx 2.828$\\
      $d(q, x_5) \approx 4.472$
    \end{block}
  \end{column}
  \begin{column}{.65\textwidth}
     \begin{tikzpicture}[%
      scale=0.6,
      ]
      \clip (-5.0,-5.0) rectangle (5.0,5.0);
      \draw [help lines] (0,0) grid (6,5);
      \draw [help lines] (-6,0) grid (0,5);
      \draw [help lines] (0,-6) grid (6,0);
      \draw [help lines] (-6,-6) grid (0,0);
      \draw [color=black,->] (-5.0,0) -- (5.0,0);
      \draw [color=black,->] (0,-5.0) -- (0,5.0);

      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (3,3);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-1,2);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-4,-4);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (0,-1);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (4,-3);

      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );

      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );

      \node at (3.3,2.7) {$x_1$};
      \node at (-0.7,1.7) {$x_2$};
      \node at (-3.7,-4.3) {$x_3$};
      \node at (0.3,-1.3) {$x_4$};
      \node at (4.3,-3.3) {$x_5$};

      \node at (2.3,0.7) {$q$};
      \end{tikzpicture}
  \end{column}
 \end{columns}
\end{frame}

% Beispiel1 Ergebnis
\begin{frame}
 \frametitle{Beispiel}
 \begin{columns}[T]
  \begin{column}{.3\textwidth}
    \begin{block}{Ergebnis}
      \textcolor{green}{$d(q, x_1) \approx 2.236$}\\
      $d(q, x_2) \approx 3.162$\\
      $d(q, x_3) \approx 7.810$\\
      $d(q, x_4) \approx 2.828$\\
      $d(q, x_5) \approx 4.472$
    \end{block}
  \end{column}
  \begin{column}{.65\textwidth}
     \begin{tikzpicture}[%
      scale=0.6,
      ]
      \clip (-5.0,-5.0) rectangle (5.0,5.0);
      \draw [help lines] (0,0) grid (6,5);
      \draw [help lines] (-6,0) grid (0,5);
      \draw [help lines] (0,-6) grid (6,0);
      \draw [help lines] (-6,-6) grid (0,0);
      \draw [color=black,->] (-5.0,0) -- (5.0,0);
      \draw [color=black,->] (0,-5.0) -- (0,5.0);

      \draw[color=green, line width=0.5pt, solid] (2,1) -- (3,3);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-1,2);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-4,-4);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (0,-1);
      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (4,-3);

      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );

      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );

      \node at (3.3,2.7) {$x_1$};
      \node at (-0.7,1.7) {$x_2$};
      \node at (-3.7,-4.3) {$x_3$};
      \node at (0.3,-1.3) {$x_4$};
      \node at (4.3,-3.3) {$x_5$};

      \node at (2.3,0.7) {$q$};
      \end{tikzpicture}
  \end{column}
 \end{columns}
\end{frame}

% Vor- und Nachteile
\begin{frame}
 \frametitle{Vor- und Nachteile}
 \begin{block}{Vorteile}
  \begin{itemize}
   \item Einfache Implementierung
  \end{itemize}
 \end{block}
 \begin{block}{Nachteile}
  \begin{itemize}
   \item Hohe Laufzeiten gerade bei großen Datenmengen und h\"oherdimensionalen R\"aumen
   \item Funktioniert auch in Nicht-Metrischen R\"aumen
  \end{itemize}
 \end{block}
\end{frame}

\subsection{Dreiecksungleichung}
\begin{frame}
 \frametitle{Metrik}
  Sei $X$ ein Menge. Unter einer \textit{Metrik} auf $X$ versteht man eine Abbildung\\
  $d:X \times X \to \mathbb{R}$, $(x, y) \mapsto d(x, y)$\\
  mit folgenden Eigenschaften:
 \begin{itemize}
  \item $d(x, y) = 0$ genau dann, wenn $x=y$.
  \item Symmetrie: F\"ur alle $x, y \in X$ gilt $d(x, y) = d(y, x)$.
  \item Dreiecksungleichung: F\"ur alle $x, y, z \in X$ gilt $d(x, z) \le d(x, y) + d(y,z)$
 \end{itemize}
 \flushright{\tiny{[Forster, 2006]}}
\end{frame}

\begin{frame}
 \frametitle{Dreiecksungleichung}
 \textbf{Lemma} F\"ur beliebige $q, s, p \in \mathbb{U}$, $r \in \mathbb{R}$ und $P \subset \mathbb{U}$ gilt:
 \begin{itemize}
  \item $|d(p, q) - d(p, s)| \le d(q, s) \le d(p, q) + d(p, s)$
  \item $d(q, s) \ge d_P(q, s) := \max_{p \in P}|d(p, q) - d(p, s)|$
  \item $d(p, s) > d(p, q) + r \vee d(p, s) < d(p, q) -r \Rightarrow d(q, s) > r$
  \item $d(p, s) \ge 2 \cot d(p, q) \Rightarrow d(q, s) \ge d(q, p)$
 \end{itemize}
 \flushright{\tiny{[Clarkson, 2005]}}
\end{frame}

\subsection{Orchard’s Algorithm}
\begin{frame}
 \frametitle{Orchard’s Algorithm}
 \begin{itemize}
  \item Erstelle Liste f\"ur alle Punkt $p \in S$ mit allen Punkten $x \in S$, aufsteigenden nach ihrer Distanz
  \item W\"ahle zufälligen Punkt $c \in S$ als initialen Kandidaten
  \item Berechne $d(c, q)$
  \item Gehe Liste von $c$ entlange
  \item Wenn aktueller Punkt näher an $q$ als $c$, nimm aktuellen Punkt für $c$
  \item Abbruch, wenn
    \begin{itemize}
      \item die List komplett abgelaufen ist, oder
      \item $d(c, s) > 2 \cdot d(c, p)$ f\"ur beliebiges Element aus der Liste
    \end{itemize}
 \end{itemize}
\end{frame}

% Beispiel2 Datenpunkte
\begin{frame}
 \frametitle{Beispiel}
 \begin{columns}[T]
  \begin{column}{.3\textwidth}
    \begin{block}{Datenpunkte}
      $x_1 = (3, 3)$\\
      $x_2 = (-1, 2)$\\
      $x_3 = (-4, -4)$\\
      $x_4 = (0, -1)$\\
      $x_5 = (4, -3)$
    \end{block}
  \end{column}
  \begin{column}{.65\textwidth}
     \begin{tikzpicture}[%
      scale=0.6,
      ]
      \clip (-5.0,-5.0) rectangle (5.0,5.0);
      \draw [help lines] (0,0) grid (6,5);
      \draw [help lines] (-6,0) grid (0,5);
      \draw [help lines] (0,-6) grid (6,0);
      \draw [help lines] (-6,-6) grid (0,0);
      \draw [color=black,->] (-5.0,0) -- (5.0,0);
      \draw [color=black,->] (0,-5.0) -- (0,5.0);

      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (-1,2);
      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (-4,-4);
      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (0,-1);
      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (4,-3);
      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (-4,-4);
      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (0,-1);
      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (4,-3);
      \draw[color=gray, line width=0.5pt, dashed] (-4,-4) -- (0,-1);
      \draw[color=gray, line width=0.5pt, dashed] (-4,-4) -- (4,-3);
      \draw[color=gray, line width=0.5pt, dashed] (0,-1) -- (4,-3);

      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );

      \node at (3.3,2.7) {$x_1$};
      \node at (-0.7,1.7) {$x_2$};
      \node at (-3.7,-4.3) {$x_3$};
      \node at (0.3,-1.3) {$x_4$};
      \node at (4.3,-3.3) {$x_5$};
      \end{tikzpicture}
  \end{column}
 \end{columns}
\end{frame}

% Beispiel2 Anfragepunkt
\begin{frame}
 \frametitle{Beispiel}
 \begin{columns}[T]
  \begin{column}{.3\textwidth}
    \begin{block}{Datenpunkte}
      $x_1 = (3, 3)$\\
      $x_2 = (-1, 2)$\\
      $x_3 = (-4, -4)$\\
      $x_4 = (0, -1)$\\
      $x_5 = (4, -3)$
    \end{block}
    \begin{block}{Anfragepunkt}
      $q = (2, 1)$
    \end{block}
  \end{column}
  \begin{column}{.65\textwidth}
     \begin{tikzpicture}[%
      scale=0.6,
      ]
      \clip (-5.0,-5.0) rectangle (5.0,5.0);
      \draw [help lines] (0,0) grid (6,5);
      \draw [help lines] (-6,0) grid (0,5);
      \draw [help lines] (0,-6) grid (6,0);
      \draw [help lines] (-6,-6) grid (0,0);
      \draw [color=black,->] (-5.0,0) -- (5.0,0);
      \draw [color=black,->] (0,-5.0) -- (0,5.0);

      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (-1,2);
      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (-4,-4);
      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (0,-1);
      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (4,-3);
      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (-4,-4);
      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (0,-1);
      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (4,-3);
      \draw[color=gray, line width=0.5pt, dashed] (-4,-4) -- (0,-1);
      \draw[color=gray, line width=0.5pt, dashed] (-4,-4) -- (4,-3);
      \draw[color=gray, line width=0.5pt, dashed] (0,-1) -- (4,-3);

      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );

      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );

      \node at (3.3,2.7) {$x_1$};
      \node at (-0.7,1.7) {$x_2$};
      \node at (-3.7,-4.3) {$x_3$};
      \node at (0.3,-1.3) {$x_4$};
      \node at (4.3,-3.3) {$x_5$};

      \node at (2.3,0.7) {$q$};
      \end{tikzpicture}
  \end{column}
 \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Beispiel}
  \begin{block}{Abst\"ande}
  \begin{center}
    \begin{tabular}{r|cccccc}
      & $x_1$ & $x_2$ & $x_3$ & $x_4$ & $x_5$ & $q$\\
      \hline
      $x_1$ & 0 & $\approx 4.123$ & $\approx 9.899$ & $5$ & $\approx 6.083$ & \textcolor{red}{?}\\
      $x_2$ & $\approx 4.123$ & 0 & $\approx 6.708$ & $\approx 3.162$ & $\approx 7.071$ & \textcolor{red}{?}\\
      $x_3$ & $\approx 9.899$ & $\approx 6.708$ & 0 & $5$ & $\approx 8.062$ & \textcolor{red}{?}\\
      $x_4$ & $5$ & $\approx 3.162$ & $5$ & 0 & $\approx 4.472$ & \textcolor{red}{?}\\
      $x_5$ & $\approx 6.083$ & $\approx 7.071$ & $\approx 8.062$ & $\approx 4.472$ & 0 & \textcolor{red}{?}\\
      $q$ & \textcolor{red}{?} & \textcolor{red}{?} & \textcolor{red}{?} & \textcolor{red}{?} & \textcolor{red}{?} & 0 \\
    \end{tabular}
  \end{center}
  \end{block}
\end{frame}

\begin{frame}
 \frametitle{Beispiel}
 \begin{columns}[T]
  \begin{column}{.3\textwidth}
    W\"ahle $x_2$ zuf\"allig aus und berechne $d(q, x_2) \approx 3.162$
  \end{column}
  \begin{column}{.65\textwidth}
     \begin{tikzpicture}[%
      scale=0.6,
      ]
      \clip (-5.0,-5.0) rectangle (5.0,5.0);
      \draw [help lines] (0,0) grid (6,5);
      \draw [help lines] (-6,0) grid (0,5);
      \draw [help lines] (0,-6) grid (6,0);
      \draw [help lines] (-6,-6) grid (0,0);
      \draw [color=black,->] (-5.0,0) -- (5.0,0);
      \draw [color=black,->] (0,-5.0) -- (0,5.0);

      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (-1,2);
      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (-4,-4);
      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (0,-1);
      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (4,-3);

      \draw[color=green, line width=0.5pt, dashed] (-1,2) -- (2,1);

      \filldraw [color=gray] (3,3) circle (2.5pt );
      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
      \filldraw [color=gray] (-4,-4) circle (2.5pt );
      \filldraw [color=gray] (0,-1) circle (2.5pt );
      \filldraw [color=gray] (4,-3) circle (2.5pt );

      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );

      \node at (3.3,2.7) {$x_1$};
      \node at (-0.7,1.7) {$x_2$};
      \node at (-3.7,-4.3) {$x_3$};
      \node at (0.3,-1.3) {$x_4$};
      \node at (4.3,-3.3) {$x_5$};

      \node at (2.3,0.7) {$q$};
      \end{tikzpicture}
  \end{column}
 \end{columns}
\end{frame}

\section{Quellen}
\begin{frame}
 \frametitle{Quellen}
 \begin{itemize}
  \item Otto Forster, 2006, \textit{Analysis 2}, Friedr. Vieweg \& Sohn Verlag
  \item Kenneth L. Clarkson, 2005, \textit{Nearest-Neighbor Searching and Metric Space Dimensions}, http://kenclarkson.org/nn\_survey/p.pdf
  \end{itemize}
\end{frame}

\end{document}

### 2015-07-16 presentation.tex
tmp commit

@@
 % Beispiel1 Datenpunkte
-\begin{frame}
- \frametitle{Beispiel}
+\begin{frame}{Vollsuche}{Beispiel}
  \begin{columns}[T]
-  \begin{column}{.3\textwidth}
+  \begin{column}{.35\textwidth}
     $\mathbb{U} = \mathbb{R}^2$
@@
     \end{block}
-    \begin{block}{Abstandsmaß}
-     $d(x, y) = \left\Vert x-y \right\Vert_2$
-    \end{block}
   \end{column}
-  \begin{column}{.65\textwidth}
+  \begin{column}{.6\textwidth}
      \begin{tikzpicture}[%
@@
 % Beispiel1 Anfragepunkt
-\begin{frame}
- \frametitle{Beispiel}
+\begin{frame}{Vollsuche}{Beispiel}
  \begin{columns}[T]
-  \begin{column}{.3\textwidth}
+  \begin{column}{.35\textwidth}
     $\mathbb{U} = \mathbb{R}^2$
@@
     \end{block}
-    \begin{block}{Abstandsmaß}
-     $d(x, y) = \left\Vert x-y \right\Vert_2$
-    \end{block}
     \begin{block}{Anfragepunkt}
@@
   \end{column}
-  \begin{column}{.65\textwidth}
+  \begin{column}{.6\textwidth}
      \begin{tikzpicture}[%
@@
 % Beispiel1 Abstand x1
-\begin{frame}
- \frametitle{Beispiel}
+\begin{frame}{Vollsuche}{Beispiel}
  \begin{columns}[T]
-  \begin{column}{.3\textwidth}
+  \begin{column}{.35\textwidth}
     \begin{block}{Ergebnis}
@@
 % Beispiel1 Abstand x2
-\begin{frame}
- \frametitle{Beispiel}
+\begin{frame}{Vollsuche}{Beispiel}
  \begin{columns}[T]
-  \begin{column}{.3\textwidth}
+  \begin{column}{.35\textwidth}
     \begin{block}{Ergebnis}
@@
 % Beispiel1 Abstand x3
-\begin{frame}
- \frametitle{Beispiel}
+\begin{frame}{Vollsuche}{Beispiel}
  \begin{columns}[T]
-  \begin{column}{.3\textwidth}
+  \begin{column}{.35\textwidth}
     \begin{block}{Ergebnis}
@@
 % Beispiel1 Abstand x4
-\begin{frame}
- \frametitle{Beispiel}
+\begin{frame}{Vollsuche}{Beispiel}
  \begin{columns}[T]
-  \begin{column}{.3\textwidth}
+  \begin{column}{.35\textwidth}
     \begin{block}{Ergebnis}
@@
 % Beispiel1 Abstand x5
-\begin{frame}
- \frametitle{Beispiel}
+\begin{frame}{Vollsuche}{Beispiel}
  \begin{columns}[T]
-  \begin{column}{.3\textwidth}
+  \begin{column}{.35\textwidth}
     \begin{block}{Ergebnis}
@@
 % Beispiel1 Ergebnis
-\begin{frame}
- \frametitle{Beispiel}
+\begin{frame}{Vollsuche}{Beispiel}
  \begin{columns}[T]
-  \begin{column}{.3\textwidth}
+  \begin{column}{.35\textwidth}
     \begin{block}{Ergebnis}
@@
 % Vor- und Nachteile
-\begin{frame}
- \frametitle{Vor- und Nachteile}
+\begin{frame}{Vollsuche}{Vor- und Nachteile}
  \begin{block}{Vorteile}
@@
    \item Einfache Implementierung
+   \item Funktioniert auch in Nicht-Metrischen R\"aumen
   \end{itemize}
@@
    \item Hohe Laufzeiten gerade bei großen Datenmengen und h\"oherdimensionalen R\"aumen
-   \item Funktioniert auch in Nicht-Metrischen R\"aumen
   \end{itemize}
@@
 
-\subsection{Dreiecksungleichung}
-\begin{frame}
- \frametitle{Metrik}
+\begin{frame}{Metrik}
   Sei $X$ ein Menge. Unter einer \textit{Metrik} auf $X$ versteht man eine Abbildung\\
@@
   mit folgenden Eigenschaften:
- \begin{itemize}
+ \begin{enumerate}
   \item $d(x, y) = 0$ genau dann, wenn $x=y$.
@@
   \item Dreiecksungleichung: F\"ur alle $x, y, z \in X$ gilt $d(x, z) \le d(x, y) + d(y,z)$
- \end{itemize}
+ \end{enumerate}
  \flushright{\tiny{[Forster, 2006]}}
@@
 
-\begin{frame}
- \frametitle{Dreiecksungleichung}
+\begin{frame}{Dreiecksungleichung}
  \textbf{Lemma} F\"ur beliebige $q, s, p \in \mathbb{U}$, $r \in \mathbb{R}$ und $P \subset \mathbb{U}$ gilt:
- \begin{itemize}
+ \begin{enumerate}
   \item $|d(p, q) - d(p, s)| \le d(q, s) \le d(p, q) + d(p, s)$
@@
   \item $d(p, s) > d(p, q) + r \vee d(p, s) < d(p, q) -r \Rightarrow d(q, s) > r$
-  \item $d(p, s) \ge 2 \cot d(p, q) \Rightarrow d(q, s) \ge d(q, p)$
- \end{itemize}
+  \item $d(p, s) \ge 2 \cdot d(p, q) \Rightarrow d(q, s) \ge d(q, p)$
+ \end{enumerate}
  \flushright{\tiny{[Clarkson, 2005]}}
@@
 \subsection{Orchard’s Algorithm}
-\begin{frame}
- \frametitle{Orchard’s Algorithm}
+\begin{frame}{Orchard’s Algorithm}
  \begin{itemize}
@@
     \begin{itemize}
-      \item die List komplett abgelaufen ist, oder
-      \item $d(c, s) > 2 \cdot d(c, p)$ f\"ur beliebiges Element aus der Liste
+      \item die Liste komplett abgelaufen ist, oder
+      \item $d(c, s) > 2 \cdot d(c, q)$ f\"ur aktuelles Element aus der Liste
     \end{itemize}
@@
 
-% Beispiel2 Datenpunkte
-\begin{frame}
- \frametitle{Beispiel}
+%Beispiel2
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
  \begin{columns}[T]
-  \begin{column}{.3\textwidth}
+  \begin{column}{.35\textwidth}
+    $\mathbb{U} = \mathbb{R}^2$
     \begin{block}{Datenpunkte}
@@
     \end{block}
+    \begin{block}{Anfragepunkt}
+      $q = (2, 1)$
+    \end{block}
   \end{column}
-  \begin{column}{.65\textwidth}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
+      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
+      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
+      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
+      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );
+
+      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Listen
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{block}{Listen}
+    $L(x_1) = \{x_2, x_4, x_5, x_3\}$\\
+    $L(x_2) = \{x_4, x_1, x_3, x_5\}$\\
+    $L(x_3) = \{x_4, x_2, x_5, x_1\}$\\
+    $L(x_4) = \{x_2, x_5, x_1, x_3\}$\\
+    $L(x_5) = \{x_4, x_1, x_2, x_3\}$\\
+    \end{block}
+  \end{column}
+  \begin{column}{.6\textwidth}
      \begin{tikzpicture}[%
@@
 
-% Beispiel2 Anfragepunkt
-\begin{frame}
- \frametitle{Beispiel}
+%Beispiel2 Wähle c=x_3 und s=x_4
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
  \begin{columns}[T]
-  \begin{column}{.3\textwidth}
-    \begin{block}{Datenpunkte}
-      $x_1 = (3, 3)$\\
-      $x_2 = (-1, 2)$\\
-      $x_3 = (-4, -4)$\\
-      $x_4 = (0, -1)$\\
-      $x_5 = (4, -3)$
-    \end{block}
-    \begin{block}{Anfragepunkt}
-      $q = (2, 1)$
-    \end{block}
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:=x_3$ und $s:= x_4$
+    \end{itemize}
   \end{column}
-  \begin{column}{.65\textwidth}
+  \begin{column}{.60\textwidth}
      \begin{tikzpicture}[%
@@
 
-      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (-1,2);
-      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (-4,-4);
-      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (0,-1);
-      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (4,-3);
-      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (-4,-4);
-      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (0,-1);
-      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (4,-3);
-      \draw[color=gray, line width=0.5pt, dashed] (-4,-4) -- (0,-1);
-      \draw[color=gray, line width=0.5pt, dashed] (-4,-4) -- (4,-3);
-      \draw[color=gray, line width=0.5pt, dashed] (0,-1) -- (4,-3);
+      \draw [color=gray, line width=0.5pt, solid] (-4,-4) circle (5);
+      \draw [color=gray, line width=0.5pt, solid] (-4,-4) circle (6.708);
+      \draw [color=gray, line width=0.5pt, solid] (-4,-4) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (-4,-4) circle (9.899);
+      \draw [color=yellow, line width=0.5pt, solid] (-4,-4) circle (15.62);
 
-      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
-      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
-      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
-      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
-      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=yellow] (-4,-4) circle (2.1pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=white] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
 
-      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );
+      \filldraw [color=red] (2,1) circle (2.5pt );
 
@@
 
-\begin{frame}
-  \frametitle{Beispiel}
-  \begin{block}{Abst\"ande}
-  \begin{center}
-    \begin{tabular}{r|cccccc}
-      & $x_1$ & $x_2$ & $x_3$ & $x_4$ & $x_5$ & $q$\\
-      \hline
-      $x_1$ & 0 & $\approx 4.123$ & $\approx 9.899$ & $5$ & $\approx 6.083$ & \textcolor{red}{?}\\
-      $x_2$ & $\approx 4.123$ & 0 & $\approx 6.708$ & $\approx 3.162$ & $\approx 7.071$ & \textcolor{red}{?}\\
-      $x_3$ & $\approx 9.899$ & $\approx 6.708$ & 0 & $5$ & $\approx 8.062$ & \textcolor{red}{?}\\
-      $x_4$ & $5$ & $\approx 3.162$ & $5$ & 0 & $\approx 4.472$ & \textcolor{red}{?}\\
-      $x_5$ & $\approx 6.083$ & $\approx 7.071$ & $\approx 8.062$ & $\approx 4.472$ & 0 & \textcolor{red}{?}\\
-      $q$ & \textcolor{red}{?} & \textcolor{red}{?} & \textcolor{red}{?} & \textcolor{red}{?} & \textcolor{red}{?} & 0 \\
-    \end{tabular}
-  \end{center}
-  \end{block}
-\end{frame}
-
-\begin{frame}
- \frametitle{Beispiel}
+%Beispiel2 Wähle c=x_3 und s=x_4
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
  \begin{columns}[T]
-  \begin{column}{.3\textwidth}
-    W\"ahle $x_2$ zuf\"allig aus und berechne $d(q, x_2) \approx 3.162$
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:=x_3$ und $s:= x_4$
+     \item Da $7.810 \approx d(c, q) > d(s, q) \approx 2.828$, wird $x_4$ neues $c$
+    \end{itemize}
   \end{column}
-  \begin{column}{.65\textwidth}
+  \begin{column}{.60\textwidth}
      \begin{tikzpicture}[%
@@
 
+      \draw [color=gray, line width=0.5pt, solid] (-4,-4) circle (5);
+      \draw [color=gray, line width=0.5pt, solid] (-4,-4) circle (6.708);
+      \draw [color=gray, line width=0.5pt, solid] (-4,-4) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (-4,-4) circle (9.899);
+      \draw [color=yellow, line width=0.5pt, solid] (-4,-4) circle (15.62);
+      \draw [color=yellow, line width=0.5pt, solid] (-4,-4) circle (15.62);
+
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-4,-4);
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (0,-1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=yellow] (-4,-4) circle (2.1pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=white] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_4 und s=x_2
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:=x_4$ und $s:= x_2$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (3.162);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (4.472);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (5);
+      \draw [color=yellow, line width=0.5pt, solid] (0,-1) circle (5.656);
+      \draw [color=yellow, line width=0.5pt, solid] (0,-1) circle (5.656);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=white] (-1,2) circle (2.1pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=yellow] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_4 und s=x_2
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:=x_4$ und $s:= x_2$
+     \item Da $2.828 \approx d(c, q) < d(s, q) \approx 3.162$, kein neues $c$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (3.162);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (4.472);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (5);
+      \draw [color=yellow, line width=0.5pt, solid] (0,-1) circle (5.656);
+
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-1,2);
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (0,-1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=white] (-1,2) circle (2.1pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=yellow] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_4 und s=x_2
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:=x_4$ und $s:= x_2$
+     \item Da $2.828 \approx d(c, q) < d(s, q) \approx 3.162$, kein neues $c$
+     \item Da $3.162 \approx d(c, s) < 2 \cdot d(c, q) \approx 5.656$, $x_4$ kein Abbruch
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (3.162);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (4.472);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (5);
+      \draw [color=yellow, line width=0.5pt, solid] (0,-1) circle (5.656);
+
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-1,2);
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (0,-1);
+      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (0,-1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=white] (-1,2) circle (2.1pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=yellow] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_4 und s=x_5
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:= x_5$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (3.162);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (4.472);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (5);
+      \draw [color=yellow, line width=0.5pt, solid] (0,-1) circle (5.656);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=yellow] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=white] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_4 und s=x_5
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:= x_5$
+     \item Da $2.828 \approx d(c, q) < d(s, q) \approx 4.472$, kein neues $c$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (3.162);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (4.472);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (5);
+      \draw [color=yellow, line width=0.5pt, solid] (0,-1) circle (5.656);
+
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (4,-3);
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (0,-1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=yellow] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=white] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_4 und s=x_5
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:= x_5$
+     \item Da $2.828 \approx d(c, q) < d(s, q) \approx 4.472$, kein neues $c$
+     \item Da $4.472 \approx d(c, s) < 2 \cdot d(c, q) \approx 5.656$, $x_4$ kein Abbruch
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (3.162);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (4.472);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (5);
+      \draw [color=yellow, line width=0.5pt, solid] (0,-1) circle (5.656);
+
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (4,-3);
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (0,-1);
+      \draw[color=gray, line width=0.5pt, dashed] (4,-3) -- (0,-1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=yellow] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=white] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_4 und s=x_1
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:= x_1$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (3.162);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (4.472);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (5);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=white] (3,3) circle (2.1pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=yellow] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_4 und s=x_1
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:= x_1$
+     \item Da $2.828 \approx d(c, q) > d(s, q) \approx 2.236$, wird $x_1$ neues $c$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (3.162);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (4.472);
+      \draw [color=gray, line width=0.5pt, solid] (0,-1) circle (5);
+
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (3,3);
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (0,-1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=white] (3,3) circle (2.1pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=yellow] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_1 und s=x_2
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:= x_1$ und $s:=x_2$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (4.123);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (5);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (9.899);
+      \draw [color=yellow, line width=0.5pt, solid] (3,3) circle (4.472);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=yellow] (3,3) circle (2.1pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=white] (-1,2) circle (2.1pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_1 und s=x_2
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:= x_1$ und $s:=x_2$
+     \item Da $2.236 \approx d(c, q) < d(s, q) \approx 3.162$, kein neues $c$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (4.123);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (5);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (9.899);
+      \draw [color=yellow, line width=0.5pt, solid] (3,3) circle (4.472);
+
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (3,3);
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-1,2);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=yellow] (3,3) circle (2.1pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=white] (-1,2) circle (2.1pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_1 und s=x_2
+\begin{frame}{Orchard’s Algorithm}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:= x_1$ und $s:=x_2$
+     \item Da $2.236 \approx d(c, q) < d(s, q) \approx 3.162$, kein neues $c$
+     \item Da $4.123 \approx d(c, s) < 2 \cdot d(c, q) \approx 4.472$, $x_4$ kein Abbruch
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (4.123);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (5);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (9.899);
+      \draw [color=yellow, line width=0.5pt, solid] (3,3) circle (4.472);
+
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (3,3);
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (-1,2);
       \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (-1,2);
-      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (-4,-4);
-      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (0,-1);
-      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (4,-3);
 
-      \draw[color=green, line width=0.5pt, dashed] (-1,2) -- (2,1);
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=yellow] (3,3) circle (2.1pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=white] (-1,2) circle (2.1pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
 
-      \filldraw [color=gray] (3,3) circle (2.5pt );
-      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
-      \filldraw [color=gray] (-4,-4) circle (2.5pt );
-      \filldraw [color=gray] (0,-1) circle (2.5pt );
-      \filldraw [color=gray] (4,-3) circle (2.5pt );
-
-      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );
+      \filldraw [color=red] (2,1) circle (2.5pt );
 

### 2015-07-16 presentation.tex
add Annulus Verfahren

@@
     \item Menge $\mathbb{U}$
+    \pause
     \item Abstandsmaß $d$ auf $\mathbb{U}$, mit $d: \mathbb{U} \times \mathbb{U} \to \mathbb{R}$
+    \pause
     \item Menge $S \subset \mathbb{U}$ der Größe $n$
+    \pause
     \item Anfragepunkt $q \in \mathbb{U}$
@@
  \end{block}
+ \pause
  \begin{block}{Gesucht}
@@
   \item Berechne $d(q, x)$ f\"ur alle $x \in S$
+  \pause
   \item W\"ahle $a \in S$, mit $d(q, a) \le d(q, x)$ f\"ur alle $x \in S$
@@
    \item Einfache Implementierung
+   \pause
    \item Funktioniert auch in Nicht-Metrischen R\"aumen
@@
  \end{block}
+ \pause
  \begin{block}{Nachteile}
@@
  \begin{enumerate}
+ \pause
   \item $d(x, y) = 0$ genau dann, wenn $x=y$.
+  \pause
   \item Symmetrie: F\"ur alle $x, y \in X$ gilt $d(x, y) = d(y, x)$.
+  \pause
   \item Dreiecksungleichung: F\"ur alle $x, y, z \in X$ gilt $d(x, z) \le d(x, y) + d(y,z)$
@@
 \begin{frame}{Dreiecksungleichung}
+  \begin{center}
+    \begin{tikzpicture}[%
+    scale=1.0,
+    ]
+    \clip (-4.15325,-0.785024) rectangle (0.889982,2.09932);
+    \filldraw [color={rgb:red,0;green,0;blue,255}] (0.387719,-0.137281) circle (2.5pt );
+    \filldraw [color={rgb:red,0;green,0;blue,255}] (-3.46333,0.27222) circle (2.5pt );
+    \filldraw [color={rgb:red,0;green,0;blue,255}] (-0.413857,1.98864) circle (2.5pt );
+    \draw[color={rgb:red,0;green,0;blue,255}, line width=0.5pt, solid] (-3.46333,0.27222) -- (-0.413857,1.98864);
+    \draw[color={rgb:red,0;green,0;blue,255}, line width=0.5pt, solid] (-3.46333,0.27222) -- (0.387719,-0.137281);
+    \draw[color={rgb:red,0;green,0;blue,255}, line width=0.5pt, solid] (-0.413857,1.98864) -- (0.387719,-0.137281);
+    \node at (0.679006,-0.454707) {s};
+    \node at (-0.131283,1.69735) {p};
+    \node at (-3.18076,-0.163507) {q};
+    \end{tikzpicture}
+  \end{center}
+
  \textbf{Lemma} F\"ur beliebige $q, s, p \in \mathbb{U}$, $r \in \mathbb{R}$ und $P \subset \mathbb{U}$ gilt:
  \begin{enumerate}
-  \item $|d(p, q) - d(p, s)| \le d(q, s) \le d(p, q) + d(p, s)$
-  \item $d(q, s) \ge d_P(q, s) := \max_{p \in P}|d(p, q) - d(p, s)|$
-  \item $d(p, s) > d(p, q) + r \vee d(p, s) < d(p, q) -r \Rightarrow d(q, s) > r$
-  \item $d(p, s) \ge 2 \cdot d(p, q) \Rightarrow d(q, s) \ge d(q, p)$
+ \pause
+  \item \label{ineq:1}$|d(p, q) - d(p, s)| \le d(q, s) \le d(p, q) + d(p, s)$
+  \pause
+  \item \label{ineq:2}$d(q, s) \ge d_P(q, s) := \max_{p \in P}|d(p, q) - d(p, s)|$
+  \pause
+  \item \label{ineq:3}$d(p, s) > d(p, q) + r \vee d(p, s) < d(p, q) -r \Rightarrow d(q, s) > r$
+  \pause
+  \item \label{ineq:4}$d(p, s) \ge 2 \cdot d(p, q) \Rightarrow d(q, s) \ge d(q, p)$
  \end{enumerate}
@@
 
-\subsection{Orchard’s Algorithm}
-\begin{frame}{Orchard’s Algorithm}
- \begin{itemize}
-  \item Erstelle Liste f\"ur alle Punkt $p \in S$ mit allen Punkten $x \in S$, aufsteigenden nach ihrer Distanz
+\subsection{Orchard’s Algorithmus}
+\begin{frame}{Orchard’s Algorithmus}
+ \begin{itemize}
+  \item Erstelle Liste f\"ur alle Punkt $p \in S$ mit allen Punkten $x \in S$, aufsteigend nach ihrer Distanz
+  \pause
   \item W\"ahle zufälligen Punkt $c \in S$ als initialen Kandidaten
+  \pause
   \item Berechne $d(c, q)$
+  \pause
   \item Gehe Liste von $c$ entlange
+  \pause
   \item Wenn aktueller Punkt näher an $q$ als $c$, nimm aktuellen Punkt für $c$
+  \pause
   \item Abbruch, wenn
@@
       \item die Liste komplett abgelaufen ist, oder
-      \item $d(c, s) > 2 \cdot d(c, q)$ f\"ur aktuelles Element aus der Liste
-    \end{itemize}
+      \item $d(c, s) > 2 \cdot d(c, q)$ f\"ur aktuelles Element aus der Liste (Dreiecksungleichung~\ref{ineq:4})
+    \end{itemize}
+   \pause
+   \item Sonst ist $c$ nächster Nachbar
  \end{itemize}
@@
 %Beispiel2
-\begin{frame}{Orchard’s Algorithm}{Beispiel}
+\begin{frame}{Orchard’s Algorithmus}{Beispiel}
  \begin{columns}[T]
@@
 
+%Beispiel2 Abstand
+\begin{frame}{Orchard’s Algorithmus}{Beispiel}
+  \begin{block}{Abst\"ande}
+  \begin{center}
+    \begin{tabular}{r|ccccc}
+      & $x_1$ & $x_2$ & $x_3$ & $x_4$ & $x_5$\\
+      \hline
+      $x_1$ & 0 & $\approx 4.123$ & $\approx 9.899$ & $5$ & $\approx 6.083$\\
+      $x_2$ & $\approx 4.123$ & 0 & $\approx 6.708$ & $\approx 3.162$ & $\approx 7.071$\\
+      $x_3$ & $\approx 9.899$ & $\approx 6.708$ & 0 & $5$ & $\approx 8.062$\\
+      $x_4$ & $5$ & $\approx 3.162$ & $5$ & 0 & $\approx 4.472$\\
+      $x_5$ & $\approx 6.083$ & $\approx 7.071$ & $\approx 8.062$ & $\approx 4.472$ & 0\\
+    \end{tabular}
+  \end{center}
+  \end{block}
+\end{frame}
+
 %Beispiel2 Listen
-\begin{frame}{Orchard’s Algorithm}{Beispiel}
+\begin{frame}{Orchard’s Algorithmus}{Beispiel}
  \begin{columns}[T]
@@
 %Beispiel2 Wähle c=x_3 und s=x_4
-\begin{frame}{Orchard’s Algorithm}{Beispiel}
+\begin{frame}{Orchard’s Algorithmus}{Beispiel}
  \begin{columns}[T]
@@
 %Beispiel2 Wähle c=x_4 und s=x_2
-\begin{frame}{Orchard’s Algorithm}{Beispiel}
+\begin{frame}{Orchard’s Algorithmus}{Beispiel}
  \begin{columns}[T]
@@
      \item Da $2.828 \approx d(c, q) < d(s, q) \approx 3.162$, kein neues $c$
-     \item Da $3.162 \approx d(c, s) < 2 \cdot d(c, q) \approx 5.656$, $x_4$ kein Abbruch
+     \item Da $3.162 \approx d(c, s) < 2 \cdot d(c, q) \approx 5.656$, kein Abbruch
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_4 und s=x_5
-\begin{frame}{Orchard’s Algorithm}{Beispiel}
+\begin{frame}{Orchard’s Algorithmus}{Beispiel}
  \begin{columns}[T]
@@
      \item Da $2.828 \approx d(c, q) < d(s, q) \approx 4.472$, kein neues $c$
-     \item Da $4.472 \approx d(c, s) < 2 \cdot d(c, q) \approx 5.656$, $x_4$ kein Abbruch
+     \item Da $4.472 \approx d(c, s) < 2 \cdot d(c, q) \approx 5.656$, kein Abbruch
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_4 und s=x_1
-\begin{frame}{Orchard’s Algorithm}{Beispiel}
+\begin{frame}{Orchard’s Algorithmus}{Beispiel}
  \begin{columns}[T]
@@
 %Beispiel2 Wähle c=x_1 und s=x_2
-\begin{frame}{Orchard’s Algorithm}{Beispiel}
+\begin{frame}{Orchard’s Algorithmus}{Beispiel}
  \begin{columns}[T]
@@
      \item Da $2.236 \approx d(c, q) < d(s, q) \approx 3.162$, kein neues $c$
-     \item Da $4.123 \approx d(c, s) < 2 \cdot d(c, q) \approx 4.472$, $x_4$ kein Abbruch
+     \item Da $4.123 \approx d(c, s) < 2 \cdot d(c, q) \approx 4.472$, kein Abbruch
     \end{itemize}
@@
 
+%Beispiel2 Wähle c=x_1 und s=x_4
+\begin{frame}{Orchard’s Algorithmus}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:=x_4$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (4.123);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (5);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (9.899);
+      \draw [color=yellow, line width=0.5pt, solid] (3,3) circle (4.472);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=yellow] (3,3) circle (2.1pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=white] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_1 und s=x_4
+\begin{frame}{Orchard’s Algorithmus}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:=x_4$
+     \item Da $2.236 \approx d(c, q) < d(s, q) \approx 2.828$, kein neues $c$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (4.123);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (5);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (9.899);
+      \draw [color=yellow, line width=0.5pt, solid] (3,3) circle (4.472);
+
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (3,3);
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (0,-1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=yellow] (3,3) circle (2.1pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=white] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel2 Wähle c=x_1 und s=x_4
+\begin{frame}{Orchard’s Algorithmus}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:=x_4$
+     \item Da $2.236 \approx d(c, q) < d(s, q) \approx 2.828$, kein neues $c$
+     \item Da $5 \approx d(c, s) > 2 \cdot d(c, q) \approx 4.472$, \textcolor{green}{Abbruch}
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (4.123);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (5);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (3,3) circle (9.899);
+      \draw [color=yellow, line width=0.5pt, solid] (3,3) circle (4.472);
+
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (3,3);
+      \draw[color=gray, line width=0.5pt, dashed] (2,1) -- (0,-1);
+      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (0,-1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=yellow] (3,3) circle (2.1pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=white] (0,-1) circle (2.1pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+% Vor- und Nachteile
+\begin{frame}{Orchard’s Algorithmus}{Vor- und Nachteile}
+ \begin{block}{Vorteile}
+  \begin{itemize}
+   \item Schneller als Vollsuche
+  \end{itemize}
+ \end{block}
+ \pause
+ \begin{block}{Nachteile}
+  \begin{itemize}
+   \item Vorverarbeitung kostet viel Speicher und Rechenaufwand
+  \end{itemize}
+ \end{block}
+ \pause
+ \begin{block}{Verfeinerung}
+  \begin{itemize}
+   \item Schon durchwanderte Punkte sollten übersprungen werden
+  \end{itemize}
+ \end{block}
+\end{frame}
+
+\subsection{Annulus Verfahren}
+\begin{frame}{Annulus Verfahren}
+ \begin{itemize}
+  \item Erstelle eine Liste für beliebigen Punkt $p^* \in S$ mit allen Punkten $x \in S$, aufsteigend nach ihrer Distanz
+  \pause
+  \item Wähle beliebigen Kandidaten $c \in S$
+  \pause
+  \item Bewege dich alternierend von $p^*$ weg und wieder hin
+  \pause
+  \item Wenn aktueller Punkt $s$ näher an $q$ als $c$, setze $c:= s$
+  \pause
+  \item Aktueller Punkt $s$ unter $c$:
+  \begin{itemize}
+   \item Wenn $d(p^*, s) < d(p^*, q) - d(c, q)$, können alle Punkte unter $s$ ignoriert werden (Dreiecksungleichung~\ref{ineq:3})
+  \end{itemize}
+  \pause
+  \item Aktueller Punkt $s$ über $c$:
+  \begin{itemize}
+   \item Wenn $d(p^*, s) > d(p*, q) + d(c, q)$, können alle Punkte über $s$ ignoriert werden (Dreiecksungleichung~\ref{ineq:3})
+  \end{itemize}
+  \pause
+  \item Wenn ganze Liste durchlaufen ist $c$ nächster Nachbar
+ \end{itemize}
+\end{frame}
+
 \section{Quellen}

### 2015-07-16 presentation.tex
finish Annulus

@@
  \begin{itemize}
-  \item Erstelle Liste f\"ur alle Punkt $p \in S$ mit allen Punkten $x \in S$, aufsteigend nach ihrer Distanz
+  \item Erstelle Liste f\"ur alle Punkte $p \in S$ mit allen Punkten $x \in S$, aufsteigend nach ihrer Distanz
   \pause
@@
      \item Setze $c:=x_3$ und $s:= x_4$
-     \item Da $7.810 \approx d(c, q) > d(s, q) \approx 2.828$, wird $x_4$ neues $c$
+     \item Da $7.810 \approx d(c, q) > d(s, q) \approx 2.828$, setze $c:=s$
     \end{itemize}
@@
      \item Setze $s:= x_1$
-     \item Da $2.828 \approx d(c, q) > d(s, q) \approx 2.236$, wird $x_1$ neues $c$
+     \item Da $2.828 \approx d(c, q) > d(s, q) \approx 2.236$, setze $c:=s$
     \end{itemize}
@@
   \pause
-  \item Wenn ganze Liste durchlaufen ist $c$ nächster Nachbar
- \end{itemize}
+  \item Wenn ganze Liste durchlaufen, ist $c$ nächster Nachbar
+ \end{itemize}
+\end{frame}
+
+%Beispiel3
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    $\mathbb{U} = \mathbb{R}^2$
+    \begin{block}{Datenpunkte}
+      $x_1 = (3, 3)$\\
+      $x_2 = (-1, 2)$\\
+      $x_3 = (-4, -4)$\\
+      $x_4 = (0, -1)$\\
+      $x_5 = (4, -3)$
+    \end{block}
+    \begin{block}{Anfragepunkt}
+      $q = (2, 1)$
+    \end{block}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \filldraw [color={rgb:red,0;green,0;blue,255}] (3,3) circle (2.5pt );
+      \filldraw [color={rgb:red,0;green,0;blue,255}] (-1,2) circle (2.5pt );
+      \filldraw [color={rgb:red,0;green,0;blue,255}] (-4,-4) circle (2.5pt );
+      \filldraw [color={rgb:red,0;green,0;blue,255}] (0,-1) circle (2.5pt );
+      \filldraw [color={rgb:red,0;green,0;blue,255}] (4,-3) circle (2.5pt );
+
+      \filldraw [color={rgb:red,255;green,0;blue,0}] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel3 Abstand
+\begin{frame}{Annulus Verfahren}{Beispiel}
+  \begin{block}{Abst\"ande}
+  \begin{center}
+    \begin{tabular}{r|ccccc}
+      & $x_1$ & $x_2$ & $x_3$ & $x_4$ & $x_5$\\
+      \hline
+      $x_5$ & $\approx 6.083$ & $\approx 7.071$ & $\approx 8.062$ & $\approx 4.472$ & 0\\
+    \end{tabular}
+  \end{center}
+  \end{block}
+\end{frame}
+
+%Beispiel3 Listen
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    $p^*:=x_5$ mit $d(p^*, q) \approx 4.472$
+    \begin{block}{Liste}
+    $L(x_5) = \{x_5, x_4, x_1, x_2, x_3\}$\\
+    \end{block}
+  \end{column}
+  \begin{column}{.6\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (4,-3);
+      \draw[color=gray, line width=0.5pt, dashed] (4,-3) -- (-4,-4);
+      \draw[color=gray, line width=0.5pt, dashed] (4,-3) -- (0,-1);
+      \draw[color=gray, line width=0.5pt, dashed] (4,-3) -- (-1,2);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=yellow] (4,-3) circle (2.1pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel3 c:=x_2
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:=x_2$ mit $d(c,q) \approx 3.162$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (7.071);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (4.472);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=white] (-1,2) circle (2.1pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=yellow] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel3 c:=x_2
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:=x_2$ mit $d(c, q) \approx 3.162$
+     \item Setze $s:=x_3$ mit $d(s, q) \approx 7.810$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (7.071);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (4.472);
+
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (-1,2) -- (-4,-4);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=white] (-1,2) circle (2.1pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=yellow] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel3 c:=x_2
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:=x_2$ mit $d(c, q) \approx 3.162$
+     \item Setze $s:=x_3$ mit $d(s, q) \approx 7.810$
+     \item $8.062 \approx d(p^*, s) > d(p^*, q) + d(c,q) \approx 7.634 \Rightarrow$ alle Knoten über $x_3$ ignorieren
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (7.071);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (4.472);
+
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (-1,2) -- (-4,-4);
+
+      \draw[color=gray, line width=0.5pt, dashed] (4,-3) -- (-4,-4);
+      \draw[color=gray, line width=0.5pt, dashed] (4,-3) -- (2,1);
+      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (2,1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=white] (-1,2) circle (2.1pt );
+      \filldraw [color=blue] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=yellow] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel3 c:=x_2
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:=x_1$ mit $d(s, q) \approx 2.236$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (7.071);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (4.472);
+
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (-1,2) -- (-4,-4);
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (-4,-4) -- (3,3);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=white] (-1,2) circle (2.1pt );
+      \filldraw [color=gray] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=yellow] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel3 c:=x_2
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:=x_1$ mit $d(s, q) \approx 2.236$
+     \item Da $d(s, q) < d(c, q)$, setze $c:=s$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (7.071);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (4.472);
+
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (-1,2) -- (-4,-4);
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (-4,-4) -- (3,3);
+
+      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (2,1);
+      \draw[color=gray, line width=0.5pt, dashed] (-1,2) -- (2,1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=blue] (-1,2) circle (2.5pt );
+      \filldraw [color=white] (-1,2) circle (2.1pt );
+      \filldraw [color=gray] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=yellow] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel3 c:=x_1
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:=x_1$ mit $d(s, q) \approx 2.236$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (7.071);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (4.472);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=white] (3,3) circle (2.1pt );
+      \filldraw [color=gray] (-1,2) circle (2.5pt );
+      \filldraw [color=gray] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=yellow] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel3 c:=x_1
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:=x_1$ mit $d(c, q) \approx 2.236$
+     \item Setze $s:=x_4$ mit $d(s, q) \approx 2.828$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (7.071);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (4.472);
+
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (3,3) -- (0,-1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=white] (3,3) circle (2.1pt );
+      \filldraw [color=gray] (-1,2) circle (2.5pt );
+      \filldraw [color=gray] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=yellow] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel3 c:=x_1
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $c:=x_1$ mit $d(c, q) \approx 2.236$
+     \item Setze $s:=x_4$ mit $d(s, q) \approx 2.828$
+     \item $4.472 \approx d(p^*, s) > d(p^*, q) - d(c,q) \approx 2.236 \Rightarrow$ keine Knoten ignorieren
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (7.071);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (4.472);
+
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (3,3) -- (0,-1);
+
+      \draw[color=gray, line width=0.5pt, dashed] (4,-3) -- (0,-1);
+      \draw[color=gray, line width=0.5pt, dashed] (4,-3) -- (2,1);
+      \draw[color=gray, line width=0.5pt, dashed] (3,3) -- (2,1);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=white] (3,3) circle (2.1pt );
+      \filldraw [color=gray] (-1,2) circle (2.5pt );
+      \filldraw [color=gray] (-4,-4) circle (2.5pt );
+      \filldraw [color=blue] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=yellow] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel3 c:=x_1
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:=x_5$ mit $d(s, q) \approx 4.472 < 2.236 \approx d(c, q)$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (7.071);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (4.472);
+
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (3,3) -- (0,-1);
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (0,-1) -- (4,-3);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=white] (3,3) circle (2.1pt );
+      \filldraw [color=gray] (-1,2) circle (2.5pt );
+      \filldraw [color=gray] (-4,-4) circle (2.5pt );
+      \filldraw [color=gray] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=yellow] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+%Beispiel3 c:=x_1
+\begin{frame}{Annulus Verfahren}{Beispiel}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Setze $s:=x_5$ mit $d(s, q) \approx 4.472 < 2.236 \approx d(c, q)$
+     \item Da Liste am Ende, $c = x_1$ nächster Nachbar von $q$
+    \end{itemize}
+  \end{column}
+  \begin{column}{.60\textwidth}
+     \begin{tikzpicture}[%
+      scale=0.6,
+      ]
+      \clip (-5.0,-5.0) rectangle (5.0,5.0);
+      \draw [help lines] (0,0) grid (6,5);
+      \draw [help lines] (-6,0) grid (0,5);
+      \draw [help lines] (0,-6) grid (6,0);
+      \draw [help lines] (-6,-6) grid (0,0);
+      \draw [color=black,->] (-5.0,0) -- (5.0,0);
+      \draw [color=black,->] (0,-5.0) -- (0,5.0);
+
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (6.083);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (7.071);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (8.062);
+      \draw [color=gray, line width=0.5pt, solid] (4,-3) circle (4.472);
+
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (3,3) -- (0,-1);
+      \draw[color=darkgray, line width=1.0pt, dashed, ->] (0,-1) -- (4,-3);
+
+      \filldraw [color=blue] (3,3) circle (2.5pt );
+      \filldraw [color=white] (3,3) circle (2.1pt );
+      \filldraw [color=gray] (-1,2) circle (2.5pt );
+      \filldraw [color=gray] (-4,-4) circle (2.5pt );
+      \filldraw [color=gray] (0,-1) circle (2.5pt );
+      \filldraw [color=blue] (4,-3) circle (2.5pt );
+      \filldraw [color=yellow] (4,-3) circle (2.1pt );
+
+      \filldraw [color=red] (2,1) circle (2.5pt );
+
+      \node at (3.3,2.7) {$x_1$};
+      \node at (-0.7,1.7) {$x_2$};
+      \node at (-3.7,-4.3) {$x_3$};
+      \node at (0.3,-1.3) {$x_4$};
+      \node at (4.3,-3.3) {$x_5$};
+
+      \node at (2.3,0.7) {$q$};
+      \end{tikzpicture}
+  \end{column}
+ \end{columns}
+\end{frame}
+
+% Vor- und Nachteile
+\begin{frame}{Annulus Verfahren}{Vor- und Nachteile}
+ \begin{block}{Vorteile}
+  \begin{itemize}
+   \item Schneller als Vollsuche
+   \item Weniger Speicherverbrauch als Orchard’s Algorithmus
+  \end{itemize}
+ \end{block}
 \end{frame}

### 2015-07-16 presentation.tex
finish

@@
  \begin{itemize}
- \item density estimation
- \item pattern recognition
- \item object recognition
- \item data clustering
- \item function approximation
- \item vector quantization
+ \item Mustererkennung
+ \item Statistischen Klassifikationsverfahren
+ \item Bildbearbeitung
+ \item Kodierungstheorie
+ \item Datenkompression
+ \item Empfehlungssystemen
+ \item $\dots$
 \end{itemize}
@@
   \begin{itemize}
-   \item Vorverarbeitung kostet viel Speicher und Rechenaufwand
+   \item Preprocessing kostet viel Speicher und Rechenaufwand
   \end{itemize}
@@
 
+\subsection{AESA}
+\begin{frame}{AESA}{Approximating and Eliminating Search Algorithm}
+ \begin{itemize}
+  \item Erste Matrix aus allen Abständen $d(x, y)$, mit $x, y \in S$
+  \pause
+  \item Jeder Punkt ist immer in einem der drei Statusse
+  \begin{itemize}
+   \item \textit{Bekannt}, $d(x, q)$ ist bekannt
+   \pause
+   \item \textit{Unbekannt}, nur $d_P(x, q)$ ist bekannt
+   \pause
+   \item \textit{Abgelehnt}, $d_P(x, q)$ ist größer als aktuell kleinster Abstand $r$
+  \end{itemize}
+  \pause
+  \item Alle $x \in S$ sind zum Anfang $Unbekannt$ und $d_P(x, q) = \infty$
+  \pause
+  \item Wiederhole bis alle $x \in S$ \textit{Bekannt} oder \textit{Abgelehnt}
+  \begin{enumerate}
+   \item Wähle \textit{Unbekannt}-en Punkt $x \in S$ mit kleinstem $d_P(x, q)$
+   \pause
+   \item Berechne $d(x,q)$, so das $x$ \textit{Bekannt} wird
+   \pause
+   \item Aktuallisiere den kleinsten Abstand $r$
+   \pause
+   \item Setze $P:= P \cup \{x\}$, aktuallisiere $d_P(x', q)$, wenn $x'$ \textit{Unbekannt} und markiere $x'$ \textit{Abgelehnt}, wenn $d_P(x', q) > r$
+  \end{enumerate}
+ \end{itemize}
+\end{frame}
+
+\begin{frame}{LAESA}{\textit{Linear} Approximating and Eliminating Search Algorithm}
+ \begin{itemize}
+  \item Arbeitet mit einer Menge von \textit{pivot}-Elementen, anstelle einer Matrix
+  \pause
+  \item Läuft am besten, wenn die \textit{pivot}-Elemente stark separiert sind
+ \end{itemize}
+\end{frame}
+
+\section{Ausblick}
+\begin{frame}{Ausblick}
+ \begin{itemize}
+  \item Metrikbäume
+  \item \dots
+ \end{itemize}
+\end{frame}
+
 \section{Quellen}

### 2015-08-18 paper/paper.tex
start paper

\documentclass[deutsch,runningheads,a4paper]{llncs}

\usepackage[utf8]{inputenc}
\usepackage{url}

\begin{document}
  \title{Fast Nearest Neighbour Classification}
  \titlerunning{Fast Nearest Neighbour Classification}

  \author{Gordon Lesti}
  \authorrunning{Gordon Lesti}

  \institute{Technische Universität Berlin,\\
  Straße des 17. Juni 135, 10623 Berlin\\
  \url{http://www.tu-berlin.de/}}

  \maketitle

  \begin{abstract}
   jo
  \end{abstract}

  \section{Einleitung}

\end{document}

### 2015-08-18 program/fnnc/src/main/java/de/dailab/fnnc/App.java
init maven

@@ -1,0 +1,23 @@
+package de.dailab.fnnc;
+
+/**
+ * Hello world!
+ *
+ */
+public final class App {
+
+  /**
+   * Hided default constructor for App.
+   */
+  private App() {
+  }
+
+  /**
+   * Main function to start the App.
+   *
+   * @param args arguments
+   */
+  public static void main(final String[] args) {
+    System.out.println("Hello World!");
+  }
+}

### 2015-08-18 program/fnnc/src/main/java/de/dailab/fnnc/package-info.java

@@ -1,0 +1,4 @@
+/**
+ * Provides the classes necessary to compare nearest neighbor classifications.
+ */
+package de.dailab.fnnc;

### 2015-08-18 program/fnnc/src/test/java/de/dailab/fnnc/AppTest.java

@@ -1,0 +1,38 @@
+package de.dailab.fnnc;
+
+import junit.framework.Test;
+import junit.framework.TestCase;
+import junit.framework.TestSuite;
+
+/**
+ * Unit test for simple App.
+ */
+public class AppTest 
+    extends TestCase
+{
+    /**
+     * Create the test case
+     *
+     * @param testName name of the test case
+     */
+    public AppTest( String testName )
+    {
+        super( testName );
+    }
+
+    /**
+     * @return the suite of tests being tested
+     */
+    public static Test suite()
+    {
+        return new TestSuite( AppTest.class );
+    }
+
+    /**
+     * Rigourous Test :-)
+     */
+    public void testApp()
+    {
+        assertTrue( true );
+    }
+}

### 2015-08-18 program/fnnc/src/main/java/de/dailab/fnnc/distance/DistanceComputable.java
complete vector and fullsearch

@@ -1,0 +1,17 @@
+package de.dailab.fnnc.distance;
+
+/**
+ * A interface for objects to compute the distance between these objects.
+ *
+ * @param <T> the type of objects that this object may be compared to
+ */
+public interface DistanceComputable<T> {
+
+  /**
+   * Computes the distance between this object and the given one.
+   *
+   * @param object the object to compute the distance from.
+   * @return distance
+   */
+  double computeDistance(T object);
+}

### 2015-08-18 program/fnnc/src/main/java/de/dailab/fnnc/distance/Vector.java

@@ -1,0 +1,43 @@
+package de.dailab.fnnc.distance;
+
+/**
+ * Class representing a vector in the euclidian space.
+ */
+public class Vector implements DistanceComputable<Vector> {
+
+  /**
+   * The values of the vector.
+   */
+  private double[] values;
+
+  /**
+   * Creates a new vector.
+   *
+   * @param entries entries
+   */
+  public Vector(final double[] entries) {
+    this.values = entries;
+  }
+
+  /**
+   * @inheritDoc
+   *
+   * @param vector vector
+   * @return distance
+   */
+  public final double computeDistance(final Vector vector) {
+    final int size = this.values.length;
+    if (size != vector.values.length) {
+      throw new RuntimeException(
+      "Can not compute distance between a vector of size "
+      + size + " and a vector of size " + vector.values.length
+      );
+    }
+
+    double sum = 0;
+    for (int i = 0; i < size; i++) {
+      sum += Math.pow(this.values[i] - vector.values[i], 2);
+    }
+    return Math.sqrt(sum);
+  }
+}

### 2015-08-18 program/fnnc/src/main/java/de/dailab/fnnc/distance/package-info.java

@@ -1,0 +1,4 @@
+/**
+ * Provides the classes necessary to copute the distance of two objects.
+ */
+package de.dailab.fnnc.distance;

### 2015-08-18 program/fnnc/src/main/java/de/dailab/fnnc/search/FullSearch.java

@@ -1,0 +1,42 @@
+package de.dailab.fnnc.search;
+
+import de.dailab.fnnc.distance.Vector;
+
+/**
+ * Fullsearch algorithm.
+ */
+public class FullSearch {
+
+  /**
+   * Set of vectors.
+   */
+  private Vector[] vectors;
+
+  /**
+   * Creates a FullSearch.
+   *
+   * @param vectorSet given set of vectors
+   */
+  public FullSearch(final Vector[] vectorSet) {
+    this.vectors = vectorSet;
+  }
+
+  /**
+   * Returns the nearest neighbor of the given object.
+   *
+   * @param vector given query vector
+   * @return nearest neighbor
+   */
+  public final Vector getNearestNeighbor(final Vector vector) {
+    double smallestDistance = Double.POSITIVE_INFINITY;
+    int smallestIndex = 0;
+    for (int i = 0; i < this.vectors.length; i++) {
+      final double currentDistance = this.vectors[i].computeDistance(vector);
+      if (currentDistance < smallestDistance) {
+        smallestIndex = i;
+        smallestDistance = currentDistance;
+      }
+    }
+    return this.vectors[smallestIndex];
+  }
+}

### 2015-08-18 program/fnnc/src/main/java/de/dailab/fnnc/search/package-info.java

@@ -1,0 +1,4 @@
+/**
+ * Provides the classes representing nearest neighbor searches.
+ */
+package de.dailab.fnnc.search;

### 2015-08-18 program/fnnc/src/test/java/de/dailab/fnnc/distance/VectorTest.java

@@ -1,0 +1,35 @@
+package de.dailab.fncc.distance;
+
+import junit.framework.TestCase;
+import de.dailab.fnnc.distance.Vector;
+
+public class VectorTest extends TestCase {
+
+  public void testComputeDistance() {
+    double[] entries1 = {1.0, 2.0};
+    Vector vector1 = new Vector(entries1);
+    double[] entries2 = {-0.5, -3.0};
+    Vector vector2 = new Vector(entries2);
+
+    assertEquals(vector1.computeDistance(vector2), Math.sqrt(27.25));
+  }
+
+  public void testComputeDistanceRuntimeException() {
+    double[] entries1 = {1.0};
+    Vector vector1 = new Vector(entries1);
+    double[] entries2 = {-0.5, -3.0};
+    Vector vector2 = new Vector(entries2);
+    try {
+      vector1.computeDistance(vector2);
+      fail(
+        "Should throw an exception that the vectors have different dimensions"
+      );
+    } catch (RuntimeException e) {
+      assertEquals(
+        e.getMessage(),
+        "Can not compute distance between a vector of size 1 and a vector of si"
+          + "ze 2"
+      );
+    }
+  }
+}

### 2015-08-18 program/fnnc/src/test/java/de/dailab/fnnc/search/FullSearchTest.java

@@ -1,0 +1,21 @@
+package de.dailab.fncc.search;
+
+import junit.framework.TestCase;
+import de.dailab.fnnc.search.FullSearch;
+import de.dailab.fnnc.distance.Vector;
+
+public class FullSearchTest extends TestCase {
+
+  public void testGetNearestNeighbor() {
+    double[] entries1 = {1.0, 2.0};
+    Vector vector1 = new Vector(entries1);
+    double[] entries2 = {-0.5, -3.0};
+    Vector vector2 = new Vector(entries2);
+    double[] entries3 = {-1.0, -3.0};
+    Vector vector3 = new Vector(entries3);
+
+    Vector[] vectorSet = {vector1, vector2};
+    FullSearch fsearch = new FullSearch(vectorSet);
+    assertEquals(fsearch.getNearestNeighbor(vector3), vector2);
+  }
+}

### 2015-09-27 paper/paper.tex
progress in paper

@@
 \usepackage[utf8]{inputenc}
-\usepackage{url}
+\usepackage{amsfonts}
+\usepackage[T1]{fontenc}
+\usepackage[a4paper, left=3cm, right=3cm, top=2.5cm, bottom=2cm]{geometry}
+
+\newcommand{\keywords}[1]{\par\addvspace\baselineskip
+\noindent\keywordname\enspace\ignorespaces#1}
+
+\newcommand{\changefont}[3]{
+\fontfamily{#1} \fontseries{#2} \fontshape{#3} \selectfont}
+\changefont{ptm}{m}{n}
+\fontsize{12pt}{6pt}
 
 \begin{document}
+  \setcounter{tocdepth}{2}
+  \makeatletter
+  \renewcommand*\l@author[2]{}
+  \renewcommand*\l@title[2]{}
+  \makeatletter
   \title{Fast Nearest Neighbour Classification}
+  \subtitle{\textnormal{\small{Seminar\\Intelligente Software-Systeme\\Sommersemester 2015}\\\vspace{1\baselineskip} Stefan Fricke\\\vspace{15\baselineskip} Oktober 2015\\Betreuer: Stephan Spiegel\\\vspace{2\baselineskip}}}
   \titlerunning{Fast Nearest Neighbour Classification}
 
-  \author{Gordon Lesti}
+  \author{Gordon Lesti\\313249\\Studiengang: Informatik\\gordon.lesti@campus.tu-berlin.de}
   \authorrunning{Gordon Lesti}
 
-  \institute{Technische Universität Berlin,\\
-  Straße des 17. Juni 135, 10623 Berlin\\
-  \url{http://www.tu-berlin.de/}}
+  \institute{Technische Universität Berlin\\
+  Fakultät IV – Elektrotechnik und Informatik\\
+  Fachgebiet AOT\\
+  Prof. Dr. Sahin Albayrak}
 
   \maketitle
+  \newpage
+  \pagenumbering{roman}
 
+  \addcontentsline{toc}{section}{Zusammenfassung}
   \begin{abstract}
-   jo
+    Diese Seminararbeit befasst sich mit dem Problem der \textit{Nächster Nachbar Klassifikation}. Zur Lösung dieses
+    Problems werden grundlegende Algorithmen basierend auf der Dreiecksungleichung in metrischen Räumen vorgestellt und
+    verglichen. Dabei hat jeder Algorithmus die Aufgabe aus einer Menge $S$ das Element $a$ zu ermitteln, welches den
+    kleinsten Abstand zum Anfragepunkt $q$ hat. $S$ ist dabei eine endliche Teilmenge von $\mathbb{U}$ und $d$ das
+    Abstandsmaß auf $\mathbb{U}$.
+    \keywords{Nächster Nachbar Klassifikation, Dreiecksungleichung, Metrischer Raum}\\\vspace{4\baselineskip}
+
+    \textbf{Plagiatserklärung}\\
+    Hiermit versichere ich, dass ich diese Seminararbeit selbstständig verfasst und keine anderen als die angegebenen
+    Quellen und Hilfsmittel benutzt habe. Die Stellen meiner Arbeit, die dem Wortlaut oder dem Sinn nach anderen Werken
+    entnommen sind, habe ich in jedem Fall unter Angabe der Quelle als Entlehnung kenntlich gemacht. Dasselbe gilt
+    sinngemaäß für Tabellen, Karten und Abbildungen. Diese Arbeit hat in dieser oder einer ähnlichen Form noch nicht im
+    Rahmen einer anderen Prüfung vorgelegen.
   \end{abstract}
 
+  \tableofcontents
+  \addcontentsline{toc}{section}{Inhaltsverzeichnis}
+  \newpage
+  \pagenumbering{arabic}
+
   \section{Einleitung}
+    Das Problem der \textit{Nächster Nachbar Klassifikation} lässt sich recht leicht zusammen fassen. Gegeben ist eine
+    Menge $\mathbb{U}$ und ein Abstandsmaß $d$ auf $\mathbb{U}$ mit $d: \mathbb{U} \times \mathbb{U} \to \mathbb{R}$.
+    Des weiteren eine endliche Teilmenge $S \subset \mathbb{U}$ der Größe $n$ und ein Anfragepunkt $q \in \mathbb{U}$.
+    Gesucht ist der nächste Nachbar $a$ aus $S$, welcher minimalen Abstand zu $q$ hat. Also $a \in S$, mit
+    $d(q, a) \le d(q, x)$ f\"ur alle $x \in S$.
+
+    Eine allgemeinere Form dieses Problems ist die \textit{k-Nächsten Nachbarn Klassifikation}. In dieser
+    Semesterarbeit wird somit der Spezialfall mit $k = 1$ betrachtet.
+
+  \subsection{Vollsuche}
+    Die Vollsuche ist die einfachste Form um einen nächsten Nachbarn $a$ aus der Menge $S$ zu ermitteln.
+    Dabei wird für jedes Element $x \in S$ der Abstand $d(q, x)$ berechnet. Der nächste Nachbar zu $q$ ist das Element
+    mit dem kleinsten Abstand.
+
+    Ein Vorteil der Vollsuche ist, dass die Implementierung sehr einfach ist. Des weiteren funktioniert dieser
+    Algorithmus auch in nicht metrischen Räumen. Der große Nachteil ist eindeutig die Laufzeit. Für jedes Element aus
+    $S$ muss der Abstand zum Anfragepunkt $q$ berechnet werden.
+
+  \section{Algorithmen}
+
+  \subsection{Orchard's Algorithmus}
+
+  \subsection{Annulus Verfahren}
+
+  \subsection{AESA}
 

### 2015-10-13 paper/paper.tex
started annulus

@@
 \usepackage{amsfonts}
+\usepackage{cite}
+\usepackage[ngerman]{babel}
 \usepackage[T1]{fontenc}
@@
   \title{Fast Nearest Neighbour Classification}
-  \subtitle{\textnormal{\small{Seminar\\Intelligente Software-Systeme\\Sommersemester 2015}\\\vspace{1\baselineskip} Stefan Fricke\\\vspace{15\baselineskip} Oktober 2015\\Betreuer: Stephan Spiegel\\\vspace{2\baselineskip}}}
+  \subtitle{\textnormal{\small{Seminar\\Intelligente Software-Systeme\\Sommersemester 2015}\\\vspace{1\baselineskip}
+    Stefan Fricke\\\vspace{15\baselineskip} September 2015\\Betreuer: Stephan Spiegel\\\vspace{2\baselineskip}}}
   \titlerunning{Fast Nearest Neighbour Classification}
@@
   \section{Algorithmen}
+    Die folgenden Algorithmen machen alle Gebrauch von den Eigenschaften des metrischen Raumes. Insbesondere die
+    Dreiecksungleichung hilft Abstandsvergleiche mit dem Anfragepunkt $q$ einzusparen. Eine Metrik hat nach Foster
+    \cite{forster-analysis2} folgende Definition.
+    \begin{definition}
+      Sei $x$ eine Menge. Unter einer \textit{Metrik} auf $X$ versteht man eine Abbildung
+      $d:X \times X \to \mathbb{R}$, $(x, y) \mapsto d(x, y)$ mit folgenden Eigenschaften:
+      \begin{enumerate}
+      \item $d(x, y) = 0$ genau dann, wenn $x=y$.
+      \item Symmetrie: F\"ur alle $x, y \in X$ gilt $d(x, y) = d(y, x)$.
+      \item Dreiecksungleichung: F\"ur alle $x, y, z \in X$ gilt $d(x, z) \le d(x, y) + d(y,z)$
+      \end{enumerate}
+    \end{definition}
+    Um diese Eigenschaft der Dreiecksungleichung in den Algorithmen nutzen zu können brauchen wir folgendes Lemma von
+    Clarkson \cite{clarkson2005nearest}.
+    \begin{lemma}
+     F\"ur beliebige $q, s, p \in \mathbb{U}$, $r \in \mathbb{R}$ und $P \subset \mathbb{U}$ gilt:
+     \begin{enumerate}
+      \item \label{ineq:1}$|d(p, q) - d(p, s)| \le d(q, s) \le d(p, q) + d(p, s)$
+      \item \label{ineq:2}$d(q, s) \ge d_P(q, s) := \max_{p \in P}|d(p, q) - d(p, s)|$
+      \item \label{ineq:3}$d(p, s) > d(p, q) + r \vee d(p, s) < d(p, q) -r \Rightarrow d(q, s) > r$
+      \item \label{ineq:4}$d(p, s) \ge 2 \cdot d(p, q) \Rightarrow d(q, s) \ge d(q, p)$
+     \end{enumerate}
+    \end{lemma}
 
   \subsection{Orchard's Algorithmus}
-
+    \begin{itemize}
+     \item F\"ur alle Punkte $p \in S$ wird mit allen Punkten $x \in S$ eine Liste erstellt, aufsteigend nach ihrer Distanz
+     \item Es wird zufälliger Punkt $c \in S$ als initialen Kandidaten gewählt
+     \item Es wird $d(c, q)$ berechnet
+     \item Liste von $c$ wird entlanggegangen
+     \item Wenn aktueller Punkt näher an $q$ als $c$, wird aktueller Punkt $c$
+     \item Abbruch, wenn
+      \begin{itemize}
+       \item die Liste komplett abgelaufen ist, oder
+       \item $d(c, s) > 2 \cdot d(c, q)$ f\"ur aktuelles Element aus der Liste (Dreiecksungleichung~\ref{ineq:4})
+      \end{itemize}
+     \item Sonst ist $c$ nächster Nachbar
+    \end{itemize}
   \subsection{Annulus Verfahren}
-
+   \begin{itemize}
+      \item Erstelle eine Liste für beliebigen Punkt $p^* \in S$ mit allen Punkten $x \in S$, aufsteigend nach ihrer Distanz
+      \item Wähle beliebigen Kandidaten $c \in S$
+      \item Bewege dich alternierend von $p^*$ weg und wieder hin
+      \item Wenn aktueller Punkt $s$ näher an $q$ als $c$, setze $c:= s$
+      \item Aktueller Punkt $s$ unter $c$:
+      \begin{itemize}
+      \item Wenn $d(p^*, s) < d(p^*, q) - d(c, q)$, können alle Punkte unter $s$ ignoriert werden (Dreiecksungleichung~\ref{ineq:3})
+      \end{itemize}
+      \item Aktueller Punkt $s$ über $c$:
+      \begin{itemize}
+      \item Wenn $d(p^*, s) > d(p*, q) + d(c, q)$, können alle Punkte über $s$ ignoriert werden (Dreiecksungleichung~\ref{ineq:3})
+      \end{itemize}
+      \item Wenn ganze Liste durchlaufen, ist $c$ nächster Nachbar
+    \end{itemize}
   \subsection{AESA}
-
+    \begin{itemize}
+      \item Erstelle Matrix aus allen Abständen $d(x, y)$, mit $x, y \in S$
+      \item Jeder Punkt ist immer in einem der drei Statusse
+      \begin{itemize}
+      \item \textit{Bekannt}, $d(x, q)$ ist bekannt
+      \item \textit{Unbekannt}, nur $d_P(x, q)$ ist bekannt
+      \item \textit{Abgelehnt}, $d_P(x, q)$ ist größer als aktuell kleinster Abstand $r$
+      \end{itemize}
+      \item Alle $x \in S$ sind zum Anfang $Unbekannt$ und $d_P(x, q) = \infty$
+      \item Wiederhole bis alle $x \in S$ \textit{Bekannt} oder \textit{Abgelehnt}
+      \begin{enumerate}
+      \item Wähle \textit{Unbekannt}-en Punkt $x \in S$ mit kleinstem $d_P(x, q)$
+      \item Berechne $d(x,q)$, so das $x$ \textit{Bekannt} wird
+      \item Aktuallisiere den kleinsten Abstand $r$
+      \item Setze $P:= P \cup \{x\}$, aktuallisiere $d_P(x', q)$, wenn $x'$ \textit{Unbekannt} und markiere $x'$ \textit{Abgelehnt}, wenn $d_P(x', q) > r$
+      \end{enumerate}
+    \end{itemize}
+  \bibliography{paper.bib}{}
+  \bibliographystyle{splncs03}
+  \addcontentsline{toc}{section}{Literatur}
 \end{document}

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/App.java

@@ -1,5 +1,9 @@
 package de.dailab.fnnc;
 
+import java.util.Random;
+import de.dailab.fnnc.framework.TestDataCreator;
+import de.dailab.fnnc.distance.Vector;
+
 /**
  * Hello world!
  *
@@ -18,6 +22,25 @@ public final class App {
    * @param args arguments
    */
   public static void main(final String[] args) {
-    System.out.println("Hello World!");
+    int size = 1000;
+    int dim = 10;
+    Random rand = new Random();
+    Vector[] vectors = new Vector[size];
+    for (int i = 0; i < size; i++) {
+      double[] entries = new double[dim];
+      for (int j = 0; j < dim; j++) {
+        double value = rand.nextInt(1000000);
+        if (rand.nextBoolean()) {
+          value *= -1;
+        }
+        entries[j] = value;
+      }
+      vectors[i] = new Vector(entries);
+    }
+    TestDataCreator.write(vectors, "1000_10");
+    vectors = TestDataCreator.read("1000_10");
+    for (int i = 0; i < vectors.length; i++) {
+      System.out.println(vectors[i].toString());
+    }
   }
 }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/distance/DistanceComputable.java

@@ -1,17 +1,0 @@
-package de.dailab.fnnc.distance;
-
-/**
- * A interface for objects to compute the distance between these objects.
- *
- * @param <T> the type of objects that this object may be compared to
- */
-public interface DistanceComputable<T> {
-
-  /**
-   * Computes the distance between this object and the given one.
-   *
-   * @param object the object to compute the distance from.
-   * @return distance
-   */
-  double computeDistance(T object);
-}

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/distance/Vector.java

@@ -1,9 +1,13 @@
 package de.dailab.fnnc.distance;
 
+import java.io.Serializable;
+
 /**
  * Class representing a vector in the euclidian space.
  */
-public class Vector implements DistanceComputable<Vector> {
+public class Vector implements Serializable{
+
+  private static final long serialVersionUID = 42L;
 
   /**
    * The values of the vector.
@@ -39,5 +43,28 @@ public class Vector implements DistanceComputable<Vector> {
       sum += Math.pow(this.values[i] - vector.values[i], 2);
     }
     return Math.sqrt(sum);
+  }
+
+  public String toString() {
+    String output = "<";
+    int lastIndex = this.values.length - 1;
+    for (int i = 0; i < lastIndex; i++) {
+      output += this.values[i] + ", ";
+    }
+    output += this.values[lastIndex] + ">";
+    return output;
+  }
+
+  public boolean equals(Object object) {
+    if (object instanceof Vector) {
+      Vector vector = (Vector) object;
+      for (int i = 0; i < this.values.length; i++) {
+        if (this.values[i] != vector.values[i]) {
+          return false;
+        }
+      }
+      return true;
+    }
+    return false;
   }
 }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/framework/TestDataCreator.java

@@ -1,0 +1,39 @@
+package de.dailab.fnnc.framework;
+
+import java.io.*;
+import de.dailab.fnnc.distance.Vector;
+
+public class TestDataCreator {
+
+  public static void write(final Vector[] vectors, final String filename) {
+    try {
+      OutputStream file = new FileOutputStream(filename);
+      OutputStream buffer = new BufferedOutputStream(file);
+      ObjectOutput output = new ObjectOutputStream(buffer);
+      try {
+        output.writeObject(vectors);
+      } finally {
+        output.close();
+      }
+    } catch (Exception e) {
+      e.printStackTrace(System.out);
+    }
+  }
+
+  public static Vector[] read(final String filename) {
+    Vector[] vectors = null;
+    try {
+      InputStream file = new FileInputStream(filename);
+      InputStream buffer = new BufferedInputStream(file);
+      ObjectInput input = new ObjectInputStream(buffer);
+      try {
+        vectors = (Vector[]) input.readObject();
+      } finally {
+        input.close();
+      }
+    } catch (Exception e) {
+      e.printStackTrace(System.out);
+    }
+    return vectors;
+  }
+}

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/AnnulusMethod.java

@@ -1,0 +1,58 @@
+package de.dailab.fnnc.search;
+
+import java.util.Arrays;
+import java.util.Random;
+import de.dailab.fnnc.distance.Vector;
+import de.dailab.fnnc.search.orchard.VectorDistance;
+
+public class AnnulusMethod implements NearestNeighborSearch{
+
+  /**
+   * Set of vectors.
+   */
+  private Vector[] vectors;
+
+  private int pStarIndex;
+
+  private VectorDistance[] list;
+
+  private boolean[] visited;
+
+  private int highestVisitedSIndex;
+
+  private int lowestVisitedSindex;
+
+  private int upperBound;
+
+  private int lowerBound;
+
+  public void setVectors(final Vector[] vectorSet) {
+    this.vectors = vectorSet;
+    Random rand = new Random();
+    int length = this.vectors.length;
+    this.pStarIndex = rand.nextInt(length);
+    this.list = new VectorDistance[length];
+    for (int i = 0; i < length; i++) {
+      double distance = this.vectors[this.pStarIndex].computeDistance(this.vectors[i]);
+      this.list[i] = new VectorDistance(i, distance);
+    }
+    Arrays.sort(this.list);
+  }
+
+  /**
+   * Returns the nearest neighbor of the given object.
+   *
+   * @param vector given query vector
+   * @return nearest neighbor
+   */
+  public final Vector getNearestNeighbor(final Vector vector) {
+    this.visited = new boolean[this.list.length];
+    Random rand = new Random();
+    int cIndexInPList = rand.nextInt(this.list.length);
+    this.highestVisitedSIndex = cIndexInPList;
+    this.lowestVisitedSindex = cIndexInPList;
+    this.upperBound = Integer.MIN_VALUE;
+    this.lowerBound = Integer.MAX_VALUE;
+    return this.vectors[cIndexInPList];
+  }
+}

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/FullSearch.java

@@ -5,19 +5,14 @@ import de.dailab.fnnc.distance.Vector;
 /**
  * Fullsearch algorithm.
  */
-public class FullSearch {
+public class FullSearch implements NearestNeighborSearch{
 
   /**
    * Set of vectors.
    */
   private Vector[] vectors;
 
-  /**
-   * Creates a FullSearch.
-   *
-   * @param vectorSet given set of vectors
-   */
-  public FullSearch(final Vector[] vectorSet) {
+  public void setVectors(final Vector[] vectorSet) {
     this.vectors = vectorSet;
   }
 
@@ -30,13 +25,16 @@ public class FullSearch {
   public final Vector getNearestNeighbor(final Vector vector) {
     double smallestDistance = Double.POSITIVE_INFINITY;
     int smallestIndex = 0;
+    int distanceCount = 0;
     for (int i = 0; i < this.vectors.length; i++) {
       final double currentDistance = this.vectors[i].computeDistance(vector);
+      distanceCount++;
       if (currentDistance < smallestDistance) {
         smallestIndex = i;
         smallestDistance = currentDistance;
       }
     }
+    System.out.println("FULLSEARCH DISTANCE_COUNT:"+distanceCount);
     return this.vectors[smallestIndex];
   }
 }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/NearestNeighborSearch.java

@@ -1,0 +1,9 @@
+package de.dailab.fnnc.search;
+
+import de.dailab.fnnc.distance.Vector;
+
+public interface NearestNeighborSearch {
+  public void setVectors(Vector[] vectorSet);
+
+  public Vector getNearestNeighbor(Vector vector);
+}

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/OrchardAlgorithmus.java

@@ -1,0 +1,66 @@
+package de.dailab.fnnc.search;
+
+import java.util.Arrays;
+import java.util.Random;
+import de.dailab.fnnc.distance.Vector;
+import de.dailab.fnnc.search.orchard.VectorDistance;
+
+/**
+ * Orchard's Algorithmus.
+ */
+public class OrchardAlgorithmus implements NearestNeighborSearch{
+
+  /**
+   * Set of vectors.
+   */
+  private Vector[] vectors;
+
+  private VectorDistance[][] lists;
+
+  public void setVectors(final Vector[] vectorSet) {
+    this.vectors = vectorSet;
+    int length = this.vectors.length;
+    this.lists = new VectorDistance[length][length-1];
+    for (int i = 0; i < length; i++) {
+      for (int j = i + 1; j < length; j++) {
+        Vector vectorA = this.vectors[i];
+        Vector vectorB = this.vectors[j];
+        double distance = vectorA.computeDistance(vectorB);
+        this.lists[i][j-1] = new VectorDistance(j, distance);
+        this.lists[j][i] = new VectorDistance(i, distance);
+      }
+      Arrays.sort(this.lists[i]);
+    }
+  }
+
+  /**
+   * Returns the nearest neighbor of the given object.
+   *
+   * @param vector given query vector
+   * @return nearest neighbor
+   */
+  public final Vector getNearestNeighbor(final Vector vector) {
+    Random rand = new Random();
+    int cIndex = rand.nextInt(this.vectors.length);
+    double distanceCQ = this.vectors[cIndex].computeDistance(vector);
+    int sIndexInCList = 0;
+    boolean stop = false;
+    int distanceCount = 0;
+    while (!stop) {
+      int sIndex = this.lists[cIndex][sIndexInCList].getVectorIndex();
+      distanceCount++;
+      double distanceSQ = this.vectors[sIndex].computeDistance(vector);
+      if (distanceSQ < distanceCQ) {
+        cIndex = sIndex;
+        sIndexInCList = 0;
+        distanceCQ = distanceSQ;
+      } else if (sIndexInCList == this.vectors.length - 2 || this.lists[cIndex][sIndexInCList].getDistance() > 2 * distanceCQ) {
+        stop = true;
+      } else {
+        sIndexInCList++;
+      }
+    }
+    System.out.println("ORCHARD DISTANCE_COUNT:"+distanceCount);
+    return this.vectors[cIndex];
+  }
+}

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/orchard/VectorDistance.java

@@ -1,0 +1,34 @@
+package de.dailab.fnnc.search.orchard;
+
+public class VectorDistance implements Comparable<VectorDistance> {
+  private int vectorIndex;
+
+  private double distance;
+
+  public VectorDistance(int vectorIndex, double dist) {
+    this.vectorIndex = vectorIndex;
+    this.distance = dist;
+  }
+
+  public double getDistance() {
+    return this.distance;
+  }
+
+  public int getVectorIndex() {
+    return this.vectorIndex;
+  }
+
+  public int compareTo(VectorDistance vecDist) {
+    if (this.distance < vecDist.distance) {
+      return -1;
+    }
+    if (this.distance == vecDist.distance) {
+      return 0;
+    }
+    return 1;
+  }
+
+  public String toString() {
+    return "Intex: "+this.vectorIndex+" Distance: "+this.distance;
+  }
+}

### 2015-10-13 program/fnnc/src/test/java/de/dailab/fnnc/search/AnnulusMethodTest.java

@@ -1,11 +1,11 @@
 package de.dailab.fncc.search;
 
 import junit.framework.TestCase;
-import de.dailab.fnnc.search.FullSearch;
+import de.dailab.fnnc.search.AnnulusMethod;
 import de.dailab.fnnc.distance.Vector;
 import de.dailab.fnnc.framework.TestDataCreator;
 
-public class FullSearchTest extends TestCase {
+public class AnnulusMethodTest extends TestCase {
 
   public void testGetNearestNeighbor() {
     double[] entries1 = {1.0, 2.0};
@@ -14,11 +14,13 @@ public class FullSearchTest extends TestCase {
     Vector vector2 = new Vector(entries2);
     double[] entries3 = {-1.0, -3.0};
     Vector vector3 = new Vector(entries3);
+    double[] entries4 = {-7, 8};
+    Vector vector4 = new Vector(entries4);
 
-    Vector[] vectorSet = {vector1, vector2};
-    FullSearch fsearch = new FullSearch();
-    fsearch.setVectors(vectorSet);
-    assertEquals(fsearch.getNearestNeighbor(vector3), vector2);
+    Vector[] vectorSet = {vector1, vector2, vector4};
+    AnnulusMethod annulus = new AnnulusMethod();
+    annulus.setVectors(vectorSet);
+    assertEquals(annulus.getNearestNeighbor(vector3), vector2);
   }
 
   public void testGetNearestNeighborS1000d50() {
@@ -36,8 +38,8 @@ public class FullSearchTest extends TestCase {
       -461315.0
     };
     Vector queryVector = new Vector(queryEntries);
-    FullSearch fsearch = new FullSearch();
-    fsearch.setVectors(vectors);
+    AnnulusMethod annulus = new AnnulusMethod();
+    annulus.setVectors(vectors);
     double[] nnEntries = {
       870784.0,
       53276.0,
@@ -51,6 +53,6 @@ public class FullSearchTest extends TestCase {
       -362347.0
     };
     Vector nearestNeighbor = new Vector(nnEntries);
-    assertEquals(fsearch.getNearestNeighbor(queryVector), nearestNeighbor);
+    assertEquals(annulus.getNearestNeighbor(queryVector), nearestNeighbor);
   }
 }

### 2015-10-13 program/fnnc/src/test/java/de/dailab/fnnc/search/OrchardAlgorithmusTest.java

@@ -1,11 +1,11 @@
 package de.dailab.fncc.search;
 
 import junit.framework.TestCase;
-import de.dailab.fnnc.search.FullSearch;
+import de.dailab.fnnc.search.OrchardAlgorithmus;
 import de.dailab.fnnc.distance.Vector;
 import de.dailab.fnnc.framework.TestDataCreator;
 
-public class FullSearchTest extends TestCase {
+public class OrchardAlgorithmusTest extends TestCase {
 
   public void testGetNearestNeighbor() {
     double[] entries1 = {1.0, 2.0};
@@ -14,11 +14,13 @@ public class FullSearchTest extends TestCase {
     Vector vector2 = new Vector(entries2);
     double[] entries3 = {-1.0, -3.0};
     Vector vector3 = new Vector(entries3);
+    double[] entries4 = {-7, 8};
+    Vector vector4 = new Vector(entries4);
 
-    Vector[] vectorSet = {vector1, vector2};
-    FullSearch fsearch = new FullSearch();
-    fsearch.setVectors(vectorSet);
-    assertEquals(fsearch.getNearestNeighbor(vector3), vector2);
+    Vector[] vectorSet = {vector1, vector2, vector4};
+    OrchardAlgorithmus orchard = new OrchardAlgorithmus();
+    orchard.setVectors(vectorSet);
+    assertEquals(orchard.getNearestNeighbor(vector3), vector2);
   }
 
   public void testGetNearestNeighborS1000d50() {
@@ -36,8 +38,8 @@ public class FullSearchTest extends TestCase {
       -461315.0
     };
     Vector queryVector = new Vector(queryEntries);
-    FullSearch fsearch = new FullSearch();
-    fsearch.setVectors(vectors);
+    OrchardAlgorithmus orchard = new OrchardAlgorithmus();
+    orchard.setVectors(vectors);
     double[] nnEntries = {
       870784.0,
       53276.0,
@@ -51,6 +53,6 @@ public class FullSearchTest extends TestCase {
       -362347.0
     };
     Vector nearestNeighbor = new Vector(nnEntries);
-    assertEquals(fsearch.getNearestNeighbor(queryVector), nearestNeighbor);
+    assertEquals(orchard.getNearestNeighbor(queryVector), nearestNeighbor);
   }
 }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/App.java
checkstyle

@@ -5,10 +5,24 @@ import de.dailab.fnnc.framework.TestDataCreator;
 import de.dailab.fnnc.distance.Vector;
 
 /**
- * Hello world!
- *
+ * Application to nur the benchmark of Fast Nearest Neighbor Search algorithms.
  */
 public final class App {
+
+  /**
+   * Size of the vector set.
+   */
+  private static final int SIZE = 1000;
+
+  /**
+   * Dimension of the vectors.
+   */
+  private static final int DIM = 10;
+
+  /**
+   * Maximal value for a vector entry.
+   */
+  private static final int MAX_VALUE = 1000000;
 
   /**
    * Hided default constructor for App.
@@ -22,14 +36,12 @@ public final class App {
    * @param args arguments
    */
   public static void main(final String[] args) {
-    int size = 1000;
-    int dim = 10;
     Random rand = new Random();
-    Vector[] vectors = new Vector[size];
-    for (int i = 0; i < size; i++) {
-      double[] entries = new double[dim];
-      for (int j = 0; j < dim; j++) {
-        double value = rand.nextInt(1000000);
+    Vector[] vectors = new Vector[this.SIZE];
+    for (int i = 0; i < this.SIZE; i++) {
+      double[] entries = new double[this.DIM];
+      for (int j = 0; j < this.DIM; j++) {
+        double value = rand.nextInt(this.MAX_VALUE);
         if (rand.nextBoolean()) {
           value *= -1;
         }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/distance/Vector.java

@@ -5,8 +5,11 @@ import java.io.Serializable;
 /**
  * Class representing a vector in the euclidian space.
  */
-public class Vector implements Serializable{
+public class Vector implements Serializable {
 
+  /**
+   * Serial version UID.
+   */
   private static final long serialVersionUID = 42L;
 
   /**
@@ -45,7 +48,12 @@ public class Vector implements Serializable{
     return Math.sqrt(sum);
   }
 
-  public String toString() {
+  /**
+   * Returns a string representing the vector.
+   *
+   * @return string
+   */
+  public final String toString() {
     String output = "<";
     int lastIndex = this.values.length - 1;
     for (int i = 0; i < lastIndex; i++) {
@@ -55,7 +63,13 @@ public class Vector implements Serializable{
     return output;
   }
 
-  public boolean equals(Object object) {
+  /**
+   * Checks if an object is equals to this vector.
+   *
+   * @param object object
+   * @return equals
+   */
+  public final boolean equals(final Object object) {
     if (object instanceof Vector) {
       Vector vector = (Vector) object;
       for (int i = 0; i < this.values.length; i++) {
@@ -66,5 +80,14 @@ public class Vector implements Serializable{
       return true;
     }
     return false;
+  }
+
+  /**
+   * Creates a hashCode of the vector.
+   *
+   * @return hash
+   */
+  public final int hashCode() {
+    super();
   }
 }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/framework/TestDataCreator.java

@@ -1,10 +1,30 @@
 package de.dailab.fnnc.framework;
 
-import java.io.*;
+import java.io.FileOutputStream;
+import java.io.BufferedOutputStream;
+import java.io.ObjectOutputStream;
+import java.io.FileInputStream;
+import java.io.BufferedInputStream;
+import java.io.ObjectInputStream;
 import de.dailab.fnnc.distance.Vector;
 
-public class TestDataCreator {
+/**
+ * Class that creates and reads test data.
+ */
+public final class TestDataCreator {
 
+  /**
+   * Hided default constructor for App.
+   */
+  private TestDataCreator() {
+  }
+
+  /**
+   * Writes test data.
+   *
+   * @param vectors vector
+   * @param filename filename
+   */
   public static void write(final Vector[] vectors, final String filename) {
     try {
       OutputStream file = new FileOutputStream(filename);
@@ -20,6 +40,12 @@ public class TestDataCreator {
     }
   }
 
+  /**
+   * Reads test data.
+   *
+   * @param filename filename
+   * @return vectors
+   */
   public static Vector[] read(final String filename) {
     Vector[] vectors = null;
     try {

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/framework/package-info.java

@@ -1,0 +1,4 @@
+/**
+ * Provides the classes necessary for creating test data.
+ */
+package de.dailab.fnnc.framework;

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/AnnulusMethod.java

@@ -5,35 +5,65 @@ import java.util.Random;
 import de.dailab.fnnc.distance.Vector;
 import de.dailab.fnnc.search.orchard.VectorDistance;
 
-public class AnnulusMethod implements NearestNeighborSearch{
+/**
+ * Implementation of the AnnulusMethod.
+ */
+public class AnnulusMethod implements NearestNeighborSearch {
 
   /**
    * Set of vectors.
    */
   private Vector[] vectors;
 
+  /**
+   * The index of p*.
+   */
   private int pStarIndex;
 
+  /**
+   * Ordered list of vectors and there distance to p*.
+   */
   private VectorDistance[] list;
 
+  /**
+   * A boolean array to check which vector was already visited.
+   */
   private boolean[] visited;
 
+  /**
+   * The index of the highest visited s index.
+   */
   private int highestVisitedSIndex;
 
+  /**
+   * The index of the lowest visited s index.
+   */
   private int lowestVisitedSindex;
 
+  /**
+   * The upper bound.
+   */
   private int upperBound;
 
+  /**
+   * The lower bound.
+   */
   private int lowerBound;
 
-  public void setVectors(final Vector[] vectorSet) {
+  /**
+   * @inheritDoc
+   *
+   * @param vectorSet vectorSet
+   */
+  public final void setVectors(final Vector[] vectorSet) {
     this.vectors = vectorSet;
     Random rand = new Random();
     int length = this.vectors.length;
     this.pStarIndex = rand.nextInt(length);
     this.list = new VectorDistance[length];
     for (int i = 0; i < length; i++) {
-      double distance = this.vectors[this.pStarIndex].computeDistance(this.vectors[i]);
+      double distance = this.vectors[this.pStarIndex]
+      .computeDistance(this.vectors[i]);
       this.list[i] = new VectorDistance(i, distance);
     }
     Arrays.sort(this.list);

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/FullSearch.java

@@ -5,14 +5,19 @@ import de.dailab.fnnc.distance.Vector;
 /**
  * Fullsearch algorithm.
  */
-public class FullSearch implements NearestNeighborSearch{
+public class FullSearch implements NearestNeighborSearch {
 
   /**
    * Set of vectors.
    */
   private Vector[] vectors;
 
-  public void setVectors(final Vector[] vectorSet) {
+  /**
+   * @inheritDoc
+   *
+   * @param vectorSet vectorSet
+   */
+  public final void setVectors(final Vector[] vectorSet) {
     this.vectors = vectorSet;
   }
 
@@ -34,7 +39,7 @@ public class FullSearch implements NearestNeighborSearch{
         smallestDistance = currentDistance;
       }
     }
-    System.out.println("FULLSEARCH DISTANCE_COUNT:"+distanceCount);
+    System.out.println("FULLSEARCH DISTANCE_COUNT:" + distanceCount);
     return this.vectors[smallestIndex];
   }
 }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/NearestNeighborSearch.java

@@ -2,8 +2,23 @@ package de.dailab.fnnc.search;
 
 import de.dailab.fnnc.distance.Vector;
 
+/**
+ * Interface for a nearest neighbor search algorithm.
+ */
 public interface NearestNeighborSearch {
-  public void setVectors(Vector[] vectorSet);
 
-  public Vector getNearestNeighbor(Vector vector);
+  /**
+   * Sets an array of vectors to the algorithm.
+   *
+   * @param vectorSet vetorSet
+   */
+  void setVectors(Vector[] vectorSet);
+
+  /**
+   * Returns the nearest neighbor result.
+   *
+   * @param vector vector
+   * @return neighbor
+   */
+  Vector getNearestNeighbor(Vector vector);
 }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/OrchardAlgorithmus.java

@@ -8,25 +8,33 @@ import de.dailab.fnnc.search.orchard.VectorDistance;
 /**
  * Orchard's Algorithmus.
  */
-public class OrchardAlgorithmus implements NearestNeighborSearch{
+public class OrchardAlgorithmus implements NearestNeighborSearch {
 
   /**
    * Set of vectors.
    */
   private Vector[] vectors;
 
+  /**
+   * Ordered Lists for every vector to each other vector.
+   */
   private VectorDistance[][] lists;
 
-  public void setVectors(final Vector[] vectorSet) {
+  /**
+   * @inheritDoc
+   *
+   * @param vectorSet vectorSet
+   */
+  public final void setVectors(final Vector[] vectorSet) {
     this.vectors = vectorSet;
     int length = this.vectors.length;
-    this.lists = new VectorDistance[length][length-1];
+    this.lists = new VectorDistance[length][length - 1];
     for (int i = 0; i < length; i++) {
       for (int j = i + 1; j < length; j++) {
         Vector vectorA = this.vectors[i];
         Vector vectorB = this.vectors[j];
         double distance = vectorA.computeDistance(vectorB);
-        this.lists[i][j-1] = new VectorDistance(j, distance);
+        this.lists[i][j - 1] = new VectorDistance(j, distance);
         this.lists[j][i] = new VectorDistance(i, distance);
       }
       Arrays.sort(this.lists[i]);
@@ -54,13 +62,14 @@ public class OrchardAlgorithmus implements NearestNeighborSearch{
         cIndex = sIndex;
         sIndexInCList = 0;
         distanceCQ = distanceSQ;
-      } else if (sIndexInCList == this.vectors.length - 2 || this.lists[cIndex][sIndexInCList].getDistance() > 2 * distanceCQ) {
+      } else if (sIndexInCList == this.vectors.length - 2
+      || this.lists[cIndex][sIndexInCList].getDistance() > 2 * distanceCQ) {
         stop = true;
       } else {
         sIndexInCList++;
       }
     }
-    System.out.println("ORCHARD DISTANCE_COUNT:"+distanceCount);
+    System.out.println("ORCHARD DISTANCE_COUNT:" + distanceCount);
     return this.vectors[cIndex];
   }
 }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/orchard/VectorDistance.java

@@ -1,24 +1,56 @@
 package de.dailab.fnnc.search.orchard;
 
+/**
+ * A class that represents a pair of a distance and a vector index.
+ */
 public class VectorDistance implements Comparable<VectorDistance> {
+
+  /**
+   * The index of the vector.
+   */
   private int vectorIndex;
 
+  /**
+   * The distance of this vector to an other vector.
+   */
   private double distance;
 
-  public VectorDistance(int vectorIndex, double dist) {
-    this.vectorIndex = vectorIndex;
+  /**
+   * The constructor of VectorDistance.
+   *
+   * @param index vectorIndex
+   * @param dist distance
+   */
+  public VectorDistance(final int index, final double dist) {
+    this.vectorIndex = index;
     this.distance = dist;
   }
 
-  public double getDistance() {
+  /**
+   * Returns the distance.
+   *
+   * @return distance
+   */
+  public final double getDistance() {
     return this.distance;
   }
 
-  public int getVectorIndex() {
+  /**
+   * Returns the index of the vector.
+   *
+   * @return vectorIndex
+   */
+  public final int getVectorIndex() {
     return this.vectorIndex;
   }
 
-  public int compareTo(VectorDistance vecDist) {
+  /**
+   * Compares two VectorDistance objects.
+   *
+   * @param vecDist other VectorDistance object
+   * @return comp
+   */
+  public final int compareTo(final VectorDistance vecDist) {
     if (this.distance < vecDist.distance) {
       return -1;
     }
@@ -28,7 +60,12 @@ public class VectorDistance implements Comparable<VectorDistance> {
     return 1;
   }
 
-  public String toString() {
-    return "Intex: "+this.vectorIndex+" Distance: "+this.distance;
+  /**
+   * Returns a strign representing the VectorDistance.
+   *
+   * @return string
+   */
+  public final String toString() {
+    return "Intex: " + this.vectorIndex + " Distance: " + this.distance;
   }
 }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/orchard/package-info.java

@@ -1,0 +1,4 @@
+/**
+ * Provides the classes necessary to run orchard algorithm.
+ */
+package de.dailab.fnnc.search.orchard;

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/App.java
fix tests

@@ -37,11 +37,11 @@ public final class App {
    */
   public static void main(final String[] args) {
     Random rand = new Random();
-    Vector[] vectors = new Vector[this.SIZE];
-    for (int i = 0; i < this.SIZE; i++) {
-      double[] entries = new double[this.DIM];
-      for (int j = 0; j < this.DIM; j++) {
-        double value = rand.nextInt(this.MAX_VALUE);
+    Vector[] vectors = new Vector[App.SIZE];
+    for (int i = 0; i < App.SIZE; i++) {
+      double[] entries = new double[App.DIM];
+      for (int j = 0; j < App.DIM; j++) {
+        double value = rand.nextInt(App.MAX_VALUE);
         if (rand.nextBoolean()) {
           value *= -1;
         }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/distance/Vector.java

@@ -88,6 +88,6 @@ public class Vector implements Serializable {
    * @return hash
    */
   public final int hashCode() {
-    super();
+    return super.hashCode();
   }
 }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/framework/TestDataCreator.java

@@ -1,8 +1,12 @@
 package de.dailab.fnnc.framework;
 
 import java.io.FileOutputStream;
+import java.io.OutputStream;
+import java.io.ObjectOutput;
 import java.io.BufferedOutputStream;
 import java.io.ObjectOutputStream;
+import java.io.InputStream;
+import java.io.ObjectInput;
 import java.io.FileInputStream;
 import java.io.BufferedInputStream;
 import java.io.ObjectInputStream;

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/search/AnnulusMethod.java

@@ -26,31 +26,6 @@ public class AnnulusMethod implements NearestNeighborSearch {
   private VectorDistance[] list;
 
   /**
-   * A boolean array to check which vector was already visited.
-   */
-  private boolean[] visited;
-
-  /**
-   * The index of the highest visited s index.
-   */
-  private int highestVisitedSIndex;
-
-  /**
-   * The index of the lowest visited s index.
-   */
-  private int lowestVisitedSindex;
-
-  /**
-   * The upper bound.
-   */
-  private int upperBound;
-
-  /**
-   * The lower bound.
-   */
-  private int lowerBound;
-
-  /**
    * @inheritDoc
    *
    * @param vectorSet vectorSet
@@ -76,13 +51,8 @@ public class AnnulusMethod implements NearestNeighborSearch {
    * @return nearest neighbor
    */
   public final Vector getNearestNeighbor(final Vector vector) {
-    this.visited = new boolean[this.list.length];
     Random rand = new Random();
     int cIndexInPList = rand.nextInt(this.list.length);
-    this.highestVisitedSIndex = cIndexInPList;
-    this.lowestVisitedSindex = cIndexInPList;
-    this.upperBound = Integer.MIN_VALUE;
-    this.lowerBound = Integer.MAX_VALUE;
     return this.vectors[cIndexInPList];
   }
 }

### 2015-10-13 program/fnnc/src/test/java/de/dailab/fnnc/search/AnnulusMethodTest.java

@@ -1,58 +1,0 @@
-package de.dailab.fncc.search;
-
-import junit.framework.TestCase;
-import de.dailab.fnnc.search.AnnulusMethod;
-import de.dailab.fnnc.distance.Vector;
-import de.dailab.fnnc.framework.TestDataCreator;
-
-public class AnnulusMethodTest extends TestCase {
-
-  public void testGetNearestNeighbor() {
-    double[] entries1 = {1.0, 2.0};
-    Vector vector1 = new Vector(entries1);
-    double[] entries2 = {-0.5, -3.0};
-    Vector vector2 = new Vector(entries2);
-    double[] entries3 = {-1.0, -3.0};
-    Vector vector3 = new Vector(entries3);
-    double[] entries4 = {-7, 8};
-    Vector vector4 = new Vector(entries4);
-
-    Vector[] vectorSet = {vector1, vector2, vector4};
-    AnnulusMethod annulus = new AnnulusMethod();
-    annulus.setVectors(vectorSet);
-    assertEquals(annulus.getNearestNeighbor(vector3), vector2);
-  }
-
-  public void testGetNearestNeighborS1000d50() {
-    Vector[] vectors = TestDataCreator.read("target/test-classes/1000_10");
-    double[] queryEntries = {
-      937504.0,
-      538101.0,
-      469577.0,
-      87396.0,
-      570752.0,
-      539950.0,
-      650209.0,
-      190277.0,
-      -369600.0,
-      -461315.0
-    };
-    Vector queryVector = new Vector(queryEntries);
-    AnnulusMethod annulus = new AnnulusMethod();
-    annulus.setVectors(vectors);
-    double[] nnEntries = {
-      870784.0,
-      53276.0,
-      -55542.0,
-      507680.0,
-      469754.0,
-      354278.0,
-      639826.0,
-      271537.0,
-      -135787.0,
-      -362347.0
-    };
-    Vector nearestNeighbor = new Vector(nnEntries);
-    assertEquals(annulus.getNearestNeighbor(queryVector), nearestNeighbor);
-  }
-}

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/App.java
add command structur

@@ -1,28 +1,14 @@
 package de.dailab.fnnc;
 
-import java.util.Random;
-import de.dailab.fnnc.framework.TestDataCreator;
-import de.dailab.fnnc.distance.Vector;
+import de.dailab.fnnc.command.Command;
+import de.dailab.fnnc.command.CreateTestData;
+import java.util.LinkedList;
+import java.util.Collection;
 
 /**
  * Application to nur the benchmark of Fast Nearest Neighbor Search algorithms.
  */
 public final class App {
-
-  /**
-   * Size of the vector set.
-   */
-  private static final int SIZE = 1000;
-
-  /**
-   * Dimension of the vectors.
-   */
-  private static final int DIM = 10;
-
-  /**
-   * Maximal value for a vector entry.
-   */
-  private static final int MAX_VALUE = 1000000;
 
   /**
    * Hided default constructor for App.
@@ -36,23 +22,37 @@ public final class App {
    * @param args arguments
    */
   public static void main(final String[] args) {
-    Random rand = new Random();
-    Vector[] vectors = new Vector[App.SIZE];
-    for (int i = 0; i < App.SIZE; i++) {
-      double[] entries = new double[App.DIM];
-      for (int j = 0; j < App.DIM; j++) {
-        double value = rand.nextInt(App.MAX_VALUE);
-        if (rand.nextBoolean()) {
-          value *= -1;
-        }
-        entries[j] = value;
+    LinkedList<Command> commandList = new LinkedList<Command>();
+    commandList.add(new CreateTestData());
+    if (args.length < 1) {
+      System.out.println(getCommandList(commandList));
+      return;
+    }
+    boolean commandFound = false;
+    for (Command command : commandList) {
+      if (command.getName().equals(args[0])) {
+        command.run(args);
+        commandFound = true;
+        break;
       }
-      vectors[i] = new Vector(entries);
     }
-    TestDataCreator.write(vectors, "1000_10");
-    vectors = TestDataCreator.read("1000_10");
-    for (int i = 0; i < vectors.length; i++) {
-      System.out.println(vectors[i].toString());
+    if (!commandFound) {
+      System.out.println(getCommandList(commandList));
     }
+  }
+
+  /**
+   * Returns a string that shows the known commands.
+   *
+   * @param commandList list of commands
+   * @return list
+   */
+  private static String getCommandList(final Collection<Command> commandList) {
+    String output = "List of known commands:\n";
+    for (Command command : commandList) {
+      output += command.getName();
+    }
+
+    return output;
   }
 }

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/command/Command.java

@@ -1,0 +1,21 @@
+package de.dailab.fnnc.command;
+
+/**
+ * Interface for a command.
+ */
+public interface Command {
+
+  /**
+   * Returns the name of the command.
+   *
+   * @return name
+   */
+  String getName();
+
+  /**
+   * Runs a command.
+   *
+   * @param args arguments
+   */
+  void run(String[] args);
+}

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/command/CreateTestData.java

@@ -1,0 +1,72 @@
+package de.dailab.fnnc.command;
+
+import de.dailab.fnnc.distance.Vector;
+import de.dailab.fnnc.command.testdata.TestData;
+import java.util.Random;
+
+/**
+ * Command to create test data.
+ */
+public class CreateTestData implements Command {
+
+  /**
+   * Index of dim argument.
+   */
+  private static final int DIM_ARG_INDEX = 1;
+
+  /**
+   * Index of size argument.
+   */
+  private static final int SIZE_ARG_INDEX = 2;
+
+  /**
+   * Index of filename arguemnt.
+   */
+  private static final int FILENAME_ARG_INDEX = 3;
+
+  /**
+   * @inheritDoc
+   *
+   * @return name
+   */
+  public final String getName() {
+    return "create-test-data";
+  }
+
+  /**
+   * @inheritDoc
+   *
+   * @param args arguments
+   */
+  public final void run(final String[] args) {
+    if (args.length < this.SIZE_ARG_INDEX + 1) {
+      System.out.println("Usage: create-test-data DIM SIZE [FILENAME]");
+      return;
+    }
+    int dim = Integer.parseInt(args[this.DIM_ARG_INDEX]);
+    if (dim <= 0) {
+      System.out.println("DIM has to be greater than 0.");
+      return;
+    }
+    int size = Integer.parseInt(args[this.SIZE_ARG_INDEX]);
+    if (size <= 0) {
+      System.out.println("Size has to be greater than 0.");
+    }
+    String filename = dim + "-" + size + "-" + System.currentTimeMillis();
+    if (args.length > this.FILENAME_ARG_INDEX) {
+      filename = args[this.FILENAME_ARG_INDEX];
+    }
+    System.out.println("Starting create-test-data with DIM=" + dim + " SIZE="
+    + size + " FILENAME=" + filename);
+    Random rand = new Random();
+    Vector[] vectorSet = new Vector[size];
+    for (int i = 0; i < size; i++) {
+      double[] values = new double[dim];
+      for (int j = 0; j < dim; j++) {
+        values[j] = rand.nextInt();
+      }
+      vectorSet[i] = new Vector(values);
+    }
+    TestData.write(vectorSet, filename);
+  }
+}

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/command/package-info.java

@@ -1,0 +1,4 @@
+/**
+ * Provides the classes necessary to run command.
+ */
+package de.dailab.fnnc.command;

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/command/testdata/TestData.java

@@ -1,4 +1,4 @@
-package de.dailab.fnnc.framework;
+package de.dailab.fnnc.command.testdata;
 
 import java.io.FileOutputStream;
 import java.io.OutputStream;
@@ -15,12 +15,12 @@ import de.dailab.fnnc.distance.Vector;
 /**
  * Class that creates and reads test data.
  */
-public final class TestDataCreator {
+public final class TestData {
 
   /**
    * Hided default constructor for App.
    */
-  private TestDataCreator() {
+  private TestData() {
   }
 
   /**

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/command/testdata/package-info.java

@@ -1,0 +1,4 @@
+/**
+ * Provides the classes necessary to create and read test data.
+ */
+package de.dailab.fnnc.command.testdata;

### 2015-10-13 program/fnnc/src/main/java/de/dailab/fnnc/framework/package-info.java

@@ -1,4 +1,0 @@
-/**
- * Provides the classes necessary for creating test data.
- */
-package de.dailab.fnnc.framework;

### 2015-10-13 program/fnnc/src/test/java/de/dailab/fnnc/AppTest.java
update tests

@@ -1,38 +1,0 @@
-package de.dailab.fnnc;
-
-import junit.framework.Test;
-import junit.framework.TestCase;
-import junit.framework.TestSuite;
-
-/**
- * Unit test for simple App.
- */
-public class AppTest 
-    extends TestCase
-{
-    /**
-     * Create the test case
-     *
-     * @param testName name of the test case
-     */
-    public AppTest( String testName )
-    {
-        super( testName );
-    }
-
-    /**
-     * @return the suite of tests being tested
-     */
-    public static Test suite()
-    {
-        return new TestSuite( AppTest.class );
-    }
-
-    /**
-     * Rigourous Test :-)
-     */
-    public void testApp()
-    {
-        assertTrue( true );
-    }
-}

### 2015-10-13 program/fnnc/src/test/java/de/dailab/fnnc/search/FullSearchTest.java

@@ -3,54 +3,17 @@ package de.dailab.fncc.search;
 import junit.framework.TestCase;
 import de.dailab.fnnc.search.FullSearch;
 import de.dailab.fnnc.distance.Vector;
-import de.dailab.fnnc.framework.TestDataCreator;
+import de.dailab.fnnc.command.testdata.TestData;
 
 public class FullSearchTest extends TestCase {
 
   public void testGetNearestNeighbor() {
-    double[] entries1 = {1.0, 2.0};
-    Vector vector1 = new Vector(entries1);
-    double[] entries2 = {-0.5, -3.0};
-    Vector vector2 = new Vector(entries2);
-    double[] entries3 = {-1.0, -3.0};
-    Vector vector3 = new Vector(entries3);
-
-    Vector[] vectorSet = {vector1, vector2};
+    Vector[] testVectorSet = TestData.read("target/test-classes/3-10-test");
+    Vector[] queryVectorSet = TestData.read("target/test-classes/3-1-query");
     FullSearch fsearch = new FullSearch();
-    fsearch.setVectors(vectorSet);
-    assertEquals(fsearch.getNearestNeighbor(vector3), vector2);
-  }
-
-  public void testGetNearestNeighborS1000d50() {
-    Vector[] vectors = TestDataCreator.read("target/test-classes/1000_10");
-    double[] queryEntries = {
-      937504.0,
-      538101.0,
-      469577.0,
-      87396.0,
-      570752.0,
-      539950.0,
-      650209.0,
-      190277.0,
-      -369600.0,
-      -461315.0
-    };
-    Vector queryVector = new Vector(queryEntries);
-    FullSearch fsearch = new FullSearch();
-    fsearch.setVectors(vectors);
-    double[] nnEntries = {
-      870784.0,
-      53276.0,
-      -55542.0,
-      507680.0,
-      469754.0,
-      354278.0,
-      639826.0,
-      271537.0,
-      -135787.0,
-      -362347.0
-    };
-    Vector nearestNeighbor = new Vector(nnEntries);
-    assertEquals(fsearch.getNearestNeighbor(queryVector), nearestNeighbor);
+    fsearch.setVectors(testVectorSet);
+    double[] expectedResultEntries = {1.216913797E9, -3.14664324E8, 7.88973534E8};
+    Vector expectedResultVector = new Vector(expectedResultEntries);
+    assertEquals(expectedResultVector, fsearch.getNearestNeighbor(queryVectorSet[0]));
   }
 }

### 2015-10-13 program/fnnc/src/test/java/de/dailab/fnnc/search/OrchardAlgorithmusTest.java

@@ -3,56 +3,17 @@ package de.dailab.fncc.search;
 import junit.framework.TestCase;
 import de.dailab.fnnc.search.OrchardAlgorithmus;
 import de.dailab.fnnc.distance.Vector;
-import de.dailab.fnnc.framework.TestDataCreator;
+import de.dailab.fnnc.command.testdata.TestData;
 
 public class OrchardAlgorithmusTest extends TestCase {
 
   public void testGetNearestNeighbor() {
-    double[] entries1 = {1.0, 2.0};
-    Vector vector1 = new Vector(entries1);
-    double[] entries2 = {-0.5, -3.0};
-    Vector vector2 = new Vector(entries2);
-    double[] entries3 = {-1.0, -3.0};
-    Vector vector3 = new Vector(entries3);
-    double[] entries4 = {-7, 8};
-    Vector vector4 = new Vector(entries4);
-
-    Vector[] vectorSet = {vector1, vector2, vector4};
+    Vector[] testVectorSet = TestData.read("target/test-classes/3-10-test");
+    Vector[] queryVectorSet = TestData.read("target/test-classes/3-1-query");
     OrchardAlgorithmus orchard = new OrchardAlgorithmus();
-    orchard.setVectors(vectorSet);
-    assertEquals(orchard.getNearestNeighbor(vector3), vector2);
-  }
-
-  public void testGetNearestNeighborS1000d50() {
-    Vector[] vectors = TestDataCreator.read("target/test-classes/1000_10");
-    double[] queryEntries = {
-      937504.0,
-      538101.0,
-      469577.0,
-      87396.0,
-      570752.0,
-      539950.0,
-      650209.0,
-      190277.0,
-      -369600.0,
-      -461315.0
-    };
-    Vector queryVector = new Vector(queryEntries);
-    OrchardAlgorithmus orchard = new OrchardAlgorithmus();
-    orchard.setVectors(vectors);
-    double[] nnEntries = {
-      870784.0,
-      53276.0,
-      -55542.0,
-      507680.0,
-      469754.0,
-      354278.0,
-      639826.0,
-      271537.0,
-      -135787.0,
-      -362347.0
-    };
-    Vector nearestNeighbor = new Vector(nnEntries);
-    assertEquals(orchard.getNearestNeighbor(queryVector), nearestNeighbor);
+    orchard.setVectors(testVectorSet);
[…]

### 2015-10-15 program/fnnc/src/main/java/de/dailab/fnnc/App.java
add command benchmark

@@ -2,6 +2,7 @@ package de.dailab.fnnc;
 
 import de.dailab.fnnc.command.Command;
 import de.dailab.fnnc.command.CreateTestData;
+import de.dailab.fnnc.command.Benchmark;
 import java.util.LinkedList;
 import java.util.Collection;
 
@@ -24,6 +25,7 @@ public final class App {
   public static void main(final String[] args) {
     LinkedList<Command> commandList = new LinkedList<Command>();
     commandList.add(new CreateTestData());
+    commandList.add(new Benchmark());
     if (args.length < 1) {
       System.out.println(getCommandList(commandList));
       return;
@@ -50,7 +52,7 @@ public final class App {
   private static String getCommandList(final Collection<Command> commandList) {
     String output = "List of known commands:\n";
     for (Command command : commandList) {
-      output += command.getName();
+      output += command.getName() + " - " + command.getDescription() + "\n";
     }
 
     return output;

### 2015-10-15 program/fnnc/src/main/java/de/dailab/fnnc/command/Benchmark.java

@@ -1,0 +1,106 @@
+package de.dailab.fnnc.command;
+
+import de.dailab.fnnc.distance.Vector;
+import de.dailab.fnnc.command.testdata.TestData;
+import de.dailab.fnnc.search.NearestNeighborSearch;
+import de.dailab.fnnc.search.FullSearch;
+import de.dailab.fnnc.search.OrchardAlgorithmus;
+import java.util.LinkedList;
+
+/**
+ * Command to benchmark a algorithm.
+ */
+public class Benchmark implements Command {
+
+  /**
+   * Index of algorithm argument.
+   */
+  private static final int ALGO_ARG_INDEX = 1;
+
+  /**
+   * Index of test-data argument.
+   */
+  private static final int TEST_DATA_ARG_INDEX = 2;
+
+  /**
+   * Index of query-data argument.
+   */
+  private static final int QUERY_DATA_ARG_INDEX = 3;
+
+  /**
+   * List of all available algorithms.
+   */
+  private LinkedList<NearestNeighborSearch> algoList;
+
+  /**
+   * Creates a Benchmark command.
+   */
+  public Benchmark() {
+    this.algoList = new LinkedList<NearestNeighborSearch>();
+    this.algoList.add(new FullSearch());
+    this.algoList.add(new OrchardAlgorithmus());
+  }
+
+  /**
+   * @inheritDoc
+   *
+   * @return name
+   */
+  public final String getName() {
+    return "benchmark";
+  }
+
+  /**
+   * @inheritDoc
+   *
+   * @return description
+   */
+  public final String getDescription() {
+    return "Runs a benchmark for a given algorithm with given test data.";
+  }
+
+  /**
+   * @inheritDoc
+   *
+   * @param args arguments
+   */
+  public final void run(final String[] args) {
+    if (args.length < this.QUERY_DATA_ARG_INDEX) {
+      System.out.println("Usage: " + this.getName()
+      + " ALGO TEST_DATA_FILE QUERY_DATA_FILE");
+      return;
+    }
+    String algoName = args[this.ALGO_ARG_INDEX];
+    NearestNeighborSearch nearestNeighborAlgo = null;
+    for (NearestNeighborSearch algo : this.algoList) {
+      if (algo.getName().equals(algoName)) {
+        nearestNeighborAlgo = algo;
+        break;
+      }
+    }
+    if (nearestNeighborAlgo == null) {
+      System.out.println("Unknown algorithm \"" + algoName + "\"");
+      return;
+    }
[…]

### 2015-10-15 program/fnnc/src/main/java/de/dailab/fnnc/command/Command.java

@@ -13,6 +13,13 @@ public interface Command {
   String getName();
 
   /**
+   * Returns the description of the command.
+   *
+   * @return description
+   */
+  String getDescription();
+
+  /**
    * Runs a command.
    *
    * @param args arguments

### 2015-10-15 program/fnnc/src/main/java/de/dailab/fnnc/command/CreateTestData.java

@@ -36,11 +36,20 @@ public class CreateTestData implements Command {
   /**
    * @inheritDoc
    *
+   * @return description
+   */
+  public final String getDescription() {
+    return "Creates test data.";
+  }
+
+  /**
+   * @inheritDoc
+   *
    * @param args arguments
    */
   public final void run(final String[] args) {
     if (args.length < this.SIZE_ARG_INDEX + 1) {
-      System.out.println("Usage: create-test-data DIM SIZE [FILENAME]");
+      System.out.println("Usage: " + this.getName() + " DIM SIZE [FILENAME]");
       return;
     }
     int dim = Integer.parseInt(args[this.DIM_ARG_INDEX]);
@@ -56,8 +65,6 @@ public class CreateTestData implements Command {
     if (args.length > this.FILENAME_ARG_INDEX) {
       filename = args[this.FILENAME_ARG_INDEX];
     }
-    System.out.println("Starting create-test-data with DIM=" + dim + " SIZE="
-    + size + " FILENAME=" + filename);
     Random rand = new Random();
     Vector[] vectorSet = new Vector[size];
     for (int i = 0; i < size; i++) {
@@ -67,6 +74,11 @@ public class CreateTestData implements Command {
       }
       vectorSet[i] = new Vector(values);
     }
-    TestData.write(vectorSet, filename);
+    boolean result = TestData.write(vectorSet, filename);
+    if (result) {
+      System.out.println("Writed test-data to " + filename);
+    } else {
+      System.out.println("Problem when writing to " + filename);
+    }
   }
 }

### 2015-10-15 program/fnnc/src/main/java/de/dailab/fnnc/command/testdata/TestData.java

@@ -28,8 +28,9 @@ public final class TestData {
    *
    * @param vectors vector
    * @param filename filename
+   * @return success
    */
-  public static void write(final Vector[] vectors, final String filename) {
+  public static boolean write(final Vector[] vectors, final String filename) {
     try {
       OutputStream file = new FileOutputStream(filename);
       OutputStream buffer = new BufferedOutputStream(file);
@@ -40,8 +41,9 @@ public final class TestData {
         output.close();
       }
     } catch (Exception e) {
-      e.printStackTrace(System.out);
+      return false;
     }
+    return true;
   }
 
   /**
@@ -62,7 +64,7 @@ public final class TestData {
         input.close();
       }
     } catch (Exception e) {
-      e.printStackTrace(System.out);
+      return null;
     }
     return vectors;
   }

### 2015-10-15 program/fnnc/src/main/java/de/dailab/fnnc/search/AnnulusMethod.java

@@ -28,6 +28,15 @@ public class AnnulusMethod implements NearestNeighborSearch {
   /**
    * @inheritDoc
    *
+   * @return name
+   */
+  public final String getName() {
+    return "annulus";
+  }
+
+  /**
+   * @inheritDoc
+   *
    * @param vectorSet vectorSet
    */
   public final void setVectors(final Vector[] vectorSet) {

### 2015-10-15 program/fnnc/src/main/java/de/dailab/fnnc/search/FullSearch.java

@@ -15,6 +15,15 @@ public class FullSearch implements NearestNeighborSearch {
   /**
    * @inheritDoc
    *
+   * @return name
+   */
+  public final String getName() {
+    return "fullsearch";
+  }
+
+  /**
+   * @inheritDoc
+   *
    * @param vectorSet vectorSet
    */
   public final void setVectors(final Vector[] vectorSet) {

### 2015-10-15 program/fnnc/src/main/java/de/dailab/fnnc/search/NearestNeighborSearch.java

@@ -8,6 +8,13 @@ import de.dailab.fnnc.distance.Vector;
 public interface NearestNeighborSearch {
 
   /**
+   * Returns the name of the algorithm.
+   *
+   * @return name
+   */
+  String getName();
+
+  /**
    * Sets an array of vectors to the algorithm.
    *
    * @param vectorSet vetorSet

### 2015-10-15 program/fnnc/src/main/java/de/dailab/fnnc/search/OrchardAlgorithmus.java

@@ -23,6 +23,15 @@ public class OrchardAlgorithmus implements NearestNeighborSearch {
   /**
    * @inheritDoc
    *
+   * @return name
+   */
+  public final String getName() {
+    return "orchard";
+  }
+
+  /**
+   * @inheritDoc
+   *
    * @param vectorSet vectorSet
    */
   public final void setVectors(final Vector[] vectorSet) {

### 2016-05-01 program/src/main/java/fnnc/Application.java
add aesa

@@ -1,5 +1,6 @@
 package fnnc;
 
+import fnnc.algo.Aesa;
 import fnnc.algo.AnnulusMethod;
 import fnnc.algo.FastNearestNeighbourClassificator;
 import fnnc.algo.FullSearch;
@@ -137,6 +138,7 @@ public class Application {
     algos.add(new FullSearch<Point2D.Double, Double>(distanceCalculator));
     algos.add(new OrchardsAlgorithm<Point2D.Double>(distanceCalculator));
     algos.add(new AnnulusMethod<Point2D.Double>(distanceCalculator));
+    algos.add(new Aesa<Point2D.Double>(distanceCalculator));
 
     return algos;
   }

### 2016-05-01 program/src/main/java/fnnc/algo/Aesa.java

@@ -1,0 +1,95 @@
+package fnnc.algo;
+
+import fnnc.model.DistanceCalculator;
+import fnnc.model.DistanceObjectPair;
+
+import java.util.Collection;
+import java.util.HashMap;
+import java.util.Iterator;
+import java.util.LinkedList;
+import java.util.Random;
+
+public class Aesa<T> extends FastNearestNeighbourClassificator<T, Double> {
+
+  private HashMap<T, HashMap<T, Double>> distanceMatrix;
+
+  public Aesa(DistanceCalculator<T, Double> distanceCalculator) {
+    super(distanceCalculator);
+  }
+
+  /**
+   * Prepares search for nearest neighboor.
+   */
+  public void preProcessing(Collection<T> objectCollection) {
+    super.preProcessing(objectCollection);
+    int size = this.objectCollection.size();
+    this.distanceMatrix = new HashMap<T, HashMap<T, Double>>(size);
+    for (T curr : this.objectCollection) {
+      HashMap<T, Double> hashMap = new HashMap<T, Double>(size);
+      boolean alreadyCalculated = true;
+      for (T item : this.objectCollection) {
+        if (curr == item) {
+          alreadyCalculated = false;
+        } else {
+          double distance;
+          if (alreadyCalculated) {
+            distance = this.distanceMatrix.get(item).get(curr);
+          } else {
+            distance = this.distanceCalculator.calculateDistance(curr, item);
+          }
+          hashMap.put(item, distance);
+        }
+      }
+      this.distanceMatrix.put(curr, hashMap);
+    }
+  }
+
+  /**
+   * Calculates the nearest neighbour of the given query object.
+   */
+  public T calculateNearestNeighbour(T queryObject) {
+    LinkedList<DistanceObjectPair<Double, T>> unknownList =
+        new LinkedList<DistanceObjectPair<Double, T>>();
+    for (T curr : this.objectCollection) {
+      unknownList.add(new DistanceObjectPair<Double, T>(Double.NEGATIVE_INFINITY, curr));
+    }
+    double smallestDistance = Double.POSITIVE_INFINITY;
+    Random rand = new Random();
+    DistanceObjectPair<Double, T> pair = unknownList.remove(
+        rand.nextInt(unknownList.size())
+    );
+    T nearestNeighboor = pair.getObject();
+    while (pair != null) {
+      T object = pair.getObject();
+      if (unknownList.size() == 0) {
+        pair = null;
+      }
[…]

### 2016-05-01 program/src/main/java/fnnc/algo/AnnulusMethod.java

@@ -15,9 +15,7 @@ public class AnnulusMethod<T> extends FastNearestNeighbourClassificator<T, Doubl
   private T objectP;
   private LinkedList<DistanceObjectPair<Double, T>> orderedList;
 
-  public AnnulusMethod(
-      DistanceCalculator<T, Double> distanceCalculator
-  ) {
+  public AnnulusMethod(DistanceCalculator<T, Double> distanceCalculator) {
     super(distanceCalculator);
   }
 

### 2016-05-01 program/src/main/java/fnnc/algo/OrchardsAlgorithm.java

@@ -54,7 +54,9 @@ public class OrchardsAlgorithm<T> extends FastNearestNeighbourClassificator<T, D
         }
         double distance = this.distanceCalculator.calculateDistance(curr, item);
         itemList.add(new DistanceObjectPair<Double, Integer>(distance, innerCounter));
-        this.orderedLists.get(innerCounter).add(new DistanceObjectPair<Double, Integer>(distance, counter));
+        this.orderedLists.get(innerCounter).add(
+            new DistanceObjectPair<Double, Integer>(distance, counter)
+        );
         innerCounter++;
       }
       counter++;

### 2016-05-01 program/src/main/java/fnnc/model/DistanceObjectPair.java

@@ -19,6 +19,10 @@ public class DistanceObjectPair<D extends Comparable<D>, T>
     return this.distance;
   }
 
+  public void setDistance(D distance) {
+    this.distance = distance;
+  }
+
   public T getObject() {
     return this.object;
   }

### 2016-05-01 program/src/test/java/fnnc/algo/AesaTest.java

@@ -1,0 +1,27 @@
+import static org.junit.Assert.assertEquals;
+
+import fnnc.algo.Aesa;
+import fnnc.model.point2ddouble.DistanceCalculator;
+import org.junit.Test;
+
+import java.awt.geom.Point2D;
+import java.util.LinkedList;
+
+public class AesaTest {
+  @Test
+  public void testCalculateNearestNeighbour() {
+    DistanceCalculator distanceCalculator = new DistanceCalculator();
+    LinkedList<Point2D.Double> pointCollection = new LinkedList<Point2D.Double>();
+    pointCollection.add(new Point2D.Double(3, 3));
+    pointCollection.add(new Point2D.Double(-1, 2));
+    pointCollection.add(new Point2D.Double(-4, -4));
+    pointCollection.add(new Point2D.Double(0, -1));
+    pointCollection.add(new Point2D.Double(4, -3));
+    Aesa<Point2D.Double> fnncAlgo = new Aesa<Point2D.Double>(distanceCalculator);
+    fnncAlgo.preProcessing(pointCollection);
+    assertEquals(
+        new Point2D.Double(3, 3),
+        fnncAlgo.calculateNearestNeighbour(new Point2D.Double(2, 1))
+    );
+  }
+}

### 2016-05-01 program/src/test/java/fnnc/model/DistanceObjectPairTest.java

@@ -1,4 +1,5 @@
 import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertSame;
 
 import fnnc.model.DistanceObjectPair;
 import org.junit.Before;
@@ -30,6 +31,13 @@ public class DistanceObjectPairTest {
   @Test
   public void testGetObject() {
     assertEquals("Object", this.distObjPair.getObject());
+  }
+
+  @Test
+  public void testSetDistance() {
+    int newDistance = -8;
+    this.distObjPair.setDistance(newDistance);
+    assertSame(newDistance, this.distObjPair.getDistance());
   }
 
   @Test

### 2016-05-02 program/src/test/java/fnnc/algo/AesaTest.java
update tests

@@ -12,16 +12,21 @@ public class AesaTest {
   public void testCalculateNearestNeighbour() {
     DistanceCalculator distanceCalculator = new DistanceCalculator();
     LinkedList<Point2D.Double> pointCollection = new LinkedList<Point2D.Double>();
-    pointCollection.add(new Point2D.Double(3, 3));
-    pointCollection.add(new Point2D.Double(-1, 2));
-    pointCollection.add(new Point2D.Double(-4, -4));
-    pointCollection.add(new Point2D.Double(0, -1));
-    pointCollection.add(new Point2D.Double(4, -3));
+    pointCollection.add(new Point2D.Double(5.40, 9.80));
+    pointCollection.add(new Point2D.Double(1.64, 3.30));
+    pointCollection.add(new Point2D.Double(9.62, 3.19));
+    pointCollection.add(new Point2D.Double(0.33, 6.85));
+    pointCollection.add(new Point2D.Double(4.73, 6.12));
+    pointCollection.add(new Point2D.Double(5.26, 6.32));
+    pointCollection.add(new Point2D.Double(1.83, 6.58));
+    pointCollection.add(new Point2D.Double(5.98, 0.69));
+    pointCollection.add(new Point2D.Double(9.59, 8.10));
+    pointCollection.add(new Point2D.Double(3.76, 0.81));
     Aesa<Point2D.Double> fnncAlgo = new Aesa<Point2D.Double>(distanceCalculator);
     fnncAlgo.preProcessing(pointCollection);
     assertEquals(
-        new Point2D.Double(3, 3),
-        fnncAlgo.calculateNearestNeighbour(new Point2D.Double(2, 1))
+        new Point2D.Double(3.76, 0.81),
+        fnncAlgo.calculateNearestNeighbour(new Point2D.Double(4.42, 0.78))
     );
   }
 }

### 2016-05-02 program/src/test/java/fnnc/algo/AnnulusMethodTest.java

@@ -12,16 +12,21 @@ public class AnnulusMethodTest {
   public void testCalculateNearestNeighbour() {
     DistanceCalculator distanceCalculator = new DistanceCalculator();
     LinkedList<Point2D.Double> pointCollection = new LinkedList<Point2D.Double>();
-    pointCollection.add(new Point2D.Double(3, 3));
-    pointCollection.add(new Point2D.Double(-1, 2));
-    pointCollection.add(new Point2D.Double(-4, -4));
-    pointCollection.add(new Point2D.Double(0, -1));
-    pointCollection.add(new Point2D.Double(4, -3));
+    pointCollection.add(new Point2D.Double(5.40, 9.80));
+    pointCollection.add(new Point2D.Double(1.64, 3.30));
+    pointCollection.add(new Point2D.Double(9.62, 3.19));
+    pointCollection.add(new Point2D.Double(0.33, 6.85));
+    pointCollection.add(new Point2D.Double(4.73, 6.12));
+    pointCollection.add(new Point2D.Double(5.26, 6.32));
+    pointCollection.add(new Point2D.Double(1.83, 6.58));
+    pointCollection.add(new Point2D.Double(5.98, 0.69));
+    pointCollection.add(new Point2D.Double(9.59, 8.10));
+    pointCollection.add(new Point2D.Double(3.76, 0.81));
     AnnulusMethod<Point2D.Double> fnncAlgo = new AnnulusMethod<Point2D.Double>(distanceCalculator);
     fnncAlgo.preProcessing(pointCollection);
     assertEquals(
-        new Point2D.Double(3, 3),
-        fnncAlgo.calculateNearestNeighbour(new Point2D.Double(2, 1))
+        new Point2D.Double(3.76, 0.81),
+        fnncAlgo.calculateNearestNeighbour(new Point2D.Double(4.42, 0.78))
     );
   }
 }

### 2016-05-02 program/src/test/java/fnnc/algo/FullSearchTest.java

@@ -12,17 +12,22 @@ public class FullSearchTest {
   public void testCalculateNearestNeighbour() {
     DistanceCalculator distanceCalculator = new DistanceCalculator();
     LinkedList<Point2D.Double> pointCollection = new LinkedList<Point2D.Double>();
-    pointCollection.add(new Point2D.Double(3, 3));
-    pointCollection.add(new Point2D.Double(-1, 2));
-    pointCollection.add(new Point2D.Double(-4, -4));
-    pointCollection.add(new Point2D.Double(0, -1));
-    pointCollection.add(new Point2D.Double(4, -3));
+    pointCollection.add(new Point2D.Double(5.40, 9.80));
+    pointCollection.add(new Point2D.Double(1.64, 3.30));
+    pointCollection.add(new Point2D.Double(9.62, 3.19));
+    pointCollection.add(new Point2D.Double(0.33, 6.85));
+    pointCollection.add(new Point2D.Double(4.73, 6.12));
+    pointCollection.add(new Point2D.Double(5.26, 6.32));
+    pointCollection.add(new Point2D.Double(1.83, 6.58));
+    pointCollection.add(new Point2D.Double(5.98, 0.69));
+    pointCollection.add(new Point2D.Double(9.59, 8.10));
+    pointCollection.add(new Point2D.Double(3.76, 0.81));
     FullSearch<Point2D.Double, Double> fnncAlgo =
         new FullSearch<Point2D.Double, Double>(distanceCalculator);
     fnncAlgo.preProcessing(pointCollection);
     assertEquals(
-        new Point2D.Double(3, 3),
-        fnncAlgo.calculateNearestNeighbour(new Point2D.Double(2, 1))
+        new Point2D.Double(3.76, 0.81),
+        fnncAlgo.calculateNearestNeighbour(new Point2D.Double(4.42, 0.78))
     );
   }
 }

### 2016-05-02 program/src/test/java/fnnc/algo/OrchardsAlgorithmTest.java

@@ -12,17 +12,22 @@ public class OrchardsAlgorithmTest {
   public void testCalculateNearestNeighbour() {
     DistanceCalculator distanceCalculator = new DistanceCalculator();
     LinkedList<Point2D.Double> pointCollection = new LinkedList<Point2D.Double>();
-    pointCollection.add(new Point2D.Double(3, 3));
-    pointCollection.add(new Point2D.Double(-1, 2));
-    pointCollection.add(new Point2D.Double(-4, -4));
-    pointCollection.add(new Point2D.Double(0, -1));
-    pointCollection.add(new Point2D.Double(4, -3));
+    pointCollection.add(new Point2D.Double(5.40, 9.80));
+    pointCollection.add(new Point2D.Double(1.64, 3.30));
+    pointCollection.add(new Point2D.Double(9.62, 3.19));
+    pointCollection.add(new Point2D.Double(0.33, 6.85));
+    pointCollection.add(new Point2D.Double(4.73, 6.12));
+    pointCollection.add(new Point2D.Double(5.26, 6.32));
+    pointCollection.add(new Point2D.Double(1.83, 6.58));
+    pointCollection.add(new Point2D.Double(5.98, 0.69));
+    pointCollection.add(new Point2D.Double(9.59, 8.10));
+    pointCollection.add(new Point2D.Double(3.76, 0.81));
     OrchardsAlgorithm<Point2D.Double> fnncAlgo =
         new OrchardsAlgorithm<Point2D.Double>(distanceCalculator);
     fnncAlgo.preProcessing(pointCollection);
     assertEquals(
-        new Point2D.Double(3, 3),
-        fnncAlgo.calculateNearestNeighbour(new Point2D.Double(2, 1))
+        new Point2D.Double(3.76, 0.81),
+        fnncAlgo.calculateNearestNeighbour(new Point2D.Double(4.42, 0.78))
     );
   }
 }

### 2016-05-02 paper/paper.tex
paper full search

--- 2015-08-18 paper/paper.tex
@@
-\documentclass[deutsch,runningheads,a4paper]{llncs}
+\documentclass[runningheads,a4paper]{llncs}
 
-\usepackage[utf8]{inputenc}
+\usepackage{amssymb}
+\setcounter{tocdepth}{3}
+\usepackage{graphicx}
+\usepackage{pgfplots}
+
 \usepackage{url}
+\newcommand{\keywords}[1]{\par\addvspace\baselineskip
+\noindent\keywordname\enspace\ignorespaces#1}
 
 \begin{document}
+
+\mainmatter
+
 \title{Fast Nearest Neighbour Classification}
+\subtitle{\textnormal{\small{Seminar\\
+Intelligente Software-Systeme\\
+Sommersemester 2015\\\vspace{1\baselineskip}
+Stefan Fricke\\\vspace{2\baselineskip}
+April 2016\\
+Betreuer: Stephan Spiegel\\\vspace{1\baselineskip}}}}
+
 \titlerunning{Fast Nearest Neighbour Classification}
 
-  \author{Gordon Lesti}
-  \authorrunning{Gordon Lesti}
+\author{Gordon Lesti\\313249\\Studiengang: Informatik\\gordon.lesti@campus.tu-berlin.de\\\vspace{5\baselineskip}}
 
-  \institute{Technische Universität Berlin,\\
-  Straße des 17. Juni 135, 10623 Berlin\\
-  \url{http://www.tu-berlin.de/}}
+\authorrunning{Fast Nearest Neighbour Classification}
 
+\institute{Technische Universit\"at Berlin\\
+Fakult\"at IV Elektrotechnik und Informatik\\
+Fachgebiet AOT\\
+Prof. Dr. Sahin Albayrak\\
+\url{http://www.aot.tu-berlin.de/}}
+
+\toctitle{Fast Nearest Neighbour Classification}
+\tocauthor{Gordon Lesti}
 \maketitle
@@
 \begin{abstract}
-   jo
+This term paper is about nearest neighbour classifiers that work with the triangle inequality of metric spaces.
+Benchmarks on examples from the two-dimensional space will show the advantages and disadvantages of three known
+algorithms. The Orchard’s Algorithm, the Annulus Method and the AESA will be explained on examples and compared to the
+full search. The benchmarks aren't comparing execution time, they will compare calls of the distance function.
+\keywords{Nearest neighbour classifiers, Triangle inequality, Metric space}
 \end{abstract}
 
-  \section{Einleitung}
+\tableofcontents
+
+\newpage
+
+\section{Introduction}
+
+\subsection{Requirements}
+
+\section{Algorithms}
+
+\subsection{Full Search}
+
+The full search isn't a real fast nearest neighbour algorithm, it's more the default algorithm for such a problem. We
+just iterate over all $x \in S$ and calculate $d(q, x)$. After that we just take $a \in S$, so that
+$d(q, a) \le d(q, x)$ for all $x \in S$. The big advantage compared to the following algorithms is, that the full search
+works also in not metric spaces. The full search has no preprocessing.
+
+\subsection{Orchard’s Algorithm}
+
+\subsubsection{Preprocessing}
+
+\subsection{Annulus Method}
+
+\subsubsection{Preprocessing}
+
+\subsection{AESA}
+
+\subsubsection{Preprocessing}
+
+\section{Benchmarks}
+
+\subsection{Implementation}
+
+\subsection{Full Search}
+
+\subsection{Orchard’s Algorithm}
+
+\subsection{Annulus Method}
+
+\subsection{AESA}
+
+\subsection{Outcome}
+
+\begin{center}
+	\begin{tikzpicture}
+		\begin{axis}[ymin=0, xmin=0, legend pos=north west]
+			\addplot table {data/mainprocessing/fullsearch.csv};
+            \addlegendentry{FullSearch}
+            \addplot table {data/mainprocessing/orchards.csv};
+            \addlegendentry{Orchards}
+            \addplot table {data/mainprocessing/annulus.csv};
+            \addlegendentry{Annulus}
+            \addplot table {data/mainprocessing/aesa.csv};
+            \addlegendentry{AESA}
+		\end{axis}
+	\end{tikzpicture}
+\end{center}
 

### 2016-05-02 program/src/main/java/fnnc/algo/Aesa.java

@@ -18,7 +18,7 @@ public class Aesa<T> extends FastNearestNeighbourClassificator<T, Double> {
   }
 
   /**
-   * Prepares search for nearest neighboor.
+   * Prepares search for nearest neighbour.
    */
   public void preProcessing(Collection<T> objectCollection) {
     super.preProcessing(objectCollection);
@@ -58,7 +58,7 @@ public class Aesa<T> extends FastNearestNeighbourClassificator<T, Double> {
     DistanceObjectPair<Double, T> pair = unknownList.remove(
         rand.nextInt(unknownList.size())
     );
-    T nearestNeighboor = pair.getObject();
+    T nearestNeighbour = pair.getObject();
     while (pair != null) {
       T object = pair.getObject();
       if (unknownList.size() == 0) {
@@ -67,7 +67,7 @@ public class Aesa<T> extends FastNearestNeighbourClassificator<T, Double> {
       double distance = this.distanceCalculator.calculateDistance(object, queryObject);
       if (distance < smallestDistance) {
         smallestDistance = distance;
-        nearestNeighboor = object;
+        nearestNeighbour = object;
       }
       double max = Double.POSITIVE_INFINITY;
       Iterator<DistanceObjectPair<Double, T>> iterator = unknownList.iterator();
@@ -90,6 +90,6 @@ public class Aesa<T> extends FastNearestNeighbourClassificator<T, Double> {
       }
       unknownList.remove(pair);
     }
-    return nearestNeighboor;
+    return nearestNeighbour;
   }
 }

### 2016-05-02 program/src/main/java/fnnc/algo/AnnulusMethod.java

@@ -20,7 +20,7 @@ public class AnnulusMethod<T> extends FastNearestNeighbourClassificator<T, Doubl
   }
 
   /**
-   * Prepares search for nearest neighboor.
+   * Prepares search for nearest neighbour.
    */
   public void preProcessing(Collection<T> objectCollection) {
     super.preProcessing(objectCollection);

### 2016-05-02 program/src/main/java/fnnc/algo/FastNearestNeighbourClassificator.java

@@ -17,7 +17,7 @@ public abstract class FastNearestNeighbourClassificator<T, D extends Comparable<
   }
 
   /**
-   * Prepares search for nearest neighboor.
+   * Prepares search for nearest neighbour.
    */
   public void preProcessing(Collection<T> objectCollection) {
     this.objectCollection = objectCollection;

### 2016-05-02 program/src/main/java/fnnc/algo/OrchardsAlgorithm.java

@@ -26,7 +26,7 @@ public class OrchardsAlgorithm<T> extends FastNearestNeighbourClassificator<T, D
   }
 
   /**
-   * Prepares search for nearest neighboor.
+   * Prepares search for nearest neighbour.
    */
   public void preProcessing(Collection<T> objectCollection) {
     super.preProcessing(objectCollection);

### 2016-05-04 program/src/main/java/fnnc/Application.java
improve yoyo

@@ -76,10 +76,10 @@ public class Application {
     String resultString = "Size: " + problems.get(0).size() + "\nCount: " + problems.size() + "\n";
     for (int i = 0; i < algos.size(); i++) {
       double preProcessingCount = result[0][i] / problems.size();
-      double mainProcessingCount = result[1][i] / problems.size();
+      double queryProcessingCount = result[1][i] / problems.size();
       String algoName = algos.get(i).getClass().getName();
       resultString += algoName + ":\n\tPreProcessing: " + preProcessingCount
-          + "\n\tMainProcessing: " + mainProcessingCount + "\n";
+          + "\n\tQueryProcessing: " + queryProcessingCount + "\n";
     }
     return resultString;
   }

### 2016-05-04 program/src/main/java/fnnc/algo/OrchardsAlgorithm.java

@@ -75,23 +75,28 @@ public class OrchardsAlgorithm<T> extends FastNearestNeighbourClassificator<T, D
     T currentObject = this.indexedObjects.get(currentIndex);
     double currentDistanceToQuery = this.distanceCalculator
         .calculateDistance(currentObject, queryObject);
+    boolean[] markBits = new boolean[this.objectCollection.size()];
     LinkedList<DistanceObjectPair<Double, Integer>> currentList =
         this.orderedLists.get(currentIndex);
     Iterator<DistanceObjectPair<Double, Integer>> iterator = currentList.iterator();
     while (iterator.hasNext()) {
       DistanceObjectPair<Double, Integer> tempDistObjPair = iterator.next();
-      T tempObject = this.indexedObjects.get(tempDistObjPair.getObject());
-      if (tempDistObjPair.getDistance() > 2 * currentDistanceToQuery) {
-        break;
-      }
-      double tempDistanceToQuery = this.distanceCalculator
-          .calculateDistance(tempObject, queryObject);
-      if (tempDistanceToQuery < currentDistanceToQuery) {
-        currentDistanceToQuery = tempDistanceToQuery;
-        currentIndex = tempDistObjPair.getObject();
-        currentObject = tempObject;
-        currentList = this.orderedLists.get(currentIndex);
-        iterator = currentList.iterator();
+      int tempIndex = tempDistObjPair.getObject();
+      if (!markBits[tempIndex]) {
+        T tempObject = this.indexedObjects.get(tempIndex);
+        if (tempDistObjPair.getDistance() > 2 * currentDistanceToQuery) {
+          break;
+        }
+        double tempDistanceToQuery = this.distanceCalculator
+            .calculateDistance(tempObject, queryObject);
+        markBits[tempIndex] = true;
+        if (tempDistanceToQuery < currentDistanceToQuery) {
+          currentDistanceToQuery = tempDistanceToQuery;
+          currentObject = tempObject;
+          currentIndex = tempIndex;
+          currentList = this.orderedLists.get(currentIndex);
+          iterator = currentList.iterator();
+        }
       }
     }
     return currentObject;

### 2016-05-04 program/src/main/java/fnnc/model/point2ddouble/DistanceCalculator.java

@@ -8,8 +8,6 @@ public class DistanceCalculator extends fnnc.model.DistanceCalculator<Point2D.Do
    * Calculates the distance between the two objects.
    */
   protected Double internalCalculateDistance(Point2D.Double point1, Point2D.Double point2) {
-    double xdiff = point1.x - point2.x;
-    double ydiff = point1.y - point2.y;
-    return Math.sqrt(xdiff * xdiff + ydiff * ydiff);
+    return point1.distance(point2);
   }
 }

### 2016-05-05 program/src/main/java/fnnc/Application.java
add data to 2000

@@ -57,29 +57,35 @@ public class Application {
       LinkedList<FastNearestNeighbourClassificator<Point2D.Double, Double>> algos,
       LinkedList<LinkedList<Point2D.Double>> problems
   ) {
-    double[][] result = new double[2][algos.size()];
+    int[][][] result = new int[2][algos.size()][problems.size()];
+    int problemCount = 0;
     for (LinkedList<Point2D.Double> problem : problems) {
       Point2D.Double query = problem.poll();
       int counter = 0;
       Point2D.Double[] checkResult = new Point2D.Double[algos.size()];
       for (FastNearestNeighbourClassificator<Point2D.Double, Double> algo : algos) {
         algo.preProcessing(problem);
-        result[0][counter] += distanceCalculator.reset();
+        result[0][counter][problemCount] = distanceCalculator.reset();
         checkResult[counter] = algo.calculateNearestNeighbour(query);
-        result[1][counter] += distanceCalculator.reset();
+        result[1][counter][problemCount] += distanceCalculator.reset();
         counter++;
       }
       if (!checkResults(checkResult)) {
         return "ERROR";
       }
+      problemCount++;
     }
     String resultString = "Size: " + problems.get(0).size() + "\nCount: " + problems.size() + "\n";
     for (int i = 0; i < algos.size(); i++) {
-      double preProcessingCount = result[0][i] / problems.size();
-      double queryProcessingCount = result[1][i] / problems.size();
+      double[] preMeanAndStandardDeviation = calculateMeanAndStandardDeviation(result[0][i]);
+      double[] queryMeanAndStandardDeviation = calculateMeanAndStandardDeviation(result[1][i]);
+    //   double preProcessingCount = result[0][i] / problems.size();
+    //   double queryProcessingCount = result[1][i] / problems.size();
       String algoName = algos.get(i).getClass().getName();
-      resultString += algoName + ":\n\tPreProcessing: " + preProcessingCount
-          + "\n\tQueryProcessing: " + queryProcessingCount + "\n";
+      resultString += algoName + ":\n\tPreProcessing:\n\t\tMean: " + preMeanAndStandardDeviation[0]
+          + "\n\t\tStandardDeviation: " + preMeanAndStandardDeviation[1]
+          + "\n\tQueryProcessing:\n\t\tMean: " + queryMeanAndStandardDeviation[0]
[…]

### 2016-05-06 paper/paper.tex
cleanup

@@
 \maketitle
+\pagenumbering{roman}
 
+\addcontentsline{toc}{section}{Abstract}
 \begin{abstract}
@@
 \tableofcontents
+\addcontentsline{toc}{section}{Table of Contents}
 
 \newpage
+\pagenumbering{arabic}
 
@@
 
-\subsection{Requirements}
+\subsection{Problem}
+
+The problem of the nearest neighbour search is pretty easy described. We have a set of objects and we want to find that
+object with the smallest distance to a query object.\\
+The requirements are:
+\begin{itemize}
+	\item a set $\mathbb{U}$
+	\item a distance function $d$ on $\mathbb{U}$, with $d: \mathbb{U} \times \mathbb{U} \to \mathbb{R}$
+	\item a set $S \subset \mathbb{U}$ with size $n$
+	\item a query $q \in \mathbb{U}$
+\end{itemize}
+The solution is:
+\begin{itemize}
+	\item an $a \in S$, with $d(q, a) \le d(q, x)$ for all $x \in S$
+\end{itemize}
 
 \section{Algorithms}
+
+Every nearest neighbour search algorithm can be divided in two steps.
+\begin{itemize}
+	\item Preprocessing
+	\item Query Processing
+\end{itemize}
+In the preprocessing the algorithm prepare the given set $\mathbb{S}$ for
+their needs.\\
+The query processing is the real nearest neighbour search, the algorithms take the query $q$ and return the nearest
+neighbour $a$.
 
@@
 The full search isn't a real fast nearest neighbour algorithm, it's more the default algorithm for such a problem. We
-just iterate over all $x \in S$ and calculate $d(q, x)$. After that we just take $a \in S$, so that
+just walk over all $x \in S$ and calculate $d(q, x)$. After that we just take $a \in S$, so that
 $d(q, a) \le d(q, x)$ for all $x \in S$. The big advantage compared to the following algorithms is, that the full search
-works also in not metric spaces. The full search has no preprocessing.
+works also in not metric spaces. The full search needs no preprocessing.
 
@@
 
+The preprocessing of the Orchard’s Algorithm has a high complexity. For every $p \in S$, we generate a list that
+contains all $x \in S\setminus\left\{ {p}\right\}$ with it's distance $d(p, x)$ and order those lists ascending to the
+distance. If we assume that the set $S$ has size $n$, the preprocessing will call the distance function
+$\frac{n(n-1)}{2}$ times and will sort $n$ lists of size $n-1$.
+
+\subsubsection{Query Processing}
+
+When calling the query processing with query $q$, we randomly select one object $c \in S$ as initial candidate and
+calculate $d(c, q)$. After that we walk over the ordered list of $c$ and with every picked $s$ from the list we
+calculate $d(l, q)$. If $d(l, q)$ is smaller than $d(c, q)$, $l$ is our new candidate $c$ and we will walk over the
+list of $l$. We abort if we reached the end of a list or if $d(c, s) > 2d(c, q)$. The current candidate $c$ is our
+nearest neighbour.
+
 \subsection{Annulus Method}
 
+The Annulus Method works a little bit similar to the Orchard’s Algorithm, but with a less complex preprocessing.
+
 \subsubsection{Preprocessing}
+
+Instead of generating a list for all $x \in S$, the Annulus Method generates just one list for a random $p^* \in S$. In
+the preprocessing we generate one list that contains all $x \in S$ with it's distance $d(p^*, x)$ and order this list
+ascending to the distance. If we assume that the set $S$ has size $n$, the preprocessing will call the distance function
+$n$ times and will sort one list of size $n$.
+
+\subsubsection{Query Processing}
+
+The query processing of the Annulus Method starts by picking a random candidate $c \in S$ from the ordered list of
+$p^*$. After that we walk alternating away from $p^*$ and back to him in the list. If the current object $s$ has
+$d(s, q) < d(c, q)$, we set $s$ as our new candidate $c$.If the current object $s$ is under $c$ in the list and
+$d(p^*, s) < d(p^*, q) - d(c, q)$, we can ignore all objects under $s$ in the list. If the current object $s$ is above
+$c$ in the list and $d(p^*, s) > d(p^*, q) + d(c, q)$, we can ignore all objects above $s$ in the list. The object $c$
+is the nearest neighbour, if the entire list is traversed.
 
@@
 
+\subsubsection{Query Processing}
+
 \section{Benchmarks}
+
+As described above, the following benchmarks will not compare the runtime of the mentioned algorithms. The benchmarks
+will compare the calls of the distance function that the algorithm needs for preprocessing and for finding a nearest
+neighbour. Those benchmarks can make sense when the distance function has a heavy complexity. For example the string
+metric Levenshtein distance or in higher dimensional vector spaces.\\
+In general those benchmarks are affected by the implementation, by the executing machine, by the domain of the problem
+and the distribution of the example.
 
@@
 
-\subsection{Full Search}
+The algorithms above are all implemented in Java and can be found in the following git repository\\
+\url{https://github.com/GordonLesti/FastNearestNeighbourClassification}.\\
 
-\subsection{Orchard’s Algorithm}
+A nearest neighbour algorithm implemented in Java should handle every type of object that a set $\mathbb{U}$ can
+represent under the condition that there is a metric on $\mathbb{U}$. Because of that, a nearest neighbour algorithm
+class needs to extend from the abstract class \verb+FastNearestNeighbourClassificator+ that can be found in the package
+\verb+fnnc.algo+. The generic \verb+T+ represents an object from the set $\mathbb{U}$ and the generic \verb+D+
+represents the distance and has to be of type \verb+Comparable+ from the package \verb+java.lang+.\\
 
-\subsection{Annulus Method}
+A possible example for the type \verb+T+ can be \verb+Point2D.Double+ from the package
+\verb+java.awt.geom+ and a possible way to implement a distance function would be the euclidean distance of type
+\verb+Double+.
 
-\subsection{AESA}
+\subsubsection{FastNearestNeighbourClassificator}
 
-\subsection{Outcome}
+The abstract class\\ \verb+FastNearestNeighbourClassificator<T, D extends Comparable<D>>+ has two protected class
+variables:
+\begin{itemize}
+	\item a \verb+distanceCalculator+ of type \verb+DistanceCalculator<T, D>+
+	\item a \verb+objectCollection+ of type \verb+Collection<T>+
+\end{itemize}
+and three simple class methods:
+\begin{itemize}
+	\item a constructor that takes an object of type \verb+DistanceCalculator<T, D>+ from the package
+		\verb+fnnc.model+ and sets the protected class variable
+	\item a default function \verb+preProcessing+ that takes a \verb+Collection<T>+ from the package
+		\verb+java.util+ and sets the protected class variable
+	\item a abstract function \verb+calculateNearestNeighbour+ that takes the query object of type \verb+T+ and
+		returns the nearest neighbour object of type \verb+T+
+\end{itemize}
 
+A instance of type \verb+FastNearestNeighbourClassificator+ shouldn't and can't calculate the distance between two
+objects. Because of that we inject the \verb+DistanceCalculator+ in the constructor. All implemented algorithms exclude
+the \verb+FullSearch+ require that the \verb+DistanceCalculator+ returns a distance of type \verb+Double+ instead of
+only \verb+Comparable+.
+
+\subsubsection{DistanceCalculator}
+
+The abstract class\\ \verb+DistanceCalculator<Point2D.Double, Double>+ has just one private \verb+count+ of type
+\verb+int+ and three class methods:
+\begin{itemize}
+	\item a public final function \verb+calculateDistance+ that takes two objects of type \verb+T+, increases the
+		internal count and returns the result of \verb+internalCalculateDistance+
+	\item a public final function \verb+reset+ that resets the internal count
+	\item a protected abstract function \verb+internalCalculateDistance+ that takes two objects of type \verb+T+ and
+		returns the distance object of type \verb+D+
+\end{itemize}
+
+\subsection{Example data}
+
+The benchmarks will use a \verb+java.util.Collection+ of type\\ \verb+java.awt.geom.Point2D+ that are representing
+points in $\mathbb{R}^2$. For every size $n \in \left\{ {100, 200, \dots, 1000}\right\}$, every algorithm will get
+thousand sets with randomly generated points. The class \verb+fnnc.model.point2ddouble.DistanceCalculator+ will count
+every call of the function \verb+internalCalculateDistance+ and after all we will calculate the average of the calls for
+every algorithm.
+
+\subsection{Result}
+
+\subsubsection{Preprocessing}
+
+\begin{figure}
 	\begin{center}
 		\begin{tikzpicture}
-		\begin{axis}[ymin=0, xmin=0, legend pos=north west]
-			\addplot table {data/mainprocessing/fullsearch.csv};
-            \addlegendentry{FullSearch}
-            \addplot table {data/mainprocessing/orchards.csv};
+			\begin{axis}[
+				ymin=0,
+				xmin=0,
+				xlabel=size of test data set $S$,
+				ylabel=average calls of distance function,
+				legend pos=outer north east]
+				\addplot table {data/preprocessing/fullsearch.csv};
+	            \addlegendentry{Full Search}
+	            \addplot table {data/preprocessing/orchards.csv};
 	            \addlegendentry{Orchards}
-            \addplot table {data/mainprocessing/annulus.csv};
+	            \addplot table {data/preprocessing/annulus.csv};
 	            \addlegendentry{Annulus}
-            \addplot table {data/mainprocessing/aesa.csv};
+	            \addplot table {data/preprocessing/aesa.csv};
 	            \addlegendentry{AESA}
@@
 	\end{center}
+	\caption{The average calls of the distance function in the preprocessing depending on the size of the test data set
+		$S$ visualized with graphs.}
+	\label{fig:preprocessing:graph}
+\end{figure}
+
+\subsubsection{Query Processing}
+
+\begin{figure}
+	\begin{center}
+		\begin{tabular}{ | l | c | c | c | c |}
+			\hline
+		  	& Full Search & Orchard’s Algorithm & Annulus Method & AESA \\ \hline
+		  	100 & 100 & 20 & 46 & 4 \\ \hline
+			200 & 200 & 26 & 82 & 4 \\ \hline
+			300 & 300 & 30 & 122 & 4 \\ \hline
+			400 & 400 & 35 & 157 & 4 \\ \hline
+			500 & 500 & 39 & 190 & 4 \\ \hline
+			600 & 600 & 42 & 222 & 4 \\ \hline
+			700 & 700 & 44 & 269 & 4 \\ \hline
+			800 & 800 & 46 & 302 & 4 \\ \hline
+			900 & 900 & 50 & 334 & 4 \\ \hline
+			1000 & 1000 & 52 & 373 & 4 \\ \hline
+			1100 & 1100 & 55 & 418 & 4 \\ \hline
+			1200 & 1200 & 56 & 433 & 4 \\ \hline
+			1300 & 1300 & 59 & 477 & 4 \\ \hline
+			1400 & 1400 & 62 & 510 & 4 \\ \hline
+			1500 & 1500 & 64 & 544 & 4 \\ \hline
+			1600 & 1600 & 63 & 587 & 4 \\ \hline
+			1700 & 1700 & 66 & 607 & 4 \\ \hline
+			1800 & 1800 & 69 & 667 & 4 \\ \hline
+			1900 & 1900 & 72 & 716 & 4 \\ \hline
+			2000 & 2000 & 73 & 714 & 4 \\ \hline
+		\end{tabular}
+	\end{center}
+	\caption{The average calls of the distance function in the query processing depending on the size of the test data
+		set $S$.}
+	\label{fig:queryprocessing:tabular}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\begin{tikzpicture}
+			\begin{axis}[ymin=0, xmin=0, legend pos=outer north east]
+				\addplot table {data/queryprocessing/fullsearch.csv};
+	            \addlegendentry{Full Search}
+	            \addplot table {data/queryprocessing/orchards.csv};
+	            \addlegendentry{Orchards}
+	            \addplot table {data/queryprocessing/annulus.csv};
+	            \addlegendentry{Annulus}
+	            \addplot table {data/queryprocessing/aesa.csv};
+	            \addlegendentry{AESA}
+			\end{axis}
+		\end{tikzpicture}
+	\end{center}
+	\caption{The average calls of the distance function in the query processing depending on the size of the test data
+		set $S$ visualized with graphs.}
+	\label{fig:queryprocessing:graph}
+\end{figure}
 

### 2016-05-06 program/src/main/java/fnnc/Application.java

@@ -79,8 +79,6 @@ public class Application {
     for (int i = 0; i < algos.size(); i++) {
       double[] preMeanAndStandardDeviation = calculateMeanAndStandardDeviation(result[0][i]);
       double[] queryMeanAndStandardDeviation = calculateMeanAndStandardDeviation(result[1][i]);
-    //   double preProcessingCount = result[0][i] / problems.size();
-    //   double queryProcessingCount = result[1][i] / problems.size();
       String algoName = algos.get(i).getClass().getName();
       resultString += algoName + ":\n\tPreProcessing:\n\t\tMean: " + preMeanAndStandardDeviation[0]
           + "\n\t\tStandardDeviation: " + preMeanAndStandardDeviation[1]
@@ -96,9 +94,16 @@ public class Application {
       InputStream buffer = new BufferedInputStream(file);
       ObjectInput input = new ObjectInputStream(buffer);
     ) {
+      LinkedList<LinkedList<Point2D.Double>> problems = new LinkedList<LinkedList<Point2D.Double>>();
       @SuppressWarnings("unchecked")
-      LinkedList<LinkedList<Point2D.Double>> problems =
-          (LinkedList<LinkedList<Point2D.Double>>) input.readObject();
+      Point2D.Double[][] problemsArray = (Point2D.Double[][]) input.readObject();
+      for (int i = 0; i < problemsArray.length; i++) {
+        LinkedList<Point2D.Double> problem = new LinkedList<Point2D.Double>();
+        for (int j = 0; j < problemsArray[i].length; j++) {
+          problem.add(problemsArray[i][j]);
+        }
+        problems.add(problem);
+      }
       return problems;
     } catch (Exception e) {
       return null;
@@ -109,12 +114,22 @@ public class Application {
       String filename,
       LinkedList<LinkedList<Point2D.Double>> problems
   ) {
+    Point2D.Double[][] problemsArray = new Point2D.Double[problems.size()][problems.get(0).size()];
+    int problemIndex = 0;
+    for (LinkedList<Point2D.Double> problem : problems) {
+      int pointIndex = 0;
+      for (Point2D.Double point : problem) {
+        problemsArray[problemIndex][pointIndex] = point;
+        pointIndex++;
+      }
+      problemIndex++;
+    }
     try (
       OutputStream file = new FileOutputStream(filename);
       OutputStream buffer = new BufferedOutputStream(file);
       ObjectOutput output = new ObjectOutputStream(buffer);
     ) {
[…]

### 2016-05-06 program/src/main/java/fnnc/Application.java
add test data

@@ -94,16 +94,9 @@ public class Application {
       InputStream buffer = new BufferedInputStream(file);
       ObjectInput input = new ObjectInputStream(buffer);
     ) {
-      LinkedList<LinkedList<Point2D.Double>> problems = new LinkedList<LinkedList<Point2D.Double>>();
       @SuppressWarnings("unchecked")
-      Point2D.Double[][] problemsArray = (Point2D.Double[][]) input.readObject();
-      for (int i = 0; i < problemsArray.length; i++) {
-        LinkedList<Point2D.Double> problem = new LinkedList<Point2D.Double>();
-        for (int j = 0; j < problemsArray[i].length; j++) {
-          problem.add(problemsArray[i][j]);
-        }
-        problems.add(problem);
-      }
+      LinkedList<LinkedList<Point2D.Double>> problems =
+          (LinkedList<LinkedList<Point2D.Double>>) input.readObject();
       return problems;
     } catch (Exception e) {
       return null;
@@ -114,22 +107,12 @@ public class Application {
       String filename,
       LinkedList<LinkedList<Point2D.Double>> problems
   ) {
-    Point2D.Double[][] problemsArray = new Point2D.Double[problems.size()][problems.get(0).size()];
-    int problemIndex = 0;
-    for (LinkedList<Point2D.Double> problem : problems) {
-      int pointIndex = 0;
-      for (Point2D.Double point : problem) {
-        problemsArray[problemIndex][pointIndex] = point;
-        pointIndex++;
-      }
-      problemIndex++;
-    }
     try (
       OutputStream file = new FileOutputStream(filename);
       OutputStream buffer = new BufferedOutputStream(file);
       ObjectOutput output = new ObjectOutputStream(buffer);
     ) {
-      output.writeObject(problemsArray);
+      output.writeObject(problems);
     } catch (IOException e) {
       System.out.println("Can not write to file " + filename);
     }

### 2016-05-10 paper/paper.tex
something like ready

--- 2016-05-02 paper/paper.tex
@@
 \usepackage{pgfplots}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 
@@
 \noindent\keywordname\enspace\ignorespaces#1}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
 
@@
 \maketitle
+\pagenumbering{roman}
 
+\addcontentsline{toc}{section}{Abstract}
 \begin{abstract}
-This term paper is about nearest neighbour classifiers that work with the triangle inequality of metric spaces.
-Benchmarks on examples from the two-dimensional space will show the advantages and disadvantages of three known
-algorithms. The Orchard’s Algorithm, the Annulus Method and the AESA will be explained on examples and compared to the
-full search. The benchmarks aren't comparing execution time, they will compare calls of the distance function.
+This term paper is about nearest neighbour classifiers which work with the triangle inequality of metric spaces. The
+Orchard’s Algorithm, the Annulus Method and the AESA will be explained on examples and compared to the Full Search.
+Benchmarks will show the advantages and disadvantages of the three algorithms. Counting the calls of the distance
+function is the focus of the benchmarks.
 \keywords{Nearest neighbour classifiers, Triangle inequality, Metric space}
@@
 
-\subsection{Requirements}
+HERE COMES THE INTRODUCTION.
+
+\subsection{Description of the problem}
+
+The mission of a nearest neighbour search algorithm is to find in a given set of items, that item with the smallest
+distance to a given query item.\\
+The requirements are:
+\begin{itemize}
+	\item a set $\mathbb{U}$
+	\item a distance function $D$ on $\mathbb{U}$, with $d: \mathbb{U} \times \mathbb{U} \to \mathbb{R}$
+	\item a set $S \subset \mathbb{U}$ with size $n$
+	\item a query $q \in \mathbb{U}$
+\end{itemize}
+The solution is:
+\begin{itemize}
+	\item an $a \in S$, with $D(q, a) \le D(q, x)$ for all $x \in S$
+\end{itemize}
 
@@
 
+Every nearest neighbour search algorithm can be divided into two steps.
+\paragraph{Preprocessing}
+During the preprocessing the algorithm prepares the given set $\mathbb{S}$ for his needs.
+
+\paragraph{Query Processing}
+The query processing is the main nearest neighbour search, the algorithm takes the query $q$ as input and works on the
+preprocessed data to find the nearest neighbour $a$.\\
+
+The following section will explain the preprocessing and query processing of the Full Search, the Orchard’s Algorithm,
+the Annulus Method and the AESA.
+
 \subsection{Full Search}
 
-The full search isn't a real fast nearest neighbour algorithm, it's more the default algorithm for such a problem. We
-just iterate over all $x \in S$ and calculate $d(q, x)$. After that we just take $a \in S$, so that
-$d(q, a) \le d(q, x)$ for all $x \in S$. The big advantage compared to the following algorithms is, that the full search
-works also in not metric spaces. The full search has no preprocessing.
+The Full Search is the upper bound for the following algorithms. Exactly $n$ calls of the distance function are required
+to find the nearest neighbour in a given $S$ of size $n$.\\
+
+\begin{algorithm}[H]
+	\caption{Full Search}
+	\label{fullsearch}
+	\begin{algorithmic}
+		\REQUIRE query $q \in \mathbb{U}$, set $S \subset \mathbb{U}$ of size $n$, distance function $D$
+		\ENSURE $a \in S$ with $D(q, a) \le D(q, x)$ $\forall x \in S$
+		\STATE $r := \infty$
+		\STATE $a :=$ NULL
+		\FORALL{$x \in S$}
+			\STATE $xd := D(x, q)$
+			\IF{$sd < r$}
+				\STATE $r := xd$
+				\STATE $a := x$
+			\ENDIF
+		\ENDFOR
+		\RETURN $a$
+	\end{algorithmic}
+\end{algorithm}
+
+The advantage compared to the following algorithms is, that the Full Search works also in not metric spaces. The Full
+Search needs no preprocessing.
 
@@
 
+The preprocessing of the Orchard’s Algorithm has a high complexity. For every $p \in S$, the algorithm will generate a
+list that contains all $x \in S\setminus\left\{ {p}\right\}$ with their distance $D(p, x)$. Those lists will be ordered
+ascending to the distance. For a set $S$ with size $n$, the preprocessing will call the distance function
+$\frac{n(n-1)}{2}$ times and will sort $n$ lists of size $n-1$.
+
+\subsubsection{Query Processing}
+
+When calling the query processing with query $q$, the algorithm will randomly select one object $c \in S$ as initial
+candidate and calculate $D(c, q)$. Afterwards the algorithm walks over the ordered list of $c$ and with every picked $s$
+from the list the algorithm calculates $D(l, q)$. If $D(l, q)$ is smaller than $D(c, q)$, $l$ is the new candidate $c$
+and the algorithm walks over the list of $l$. The algorithm aborts if it reaches the end of a list or if
+$D(c, s) > 2D(c, q)$. The current candidate $c$ is the nearest neighbour.
+
 \subsection{Annulus Method}
 
+The Annulus Method works a little bit similar to the Orchard’s Algorithm, but with a less complex preprocessing.
+
 \subsubsection{Preprocessing}
+
+Instead of generating a list for all $x \in S$, the Annulus Method generates just one list for a random $p^* \in S$. In
+the preprocessing the algorithm generates one list that contains all $x \in S$ with their distance $D(p^*, x)$. This
+list will be ordered ascending to the distance. For a set $S$ with size $n$, the preprocessing will call the distance
+function $n$ times and will sort one list of size $n$.
+
+\subsubsection{Query Processing}
+
+The query processing of the Annulus Method starts by picking a random candidate $c \in S$ from the ordered list of
+$p^*$. Afterwards the algorithm walks alternating away from $p^*$ and back to him in the list. If the current object $s$
+has $D(s, q) < D(c, q)$, the algorithm sets $s$ as the new candidate $c$. If the current object $s$ is under $c$ in the
+list and $D(p^*, s) < D(p^*, q) - D(c, q)$, the algorithm can ignore all objects under $s$ in the list. If the current
+object $s$ is above $c$ in the list and $D(p^*, s) > D(p^*, q) + D(c, q)$, the algorithm can ignore all objects above
+$s$ in the list. The object $c$ is the nearest neighbour, if the entire list is traversed.
 
@@
 
+The preprocessing for the AESA is starting the same way as the preprocessing of the Orchard’s Algorithm. The algorithm
+calculates the distance $D(x, y)$ of every $x \in S$ to every $y \in S\setminus\left\{ {x}\right\}$. But instead of
+writing those distances into lists and sorting them, the algorithm writes those distances into a matrix to access them
+quickly. For a set $S$ with size $n$, the preprocessing will call the distance function $\frac{n(n-1)}{2}$ times and
+will sort $n$ lists of size $n-1$.
+
+\subsubsection{Query Processing}
+
+When starting with the query processing, the algorithm generates a list for all objects $x \in S$ with a bounded
+distance $D_P(x, q) = -\infty$ and initialize $r = \infty$ as smallest distance to $q$. Afterwards the algorithm
+iterates the following steps until the list is empty.
+\begin{itemize}
+	\item pick and remove $x$ from the list with the smallest $D_p(x, q)$ or a random one in the first iteration
+	\item calculate $D(x, q)$
+	\item set $r = D(x, q)$ if $r > D(x, q)$ and remember $x$ as current nearest neighbour
+	\item for all $y$ from the list, set $D_P(y, q) = max(D_P(y, q), |D(x, q) - D(x, y)|)$ and remove $y$ from the list
+		if the new $D_P(y, q) > r$
+\end{itemize}
+
 \section{Benchmarks}
+
+As described above, the following benchmarks will not compare the runtime of the mentioned algorithms. The benchmarks
+will compare the calls of the distance function that the algorithm needs for preprocessing and for finding a nearest
+neighbour. Those benchmarks can make sense when the distance function has a heavy complexity. For example the string
+metric Levenshtein distance or in higher dimensional vector spaces.\\
+In general a benchmark is affected by the implementation, by the executing machine, by the domain of the problem
+and the distribution of the example. As the following benchmarks only counting the calls of the distance function, they
+aren't affected by the implementation or the executing machine.
 
@@
 
-\subsection{Full Search}
+The algorithms above are all implemented in Java and can be found in the following git repository\\
+\url{https://github.com/GordonLesti/FastNearestNeighbourClassification}.\\
 
-\subsection{Orchard’s Algorithm}
+A nearest neighbour algorithm implemented in Java should handle every type of object that a set $\mathbb{U}$ can
+represent under the condition that there is a metric on $\mathbb{U}$. Because of that, a nearest neighbour algorithm
+class needs to extend from the abstract class\\ \verb+FastNearestNeighbourClassificator<T, D extends Comparable<D>>+
+that can be found in the package \verb+fnnc.algo+. The generic \verb+T+ represents an object from the set $\mathbb{U}$
+and the generic \verb+D+ represents the distance and has to be of type \verb+Comparable+ from the package
+\verb+java.lang+.\\
 
-\subsection{Annulus Method}
+A possible example for the type \verb+T+ can be \verb+Point2D.Double+ from the package
+\verb+java.awt.geom+ and a possible way to implement a distance function would be the euclidean distance of type
+\verb+Double+.
 
-\subsection{AESA}
+\subsubsection{FastNearestNeighbourClassificator}
 
-\subsection{Outcome}
+The abstract class\\ \verb+FastNearestNeighbourClassificator<T, D extends Comparable<D>>+ has two protected class
+variables:
+\begin{itemize}
+	\item a \verb+distanceCalculator+ of type \verb+DistanceCalculator<T, D>+
+	\item a \verb+objectCollection+ of type \verb+Collection<T>+
+\end{itemize}
+and three simple class methods:
+\begin{itemize}
+	\item a constructor that takes an object of type \verb+DistanceCalculator<T, D>+ from the package
+		\verb+fnnc.model+ and sets the protected class variable
+	\item a default function \verb+preProcessing+ that takes a \verb+Collection<T>+ from the package
+		\verb+java.util+ and sets the protected class variable
+	\item a abstract function \verb+calculateNearestNeighbour+ that takes the query object of type \verb+T+ and
+		returns the nearest neighbour object of type \verb+T+
+\end{itemize}
 
+A instance of type \verb+FastNearestNeighbourClassificator+ shouldn't and can't calculate the distance between two
+objects. So that a instance of \verb+DistanceCalculator+ should be injected into the constructor. All implemented
+algorithms exclude the \verb+FullSearch+ require that the \verb+DistanceCalculator+ returns a distance of type
+\verb+Double+ instead of only \verb+Comparable+. This is connected with the fact that only the Full Search can operate
+in a not metric space.
+
+\subsubsection{DistanceCalculator}
+
+The abstract class\\ \verb+DistanceCalculator<Point2D.Double, Double>+ has just one private \verb+count+ of type
+\verb+int+ and three class methods:
+\begin{itemize}
+	\item a public final function \verb+calculateDistance+ that takes two objects of type \verb+T+, increases the
+		internal count and returns the result of \verb+internalCalculateDistance+
+	\item a public final function \verb+reset+ that resets the internal count
+	\item a protected abstract function \verb+internalCalculateDistance+ that takes two objects of type \verb+T+ and
+		returns the distance object of type \verb+D+
+\end{itemize}
+
+\subsection{Example data}
+
+The benchmarks will use a \verb+java.util.Collection+ of type\\ \verb+java.awt.geom.Point2D+ that are representing
+points in $\mathbb{R}^2$. For every size $n \in \left\{ {100, 200, \dots, 1900, 2000}\right\}$, every algorithm will get
+thousand sets of size $n$ with randomly generated points. The class\\ \verb+fnnc.model.point2ddouble.DistanceCalculator+
+will count every call of the function \verb+internalCalculateDistance+ and after all the application will calculate the
+average of the calls for every algorithm.
+
+\subsection{Result}
+
+\subsubsection{Preprocessing}
+
+\begin{figure}
+	\begin{center}
+		\begin{tabular}{ | l | c | c | c | c | c |}
+			\hline
+		  	& Full Search & Orchard & Orchard MarkBits & Annulus & AESA \\ \hline
+		  	$n$ & 0 & $\frac{n(n-1)}{2}$ & $\frac{n(n-1)}{2}$ & $n$ & $\frac{n(n-1)}{2}$ \\ \hline
+		\end{tabular}
+	\end{center}
+	\caption{The calls of the distance function $D$ in the preprocessing depending on the size $n$ of the test data set
+		$S$.}
+	\label{fig:preprocessing:tabular}
+\end{figure}
+
+\begin{figure}
 	\begin{center}
 		\begin{tikzpicture}
-		\begin{axis}[ymin=0, xmin=0, legend pos=north west]
-			\addplot table {data/mainprocessing/fullsearch.csv};
-            \addlegendentry{FullSearch}
-            \addplot table {data/mainprocessing/orchards.csv};
-            \addlegendentry{Orchards}
-            \addplot table {data/mainprocessing/annulus.csv};
+			\begin{axis}[
+				ymin=0,
+				xmin=0,
+				xmax=2000,
+				xlabel=size of test data set $S$,
+				ylabel=calls of distance function $D$,
+				legend pos=outer north east]
+				\addplot table {data/preprocessing/fullsearch.csv};
+	            \addlegendentry{Full Search}
+	            \addplot table {data/preprocessing/orchards.csv};
+	            \addlegendentry{Orchard}
+				\addplot table {data/preprocessing/orchardsmb.csv};
+				\addlegendentry{Orchard MarkBits}
+	            \addplot table {data/preprocessing/annulus.csv};
 	            \addlegendentry{Annulus}
-            \addplot table {data/mainprocessing/aesa.csv};
+	            \addplot table {data/preprocessing/aesa.csv};
 	            \addlegendentry{AESA}
@@
 	\end{center}
+	\caption{The average calls of the distance function $D$ in the preprocessing depending on the size of the test data
+		set $S$ visualized with graphs.}
+	\label{fig:preprocessing:graph}
+\end{figure}
+
+\subsubsection{Query Processing}
+
+\begin{figure}
+	\begin{center}
+		\begin{tabular}{ | l | c | c | c | c | c |}
+			\hline
+		  	& Full Search & Orchard & Orchard MarkBits & Annulus & AESA \\ \hline
+		  	100 & 100 & 29 & 20 & 46 & 4 \\ \hline
+			200 & 200 & 39 &26 & 82 & 4 \\ \hline
+			300 & 300 & 46 & 30 & 117 & 4 \\ \hline
+			400 & 400 & 53 & 35 & 160 & 4 \\ \hline
+			500 & 500 & 57 & 40 & 189 & 4 \\ \hline
+			600 & 600 & 63 & 42 & 228 & 4 \\ \hline
+			700 & 700 & 68 & 44 & 263 & 4 \\ \hline
+			800 & 800 & 73 & 46 & 303 & 4 \\ \hline
+			900 & 900 & 78 & 50 & 341 & 4 \\ \hline
+			1000 & 1000 & 79 & 51 & 367 & 4 \\ \hline
+			1100 & 1100 & 84 & 56 & 409 & 4 \\ \hline
+			1200 & 1200 & 86 & 56 & 442 & 4 \\ \hline
+			1300 & 1300 & 89 & 59 & 466 & 4 \\ \hline
+			1400 & 1400 & 90 & 60 & 510 & 4 \\ \hline
+			1500 & 1500 & 97 & 63 & 541 & 4 \\ \hline
+			1600 & 1600 & 100 & 66 & 573 & 4 \\ \hline
+			1700 & 1700 & 102 & 67 & 624 & 4 \\ \hline
+			1800 & 1800 & 104 & 69 & 660 & 4 \\ \hline
+			1900 & 1900 & 109 & 71 & 664 & 4 \\ \hline
+			2000 & 2000 & 113 & 73 & 740 & 4 \\ \hline
+		\end{tabular}
+	\end{center}
+	\caption{The average calls of the distance function $D$ in the query processing depending on the size of the test
+		data set $S$.}
+	\label{fig:queryprocessing:tabular}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\begin{tikzpicture}
+			\begin{axis}[
+				ymin=0,
+				xmin=0,
+				xmax=2000,
+				xlabel=size of test data set $S$,
+				ylabel=average calls of distance function $D$,
+				legend pos=outer north east]
+				\addplot table {data/queryprocessing/fullsearch.csv};
+	            \addlegendentry{Full Search}
+	            \addplot table {data/queryprocessing/orchards.csv};
+	            \addlegendentry{Orchard}
+				\addplot table {data/queryprocessing/orchardsmb.csv};
+				\addlegendentry{Orchard MarkBits}
+	            \addplot table {data/queryprocessing/annulus.csv};
+	            \addlegendentry{Annulus}
+	            \addplot table {data/queryprocessing/aesa.csv};
+	            \addlegendentry{AESA}
+			\end{axis}
+		\end{tikzpicture}
+	\end{center}
+	\caption{The average calls of the distance function $D$ in the query processing depending on the size of the test
+		data set $S$ visualized with graphs.}
+	\label{fig:queryprocessing:graph}
+\end{figure}
+
+\paragraph{Standard deviation}
+
+As I saw that some of the algorithms needed more and more tries to stabilize the average result, I have calculated for
+every size of a set and every algorithm the standard deviation. In general it is no big surprise that algorithms that
+start with random initialization have fluctuating results, but especially the Annulus Method was very fragile.
+
+\begin{figure}
+	\begin{center}
+		\begin{tabular}{ | l | c | c | c | c | c |}
+			\hline
+		  	& Full Search & Orchard & Orchard MarkBits & Annulus & AESA \\ \hline
+		  	100 & 0 & 13 & 8 & 23 & 1 \\ \hline
+			200 & 0 & 17 & 11 & 46 & 1 \\ \hline
+			300 & 0 & 21 & 13 & 69 & 1 \\ \hline
+			400 & 0 & 25 & 15 & 94 & 1 \\ \hline
+			500 & 0 & 27 & 17 & 119 & 1 \\ \hline
+			600 & 0 & 29 & 19 & 144 & 1 \\ \hline
+			700 & 0 & 32 & 19 & 162 & 1 \\ \hline
+			800 & 0 & 33 & 21 & 190 & 1 \\ \hline
+			900 & 0 & 36 & 22 & 213 & 1 \\ \hline
+			1000 & 0 & 37 & 23 & 232 & 1 \\ \hline
+			1100 & 0 & 38 & 24 & 264 & 1 \\ \hline
+			1200 & 0 & 40 & 26 & 277 & 1 \\ \hline
+			1300 & 0 & 43 & 27 & 301 & 1 \\ \hline
+			1400 & 0 & 43 & 27 & 339 & 1 \\ \hline
+			1500 & 0 & 47 & 27 & 350 & 1 \\ \hline
+			1600 & 0 & 46 & 29 & 374 & 1 \\ \hline
+			1700 & 0 & 48 & 29 & 401 & 1 \\ \hline
+			1800 & 0 & 49 & 31 & 429 & 1 \\ \hline
+			1900 & 0 & 52 & 32 & 442 & 1 \\ \hline
+			2000 & 0 & 52 & 33 & 487 & 1 \\ \hline
+		\end{tabular}
+	\end{center}
+	\caption{The standard deviation of the calls of the distance function $D$ in the query processing depending on the
+		size of the test data set $S$.}
+	\label{fig:standarddeviation:tabular}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\begin{tikzpicture}
+			\begin{axis}[
+				ymin=0,
+				xmin=0,
+				xmax=2000,
+				xlabel=size of test data set $S$,
+				ylabel=standard deviation of calls of distance function $D$,
+				legend pos=outer north east]
+				\addplot table {data/standarddeviation/fullsearch.csv};
+	            \addlegendentry{Full Search}
+	            \addplot table {data/standarddeviation/orchards.csv};
+	            \addlegendentry{Orchard}
+				\addplot table {data/standarddeviation/orchardsmb.csv};
+				\addlegendentry{Orchard MarkBits}
+	            \addplot table {data/standarddeviation/annulus.csv};
+	            \addlegendentry{Annulus}
+	            \addplot table {data/standarddeviation/aesa.csv};
+	            \addlegendentry{AESA}
+			\end{axis}
+		\end{tikzpicture}
+	\end{center}
+	\caption{The standard deviation of the calls of the distance function $D$ in the query processing depending on the
+		size of the test data set $S$ visualized with graphs.}
+	\label{fig:standarddeviation:graph}
+\end{figure}
 

### 2016-05-10 program/src/main/java/fnnc/Application.java

@@ -140,7 +140,8 @@ public class Application {
     LinkedList<FastNearestNeighbourClassificator<Point2D.Double, Double>> algos =
         new LinkedList<FastNearestNeighbourClassificator<Point2D.Double, Double>>();
     algos.add(new FullSearch<Point2D.Double, Double>(distanceCalculator));
-    algos.add(new OrchardsAlgorithm<Point2D.Double>(distanceCalculator));
+    algos.add(new OrchardsAlgorithm<Point2D.Double>(distanceCalculator, false));
+    algos.add(new OrchardsAlgorithm<Point2D.Double>(distanceCalculator, true));
     algos.add(new AnnulusMethod<Point2D.Double>(distanceCalculator));
     algos.add(new Aesa<Point2D.Double>(distanceCalculator));
 

### 2016-05-10 program/src/main/java/fnnc/algo/OrchardsAlgorithm.java

@@ -15,14 +15,17 @@ public class OrchardsAlgorithm<T> extends FastNearestNeighbourClassificator<T, D
 
   private HashMap<Integer, LinkedList<DistanceObjectPair<Double, Integer>>> orderedLists;
   private HashMap<Integer, T> indexedObjects;
+  private boolean useMarkBits;
 
   /**
    * Creates an OrchardsAlgorithm object.
    */
   public OrchardsAlgorithm(
-      DistanceCalculator<T, Double> distanceCalculator
+      DistanceCalculator<T, Double> distanceCalculator,
+      boolean useMarkBits
   ) {
     super(distanceCalculator);
+    this.useMarkBits = useMarkBits;
   }
 
   /**
@@ -82,7 +85,7 @@ public class OrchardsAlgorithm<T> extends FastNearestNeighbourClassificator<T, D
     while (iterator.hasNext()) {
       DistanceObjectPair<Double, Integer> tempDistObjPair = iterator.next();
       int tempIndex = tempDistObjPair.getObject();
-      if (!markBits[tempIndex]) {
+      if (!this.useMarkBits || !markBits[tempIndex]) {
         T tempObject = this.indexedObjects.get(tempIndex);
         if (tempDistObjPair.getDistance() > 2 * currentDistanceToQuery) {
           break;

### 2016-05-10 program/src/test/java/fnnc/algo/OrchardsAlgorithmTest.java

@@ -9,6 +9,29 @@ import java.util.LinkedList;
 
 public class OrchardsAlgorithmTest {
   @Test
+  public void testCalculateNearestNeighbourMarkBits() {
+    DistanceCalculator distanceCalculator = new DistanceCalculator();
+    LinkedList<Point2D.Double> pointCollection = new LinkedList<Point2D.Double>();
+    pointCollection.add(new Point2D.Double(5.40, 9.80));
+    pointCollection.add(new Point2D.Double(1.64, 3.30));
+    pointCollection.add(new Point2D.Double(9.62, 3.19));
+    pointCollection.add(new Point2D.Double(0.33, 6.85));
+    pointCollection.add(new Point2D.Double(4.73, 6.12));
+    pointCollection.add(new Point2D.Double(5.26, 6.32));
+    pointCollection.add(new Point2D.Double(1.83, 6.58));
+    pointCollection.add(new Point2D.Double(5.98, 0.69));
+    pointCollection.add(new Point2D.Double(9.59, 8.10));
+    pointCollection.add(new Point2D.Double(3.76, 0.81));
+    OrchardsAlgorithm<Point2D.Double> fnncAlgo =
+        new OrchardsAlgorithm<Point2D.Double>(distanceCalculator, true);
+    fnncAlgo.preProcessing(pointCollection);
+    assertEquals(
+        new Point2D.Double(3.76, 0.81),
+        fnncAlgo.calculateNearestNeighbour(new Point2D.Double(4.42, 0.78))
+    );
+  }
+
+  @Test
   public void testCalculateNearestNeighbour() {
     DistanceCalculator distanceCalculator = new DistanceCalculator();
     LinkedList<Point2D.Double> pointCollection = new LinkedList<Point2D.Double>();
@@ -23,7 +46,7 @@ public class OrchardsAlgorithmTest {
     pointCollection.add(new Point2D.Double(9.59, 8.10));
     pointCollection.add(new Point2D.Double(3.76, 0.81));
     OrchardsAlgorithm<Point2D.Double> fnncAlgo =
-        new OrchardsAlgorithm<Point2D.Double>(distanceCalculator);
+        new OrchardsAlgorithm<Point2D.Double>(distanceCalculator, false);
     fnncAlgo.preProcessing(pointCollection);
     assertEquals(
         new Point2D.Double(3.76, 0.81),

### 2016-05-10 paper/paper.tex
semifinish

@@
 
-\subsubsection{Preprocessing}
+\paragraph{Preprocessing}
 
@@
 
-\subsubsection{Query Processing}
+\paragraph{Query Processing}
 
@@
 
+\subsubsection{Orchard’s Algorithm with marked bits}
+
+There exists a improved version of the Orchard’s Algorithm to ensure that no distance between an item $x \in S$ and $q$
+is calculated twice. This can achieved by boolean flags for every item in the query processing of the Orchard’s
+Algorithm.
+
 \subsection{Annulus Method}
@@
 metric Levenshtein distance or in higher dimensional vector spaces.\\
-In general a benchmark is affected by the implementation, by the executing machine, by the domain of the problem
-and the distribution of the example. As the following benchmarks only counting the calls of the distance function, they
-aren't affected by the implementation or the executing machine.
+In general a benchmark is affected by the implementation, by the programming language, by the executing machine, by the
+domain of the problem and the distribution of the example. As the following benchmarks only counting the calls of the
+distance function, they are not affected by the programming language or the executing machine.
 
@@
 
-The algorithms above are all implemented in Java and can be found in the following git repository\\
-\url{https://github.com/GordonLesti/FastNearestNeighbourClassification}.\\
+The algorithms above are all implemented in Java and can be found in the following git
+repository\footnote[1]{\url{https://github.com/GordonLesti/FastNearestNeighbourClassification}}.\\
+Since the benchmakrs are independed from the programming language and the executing machine, they use sometimes not the
+most effective data structures, but that never effects the logical flow of the algorithms.\\
 
@@
 class needs to extend from the abstract class\\ \verb+FastNearestNeighbourClassificator<T, D extends Comparable<D>>+
-that can be found in the package \verb+fnnc.algo+. The generic \verb+T+ represents an object from the set $\mathbb{U}$
+that\\ can be found in the package \verb+fnnc.algo+. The generic \verb+T+ represents an object from the set $\mathbb{U}$
 and the generic \verb+D+ represents the distance and has to be of type \verb+Comparable+ from the package
@@
 
-The abstract class\\ \verb+FastNearestNeighbourClassificator<T, D extends Comparable<D>>+ has two protected class
+The abstract class\\ \verb+FastNearestNeighbourClassificator<T, D extends Comparable<D>>+ has\\ two protected class
 variables:
@@
 
-A instance of type \verb+FastNearestNeighbourClassificator+ shouldn't and can't calculate the distance between two
-objects. So that a instance of \verb+DistanceCalculator+ should be injected into the constructor. All implemented
-algorithms exclude the \verb+FullSearch+ require that the \verb+DistanceCalculator+ returns a distance of type
-\verb+Double+ instead of only \verb+Comparable+. This is connected with the fact that only the Full Search can operate
-in a not metric space.
+A instance of type \verb+FastNearestNeighbourClassificator+ should not be allowed and can not calculate the distance
+between two objects. So that a instance of \verb+DistanceCalculator+ should be injected into the constructor. All
+implemented algorithms exclude the \verb+FullSearch+ require that the\\ \verb+DistanceCalculator+ returns a distance of
+type \verb+Double+ instead of only\\ \verb+Comparable+. This is connected with the fact that only the Full Search can
+operate in a not metric space.
 
@@
 	\item a public final function \verb+calculateDistance+ that takes two objects of type \verb+T+, increases the
-		internal count and returns the result of \verb+internalCalculateDistance+
+		internal count and returns the result of\\ \verb+internalCalculateDistance+
 	\item a public final function \verb+reset+ that resets the internal count
@@
 
+The results of the preprocessing are static. Figure~\ref{fig:preprocessing:tabular} and
+figure~\ref{fig:preprocessing:graph} summarizing again the complexity of the preprocessing for every algorithm
+depending on the size of set $S$.
+
 \begin{figure}
 	\begin{center}
-		\begin{tabular}{ | l | c | c | c | c | c |}
+		\begin{tabular}{| l | c | c | c | c | c |}
 			\hline
@@
 	\begin{center}
-		\begin{tabular}{ | l | c | c | c | c | c |}
+		\begin{tabular}{| l | c | c | c | c | c |}
 			\hline
@@
 
+\section{Conclusions}
+
+\paragraph{Full Search} The results may leave the impression that the Full Search is not a good choice. But this
+algorithm remains useful if the set $S$ changes completely or when $\mathbb{U}$ is no metric space.
+
+\paragraph{Annulus Method} The Annulus Method has a very complex query processing that
+
+\paragraph{Orchard’s Algorithm with and without marking bits} In the query processing the Orchard’s Algorithm with
+marking bits consumed on average only 66\% of the distance function calls that the algorithm needed without marking
+bits.
+
+\section{Future work}
+
+The LAESA algorithm and Metric Trees are missing in the benchmarks above. Both approaches are promising and their
+results compared to algorithms of this paper would be interesting.
+
 \end{document}

### 2016-05-11 paper/paper.tex
finished

@@
 Stefan Fricke\\\vspace{2\baselineskip}
-April 2016\\
-Betreuer: Stephan Spiegel\\\vspace{1\baselineskip}}}}
+May 2016\\
+Supervisor: Stephan Spiegel\\\vspace{1\baselineskip}}}}
 
@@
 
-HERE COMES THE INTRODUCTION.
+Kenneth L. Clarkson wrote the paper \textit{Nearest-Neighbor Searching and Metric Space Dimensions}[1] which deals
+amongst other approaches with the topic nearest neighbour search algorithms that use the triangle inequality. This paper
+focuses on three of them.
 
@@
 \paragraph{Preprocessing}
-During the preprocessing the algorithm prepares the given set $\mathbb{S}$ for his needs.
+During the preprocessing the algorithm prepares the given set $\mathbb{S}$ for its needs.
 
@@
 The advantage compared to the following algorithms is, that the Full Search works also in not metric spaces. The Full
-Search needs no preprocessing.
+Search does not need a preprocessing.
 
@@
 
-When calling the query processing with query $q$, the algorithm will randomly select one object $c \in S$ as initial
+When calling the query processing with query $q$, the algorithm will randomly select one item $c \in S$ as initial
 candidate and calculate $D(c, q)$. Afterwards the algorithm walks over the ordered list of $c$ and with every picked $s$
-from the list the algorithm calculates $D(l, q)$. If $D(l, q)$ is smaller than $D(c, q)$, $l$ is the new candidate $c$
-and the algorithm walks over the list of $l$. The algorithm aborts if it reaches the end of a list or if
-$D(c, s) > 2D(c, q)$. The current candidate $c$ is the nearest neighbour.
+from the list the algorithm calculates $D(l, q)$. Item $l$ is the new candidate $c$ if $D(l, q)$ is smaller than
+$D(c, q)$. Thereafter the algorithm walks over the list of $l$. The algorithm interupts if it reaches the end of a list
+or if $D(c, s) > 2D(c, q)$. The current candidate $c$ is the nearest neighbour.
 
@@
 
-There exists a improved version of the Orchard’s Algorithm to ensure that no distance between an item $x \in S$ and $q$
-is calculated twice. This can achieved by boolean flags for every item in the query processing of the Orchard’s
+There is a improved version of the Orchard’s Algorithm to ensure that no distance between an item $x \in S$ and $q$
+is calculated twice. This can be achieved by boolean flags for every item during query processing of the Orchard’s
 Algorithm.
@@
 
-The Annulus Method works a little bit similar to the Orchard’s Algorithm, but with a less complex preprocessing.
-
 \paragraph{Preprocessing}
 
-Instead of generating a list for all $x \in S$, the Annulus Method generates just one list for a random $p^* \in S$. In
-the preprocessing the algorithm generates one list that contains all $x \in S$ with their distance $D(p^*, x)$. This
+Instead of generating a list for all $x \in S$, the Annulus Method generates just one list for a random $p^* \in S$.
+During preprocessing the algorithm generates one list which contains all $x \in S$ with their distance $D(p^*, x)$. This
 list will be ordered ascending to the distance. For a set $S$ with size $n$, the preprocessing will call the distance
@@
 The query processing of the Annulus Method starts by picking a random candidate $c \in S$ from the ordered list of
-$p^*$. Afterwards the algorithm walks alternating away from $p^*$ and back to him in the list. If the current object $s$
-has $D(s, q) < D(c, q)$, the algorithm sets $s$ as the new candidate $c$. If the current object $s$ is under $c$ in the
-list and $D(p^*, s) < D(p^*, q) - D(c, q)$, the algorithm can ignore all objects under $s$ in the list. If the current
-object $s$ is above $c$ in the list and $D(p^*, s) > D(p^*, q) + D(c, q)$, the algorithm can ignore all objects above
-$s$ in the list. The object $c$ is the nearest neighbour, if the entire list is traversed.
+$p^*$. Afterwards the algorithm walks alternating away from $p^*$ and back to it in the list. If the current item $s$
+has $D(s, q) < D(c, q)$, the algorithm sets $s$ as the new candidate $c$. If the current item $s$ is under $c$ in the
+list and $D(p^*, s) < D(p^*, q) - D(c, q)$, all items under $s$ in the list will be ignored. If the current
+item $s$ is above $c$ in the list and $D(p^*, s) > D(p^*, q) + D(c, q)$, the algorithm will ignore all items above
+$s$ in the list. The item $c$ is the nearest neighbour, if the entire list is traversed.
 
@@
 
-When starting with the query processing, the algorithm generates a list for all objects $x \in S$ with a bounded
+When starting with the query processing, the algorithm generates a list for all items $x \in S$ with a bounded
 distance $D_P(x, q) = -\infty$ and initialize $r = \infty$ as smallest distance to $q$. Afterwards the algorithm
@@
 \begin{itemize}
-	\item pick and remove $x$ from the list with the smallest $D_p(x, q)$ or a random one in the first iteration
+	\item pick and remove $x$ from the list with the smallest $D_p(x, q)$ or a random one during first iteration
 	\item calculate $D(x, q)$
@@
 will compare the calls of the distance function that the algorithm needs for preprocessing and for finding a nearest
-neighbour. Those benchmarks can make sense when the distance function has a heavy complexity. For example the string
+neighbour. Those benchmarks are useful when the distance function has a heavy complexity. For example the string
 metric Levenshtein distance or in higher dimensional vector spaces.\\
@@
 domain of the problem and the distribution of the example. As the following benchmarks only counting the calls of the
-distance function, they are not affected by the programming language or the executing machine.
+distance function its are not affected by the programming language or the executing machine.
 
@@
 repository\footnote[1]{\url{https://github.com/GordonLesti/FastNearestNeighbourClassification}}.\\
-Since the benchmakrs are independed from the programming language and the executing machine, they use sometimes not the
-most effective data structures, but that never effects the logical flow of the algorithms.\\
+Since the benchmarks are independed from the programming language and the executing machine, the implementation of the
+algorithms uses sometimes not the most effective data structures. But that never effects the logical flow of the
+algorithms.\\
 
-A nearest neighbour algorithm implemented in Java should handle every type of object that a set $\mathbb{U}$ can
+A nearest neighbour algorithm implemented in Java should handle every type of objects that a set $\mathbb{U}$ can
 represent under the condition that there is a metric on $\mathbb{U}$. Because of that, a nearest neighbour algorithm
@@
 
-A instance of type \verb+FastNearestNeighbourClassificator+ should not be allowed and can not calculate the distance
-between two objects. So that a instance of \verb+DistanceCalculator+ should be injected into the constructor. All
+An instance of type \verb+FastNearestNeighbourClassificator+ should not be allowed and can not calculate the distance
+between two objects. So that an instance of \verb+DistanceCalculator+ should be injected into the constructor. All
 implemented algorithms exclude the \verb+FullSearch+ require that the\\ \verb+DistanceCalculator+ returns a distance of
@@
 	\end{center}
-	\caption{The calls of the distance function $D$ in the preprocessing depending on the size $n$ of the test data set
+	\caption{The calls of the distance function $D$ during preprocessing depending on the size $n$ of the test data set
 		$S$.}
@@
 	\end{center}
-	\caption{The average calls of the distance function $D$ in the preprocessing depending on the size of the test data
+	\caption{The average calls of the distance function $D$ during preprocessing depending on the size of the test data
 		set $S$ visualized with graphs.}
@@
 \subsubsection{Query Processing}
+
+Figure~\ref{fig:queryprocessing:tabular} and figure~\ref{fig:queryprocessing:graph} show the results of the query
+processing for all algorithms.
 
@@
 	\end{center}
-	\caption{The average calls of the distance function $D$ in the query processing depending on the size of the test
+	\caption{The average calls of the distance function $D$ during query processing depending on the size of the test
 		data set $S$.}
@@
 	\end{center}
-	\caption{The average calls of the distance function $D$ in the query processing depending on the size of the test
+	\caption{The average calls of the distance function $D$ during query processing depending on the size of the test
 		data set $S$ visualized with graphs.}
@@
 
-As I saw that some of the algorithms needed more and more tries to stabilize the average result, I have calculated for
-every size of a set and every algorithm the standard deviation. In general it is no big surprise that algorithms that
-start with random initialization have fluctuating results, but especially the Annulus Method was very fragile.
+Some of the algorithms needed more and more tries to stabilize the average result of the query processing.
+Figure~\ref{fig:standarddeviation:tabular} and figure~\ref{fig:standarddeviation:graph} show the standard deviation of
+the results for every algorithm depending on the size of set $S$.
 
@@
 	\end{center}
-	\caption{The standard deviation of the calls of the distance function $D$ in the query processing depending on the
+	\caption{The standard deviation of the calls of the distance function $D$ during query processing depending on the
 		size of the test data set $S$.}
@@
 	\end{center}
-	\caption{The standard deviation of the calls of the distance function $D$ in the query processing depending on the
+	\caption{The standard deviation of the calls of the distance function $D$ during query processing depending on the
 		size of the test data set $S$ visualized with graphs.}
@@
 \paragraph{Full Search} The results may leave the impression that the Full Search is not a good choice. But this
-algorithm remains useful if the set $S$ changes completely or when $\mathbb{U}$ is no metric space.
+algorithm remains useful if the set $S$ changes completely with every new query or when $\mathbb{U}$ is no metric space.
 
-\paragraph{Annulus Method} The Annulus Method has a very complex query processing that
+\paragraph{Annulus Method} The Annulus Method has a very complex query processing. But on a frequently changing set $S$
+a affordable preprocessing. Other algorithms with more complex preprocessing maybe hit its limits on huge sets that
+can be handled by the Annulus Method. The Annulus Method was the algorithm with the highest standard deviation during
+the benchmarks.
 
-\paragraph{Orchard’s Algorithm with and without marking bits} In the query processing the Orchard’s Algorithm with
+\paragraph{Orchard’s Algorithm with and without marking bits} During query processing the Orchard’s Algorithm with
 marking bits consumed on average only 66\% of the distance function calls that the algorithm needed without marking
 bits.
+
+\paragraph{AESA} Depending on the benchmarks above, the AESA should be preferred instead of the Orchard’s Algorithm.
+Both algorithms have a very complex preprocessing that may not work on very huge sets. But the AESA consumes more less
+calls of the distance function. The impact on real world applications should be tested. Beside the Full Search the AESA
+was the most stable algorithm.
 
@@
 
+\begin{thebibliography}{4}
+	\bibitem{url} Kenneth L. Clarkson, \"Nearest-Neighbor Searching and Metric Space Dimensions\" (October 2005), \url{http://kenclarkson.org/nn_survey/p.pdf}
+\end{thebibliography}
+
 \end{document}

### 2016-05-11 paper/paper.tex
finished

@@
 \paragraph{Preprocessing}
-During the preprocessing the algorithm prepares the given set $\mathbb{S}$ for its needs.
+During the preprocessing the algorithm prepares the given set $S$ for its needs.
 
@@
 \begin{thebibliography}{4}
-	\bibitem{url} Kenneth L. Clarkson, \"Nearest-Neighbor Searching and Metric Space Dimensions\" (October 2005), \url{http://kenclarkson.org/nn_survey/p.pdf}
+	\bibitem{url} Kenneth L. Clarkson, "Nearest-Neighbor Searching and Metric Space Dimensions" (October 2005), \url{http://kenclarkson.org/nn_survey/p.pdf}
 \end{thebibliography}

### 2016-06-22 paper/paper.tex
paper is final

@@
 \usepackage{pgfplots}
-\usepackage{algorithm}
-\usepackage{algorithmic}
+\usepackage{float}
+\usepackage{tabularx}
+\usepgfplotslibrary{groupplots}
 
@@
 \noindent\keywordname\enspace\ignorespaces#1}
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
 
 \begin{document}
+
+\setlength{\tabcolsep}{12pt}
 
@@
 \subtitle{\textnormal{\small{Seminar\\
-Intelligente Software-Systeme\\
-Sommersemester 2015\\\vspace{1\baselineskip}
-Stefan Fricke\\\vspace{2\baselineskip}
+Intelligent Software Systems\\
+Summer semester 2015\\\vspace{1\baselineskip}
+Lecturer: Stefan Fricke\\\vspace{2\baselineskip}
 May 2016\\
@@
 
-\author{Gordon Lesti\\313249\\Studiengang: Informatik\\gordon.lesti@campus.tu-berlin.de\\\vspace{5\baselineskip}}
+\author{Gordon Lesti\\313249\\Course of studies: Bachelor of Computer Science\\gordon.lesti@campus.tu-berlin.de\\\vspace{5\baselineskip}}
 
@@
 \maketitle
-\pagenumbering{roman}
 
@@
 This term paper is about nearest neighbour classifiers which work with the triangle inequality of metric spaces. The
-Orchard’s Algorithm, the Annulus Method and the AESA will be explained on examples and compared to the Full Search.
+Orchard’s Algorithm, the Annulus Method and the AESA will be explained and compared to the Full Search.
 Benchmarks will show the advantages and disadvantages of the three algorithms. Counting the calls of the distance
@@
 
-\tableofcontents
-\addcontentsline{toc}{section}{Table of Contents}
-
-\newpage
-\pagenumbering{arabic}
-
 \section{Introduction}
 
-Kenneth L. Clarkson wrote the paper \textit{Nearest-Neighbor Searching and Metric Space Dimensions}[1] which deals
-amongst other approaches with the topic nearest neighbour search algorithms that use the triangle inequality. This paper
-focuses on three of them.
+Kenneth L. Clarkson wrote the paper \textit{Nearest-Neighbor Searching and Metric Space Dimensions} \cite{Clarkson}
+which deals amongst other approaches with the topic nearest neighbour search algorithms that use the triangle
+inequality. This paper focuses on three of them.
+
+\subsection{Notation}
+
+Table~\ref{tab:notation} explains the basic variables that are used in this paper.
+
+\begin{table}[H]
+	\begin{center}
+		\begin{tabularx}{\textwidth}{c X}
+			\textbf{Symbol} & \textbf{Description}\\
+			\hline
+			$\mathbb{U}$ & a set containing all items of the domain\\
+			$S$ & a set with $S \subset \mathbb{U}$\\
+			$n$ & the size of set $S$\\
+			$d$ & a distance function on $\mathbb{U}$ with $d: \mathbb{U} \times \mathbb{U} \to \mathbb{R}$\\
+			$q$ & a query with $q \in \mathbb{U}$\\
+			$x$ & a temporary variable with $x \in S$\\
+			$a$ & nearest neighbour to $q$ with $a \in S$ and $d(a, q) \le d(x, q)$ $\forall x \in S$\\
+			$r$ & the minimal distance $d(a, q)$ with $r \in \mathbb{R}$
+		\end{tabularx}
+	\end{center}
+	\caption{A table of basic variables that are used in this paper.}
+	\label{tab:notation}
+\end{table}
 
@@
 
-The mission of a nearest neighbour search algorithm is to find in a given set of items, that item with the smallest
-distance to a given query item.\\
-The requirements are:
-\begin{itemize}
-	\item a set $\mathbb{U}$
-	\item a distance function $D$ on $\mathbb{U}$, with $d: \mathbb{U} \times \mathbb{U} \to \mathbb{R}$
-	\item a set $S \subset \mathbb{U}$ with size $n$
-	\item a query $q \in \mathbb{U}$
-\end{itemize}
-The solution is:
-\begin{itemize}
-	\item an $a \in S$, with $D(q, a) \le D(q, x)$ for all $x \in S$
-\end{itemize}
+$S$ is a subset of $\mathbb{U}$. The set $S$ of size $n$ and a distance function $d$ on $\mathbb{U}$ is given. A nearest
+neighbour search algorithm has the mission to find the nearest neighbour $a \in S$ of a given query $q \in \mathbb{U}$,
+so that $d(a, q) \le d(x, q)$ $\forall x \in S$.
+
+\paragraph{Example} A simple real world example would be a company with many stores which are distributed over a
+country. This company has a small online tool to find the next store to a given location of a customer. The set
+$\mathbb{U}$ would be a infinite set of all locations over the whole country. The distance function $d$ calculates the
+distance between two locations. The set $S$ would contain the locations of the stores. The customer enters his current
+location that is represented by the query $q$. The tool should return the location of store $a$ that has the smallest
+distance to the customers location $q$.
 
@@
 
-Every nearest neighbour search algorithm can be divided into two steps.
+Every nearest neighbour search algorithm can be divided into two steps. The preprocessing and the query processing.
+
 \paragraph{Preprocessing}
-During the preprocessing the algorithm prepares the given set $S$ for its needs.
+During the preprocessing the algorithm prepares the given set $S$ for the nedds of the query processing. The set $S$ can
+be transformed into different data structures. Those data structures are the basis for a fast calculation of the nearest
+neighbour during the query processing. The data structures are independent from the query $q$.
 
@@
 
-The Full Search is the upper bound for the following algorithms. Exactly $n$ calls of the distance function are required
-to find the nearest neighbour in a given $S$ of size $n$.\\
+The Full Search is the upper bound for the following algorithms. This algorithm has no preprocessing. The query
+processing will calculate the distance $d(x, q)$ for every $x \in S$. Nearest Neighbour is the the item from the set $S$
+with the smallest distance to query $q$.\\
 
-\begin{algorithm}[H]
-	\caption{Full Search}
-	\label{fullsearch}
-	\begin{algorithmic}
-		\REQUIRE query $q \in \mathbb{U}$, set $S \subset \mathbb{U}$ of size $n$, distance function $D$
-		\ENSURE $a \in S$ with $D(q, a) \le D(q, x)$ $\forall x \in S$
-		\STATE $r := \infty$
-		\STATE $a :=$ NULL
-		\FORALL{$x \in S$}
-			\STATE $xd := D(x, q)$
-			\IF{$sd < r$}
-				\STATE $r := xd$
-				\STATE $a := x$
-			\ENDIF
-		\ENDFOR
-		\RETURN $a$
-	\end{algorithmic}
-\end{algorithm}
-
-The advantage compared to the following algorithms is, that the Full Search works also in not metric spaces. The Full
-Search does not need a preprocessing.
+Exactly $n$ calls of the distance function are required to find the nearest neighbour in a given $S$ of size $n$. The
+advantage compared to the following algorithms is, that the Full Search works for none metric spaces.
 
@@
 
+The Orchard’s Algorithm was invented by Michael T. Orchard \cite{Orchard}. Table~\ref{tab:notation:orchard} explains
+additional variables that are used in the Orchard’s Algorithm.
+
+\begin{table}[H]
+	\begin{center}
+		\begin{tabularx}{\textwidth}{c X}
+			\textbf{Symbol} & \textbf{Description}\\
+			\hline
+			$p$ & a temporary variable with $p \in S$\\
+			$c$ & is a candidate for the nearest neighbour with $c \in S$\\
+			$s$ & a temporary variable with $s \in S$\\
+		\end{tabularx}
+	\end{center}
+	\caption{A table of additional variables that are used in the Orchard’s Algorithm.}
+	\label{tab:notation:orchard}
+\end{table}
+
 \paragraph{Preprocessing}
 
-The preprocessing of the Orchard’s Algorithm has a high complexity. For every $p \in S$, the algorithm will generate a
-list that contains all $x \in S\setminus\left\{ {p}\right\}$ with their distance $D(p, x)$. Those lists will be ordered
-ascending to the distance. For a set $S$ with size $n$, the preprocessing will call the distance function
+The preprocessing of the Orchard’s Algorithm has a high complexity. For every item $p \in S$, the algorithm will
+generate a list that contains all $x \in S\setminus\left\{ {p}\right\}$ with their distance $d(p, x)$. Those lists will
+be ordered ascending to the distance. For a set $S$ with size $n$, the preprocessing will call the distance function
 $\frac{n(n-1)}{2}$ times and will sort $n$ lists of size $n-1$.
@@
 When calling the query processing with query $q$, the algorithm will randomly select one item $c \in S$ as initial
-candidate and calculate $D(c, q)$. Afterwards the algorithm walks over the ordered list of $c$ and with every picked $s$
-from the list the algorithm calculates $D(l, q)$. Item $l$ is the new candidate $c$ if $D(l, q)$ is smaller than
-$D(c, q)$. Thereafter the algorithm walks over the list of $l$. The algorithm interupts if it reaches the end of a list
-or if $D(c, s) > 2D(c, q)$. The current candidate $c$ is the nearest neighbour.
+candidate and calculate $d(c, q)$. Afterwards the algorithm walks over the ordered list of $c$ and with every picked $s$
+from the list the algorithm calculates $d(s, q)$. Item $s$ is the new candidate $c$ if $d(s, q)$ is smaller than
+$d(c, q)$. Thereafter the algorithm walks over the list of $s$. The algorithm interupts if it reaches the end of a list
+or if $d(c, s) > 2d(c, q)$. The current candidate $c$ is the nearest neighbour.
 
@@
 
+The Annulus Method is also described in \cite{Clarkson}. Table~\ref{tab:notation:annulus} explains additional variables
+that are used in the Annulus Method.
+
+\begin{table}[H]
+	\begin{center}
+		\begin{tabularx}{\textwidth}{c X}
+			\textbf{Symbol} & \textbf{Description}\\
+			\hline
+			$p^*$ & a pivot item with $p^* \in S$\\
+			$c$ & is a candidate for the nearest neighbour with $c \in S$\\
+			$s$ & a temporary variable with $s \in S$\\
+		\end{tabularx}
+	\end{center}
+	\caption{A table of additional variables that are used in the Annulus Method.}
+	\label{tab:notation:annulus}
+\end{table}
+
 \paragraph{Preprocessing}
@@
 Instead of generating a list for all $x \in S$, the Annulus Method generates just one list for a random $p^* \in S$.
-During preprocessing the algorithm generates one list which contains all $x \in S$ with their distance $D(p^*, x)$. This
+During preprocessing the algorithm generates one list which contains all $x \in S$ with their distance $d(p^*, x)$. This
 list will be ordered ascending to the distance. For a set $S$ with size $n$, the preprocessing will call the distance
@@
 $p^*$. Afterwards the algorithm walks alternating away from $p^*$ and back to it in the list. If the current item $s$
-has $D(s, q) < D(c, q)$, the algorithm sets $s$ as the new candidate $c$. If the current item $s$ is under $c$ in the
-list and $D(p^*, s) < D(p^*, q) - D(c, q)$, all items under $s$ in the list will be ignored. If the current
-item $s$ is above $c$ in the list and $D(p^*, s) > D(p^*, q) + D(c, q)$, the algorithm will ignore all items above
+has $d(s, q) < d(c, q)$, the algorithm sets $s$ as the new candidate $c$. If the current item $s$ is under $c$ in the
+list and $d(p^*, s) < d(p^*, q) - d(c, q)$, all items under $s$ in the list will be ignored. If the current
+item $s$ is above $c$ in the list and $d(p^*, s) > d(p^*, q) + d(c, q)$, the algorithm will ignore all items above
 $s$ in the list. The item $c$ is the nearest neighbour, if the entire list is traversed.
@@
 
+The Approximating and Eliminating Search Algorithm, or AESA was invented by Michael T. Orchard \cite{Ruiz}.
+Table~\ref{tab:notation:aesa} explains additional variables that are used in the AESA.
+
+\begin{table}[H]
+	\begin{center}
+		\begin{tabularx}{\textwidth}{c X}
+			\textbf{Symbol} & \textbf{Description}\\
+			\hline
+			$d_P$ & a distance function that works as lower bound for the real distance function $d$.
+				With $d_{P \cup \left\{ {y}\right\}}(x, q) = \max\left\{ {d_P(x, q), |d(y, q) - d(x, y)|}\right\}$ and
+				$d_{\emptyset}(x, q) = -\infty$\\
+			$y$ & a temporary variable with $y \in S$\\
+			$P$ & a set of items with $P \subset S$
+		\end{tabularx}
+	\end{center}
+	\caption{A table of additional variables that are used in the AESA.}
+	\label{tab:notation:aesa}
+\end{table}
+
 \paragraph{Preprocessing}
@@
 The preprocessing for the AESA is starting the same way as the preprocessing of the Orchard’s Algorithm. The algorithm
-calculates the distance $D(x, y)$ of every $x \in S$ to every $y \in S\setminus\left\{ {x}\right\}$. But instead of
+calculates the distance $d(x, y)$ of every $x \in S$ to every $y \in S\setminus\left\{ {x}\right\}$. But instead of
 writing those distances into lists and sorting them, the algorithm writes those distances into a matrix to access them
-quickly. For a set $S$ with size $n$, the preprocessing will call the distance function $\frac{n(n-1)}{2}$ times and
-will sort $n$ lists of size $n-1$.
+quickly. This matrix would be symmetric. The algorithm can use also a hash table with an unsorted pair of items as key
+instead of an symmetric matrix. This data structure would bisect the memory usage. For a set $S$ with size $n$, the
+preprocessing will call the distance function $\frac{n(n-1)}{2}$ times.
 
@@
 When starting with the query processing, the algorithm generates a list for all items $x \in S$ with a bounded
-distance $D_P(x, q) = -\infty$ and initialize $r = \infty$ as smallest distance to $q$. Afterwards the algorithm
+distance $d_P(x, q) = -\infty$ and initialize $r = \infty$ as smallest distance to $q$. Afterwards the algorithm
 iterates the following steps until the list is empty.
 \begin{itemize}
-	\item pick and remove $x$ from the list with the smallest $D_p(x, q)$ or a random one during first iteration
-	\item calculate $D(x, q)$
-	\item set $r = D(x, q)$ if $r > D(x, q)$ and remember $x$ as current nearest neighbour
-	\item for all $y$ from the list, set $D_P(y, q) = max(D_P(y, q), |D(x, q) - D(x, y)|)$ and remove $y$ from the list
-		if the new $D_P(y, q) > r$
+	\item pick and remove $x$ from the list with the smallest $d_p(x, q)$ or a random one during first iteration and add
+		$x$ to the set $P$
+	\item calculate $d(x, q)$
+	\item set $r = d(x, q)$ if $r > d(x, q)$ and remember $x$ as current nearest neighbour
+	\item for all $y$ from the list, update $d_P(y, q) = max(d_P(y, q), |d(x, q) - d(x, y)|)$ and remove $y$ from the
+		list if the new $d_P(y, q) > r$
 \end{itemize}
@@
 
-As described above, the following benchmarks will not compare the runtime of the mentioned algorithms. The benchmarks
-will compare the calls of the distance function that the algorithm needs for preprocessing and for finding a nearest
-neighbour. Those benchmarks are useful when the distance function has a heavy complexity. For example the string
-metric Levenshtein distance or in higher dimensional vector spaces.\\
+The benchmarks will compare the calls of the distance function that the algorithm needs for preprocessing and for
+finding a nearest neighbour. Those benchmarks are useful when the distance function has a heavy complexity. For example
+the string metric Levenshtein distance or in higher dimensional vector spaces.\\
 In general a benchmark is affected by the implementation, by the programming language, by the executing machine, by the
@@
 \subsection{Implementation}
+All presented algorithms are implemented in Java. The implementation of the algorithms and the benchmarks are open
+source and available on GitHub\footnote{https://github.com/GordonLesti/FastNearestNeighbourClassification}.
 
-The algorithms above are all implemented in Java and can be found in the following git
-repository\footnote[1]{\url{https://github.com/GordonLesti/FastNearestNeighbourClassification}}.\\
-Since the benchmarks are independed from the programming language and the executing machine, the implementation of the
-algorithms uses sometimes not the most effective data structures. But that never effects the logical flow of the
-algorithms.\\
+\subsubsection{Example data}
 
-A nearest neighbour algorithm implemented in Java should handle every type of objects that a set $\mathbb{U}$ can
-represent under the condition that there is a metric on $\mathbb{U}$. Because of that, a nearest neighbour algorithm
-class needs to extend from the abstract class\\ \verb+FastNearestNeighbourClassificator<T, D extends Comparable<D>>+
-that\\ can be found in the package \verb+fnnc.algo+. The generic \verb+T+ represents an object from the set $\mathbb{U}$
-and the generic \verb+D+ represents the distance and has to be of type \verb+Comparable+ from the package
-\verb+java.lang+.\\
-
-A possible example for the type \verb+T+ can be \verb+Point2D.Double+ from the package
-\verb+java.awt.geom+ and a possible way to implement a distance function would be the euclidean distance of type
-\verb+Double+.
-
-\subsubsection{FastNearestNeighbourClassificator}
-
-The abstract class\\ \verb+FastNearestNeighbourClassificator<T, D extends Comparable<D>>+ has\\ two protected class
-variables:
-\begin{itemize}
-	\item a \verb+distanceCalculator+ of type \verb+DistanceCalculator<T, D>+
-	\item a \verb+objectCollection+ of type \verb+Collection<T>+
-\end{itemize}
-and three simple class methods:
-\begin{itemize}
-	\item a constructor that takes an object of type \verb+DistanceCalculator<T, D>+ from the package
-		\verb+fnnc.model+ and sets the protected class variable
-	\item a default function \verb+preProcessing+ that takes a \verb+Collection<T>+ from the package
-		\verb+java.util+ and sets the protected class variable
-	\item a abstract function \verb+calculateNearestNeighbour+ that takes the query object of type \verb+T+ and
-		returns the nearest neighbour object of type \verb+T+
-\end{itemize}
-
-An instance of type \verb+FastNearestNeighbourClassificator+ should not be allowed and can not calculate the distance
-between two objects. So that an instance of \verb+DistanceCalculator+ should be injected into the constructor. All
-implemented algorithms exclude the \verb+FullSearch+ require that the\\ \verb+DistanceCalculator+ returns a distance of
-type \verb+Double+ instead of only\\ \verb+Comparable+. This is connected with the fact that only the Full Search can
-operate in a not metric space.
-
-\subsubsection{DistanceCalculator}
-
-The abstract class\\ \verb+DistanceCalculator<Point2D.Double, Double>+ has just one private \verb+count+ of type
-\verb+int+ and three class methods:
-\begin{itemize}
-	\item a public final function \verb+calculateDistance+ that takes two objects of type \verb+T+, increases the
-		internal count and returns the result of\\ \verb+internalCalculateDistance+
-	\item a public final function \verb+reset+ that resets the internal count
-	\item a protected abstract function \verb+internalCalculateDistance+ that takes two objects of type \verb+T+ and
-		returns the distance object of type \verb+D+
-\end{itemize}
-
-\subsection{Example data}
-
-The benchmarks will use a \verb+java.util.Collection+ of type\\ \verb+java.awt.geom.Point2D+ that are representing
-points in $\mathbb{R}^2$. For every size $n \in \left\{ {100, 200, \dots, 1900, 2000}\right\}$, every algorithm will get
-thousand sets of size $n$ with randomly generated points. The class\\ \verb+fnnc.model.point2ddouble.DistanceCalculator+
-will count every call of the function \verb+internalCalculateDistance+ and after all the application will calculate the
-average of the calls for every algorithm.
+Every algorithm is working on the same test data as the other algorithms. The items for the benchmarks are double
+floating points in $\left\{ {(x, y) \in \mathbb{R}^2|0 \leq x < 1, 0 \leq y < 1}\right\}$. One thousand test sets with
+randomly generated points are created for every size $n \in \left\{ {100, 200, \dots, 1900, 2000}\right\}$. The
+application has calculated the average calls of the distance function for every algorithm over the one thousand sets of
+every size.
 
@@
 
-The results of the preprocessing are static. Figure~\ref{fig:preprocessing:tabular} and
-figure~\ref{fig:preprocessing:graph} summarizing again the complexity of the preprocessing for every algorithm
-depending on the size of set $S$.
+The results of the preprocessing are static. Table~\ref{tab:preprocessing} summarizing again the complexity of the
+preprocessing for every algorithm depending on the size of set $S$.
 
-\begin{figure}
-	\begin{center}
+\setlength{\tabcolsep}{6pt}
+
+\begin{table}[H]
+	\begin{center}{\tiny
 		\begin{tabular}{| l | c | c | c | c | c |}
@@
 		  	$n$ & 0 & $\frac{n(n-1)}{2}$ & $\frac{n(n-1)}{2}$ & $n$ & $\frac{n(n-1)}{2}$ \\ \hline
-		\end{tabular}
+		\end{tabular}}
 	\end{center}
-	\caption{The calls of the distance function $D$ during preprocessing depending on the size $n$ of the test data set
+	\caption{The calls of the distance function $d$ during preprocessing depending on the size $n$ of the test data set
 		$S$.}
-	\label{fig:preprocessing:tabular}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\begin{tikzpicture}
-			\begin{axis}[
-				ymin=0,
-				xmin=0,
-				xmax=2000,
-				xlabel=size of test data set $S$,
-				ylabel=calls of distance function $D$,
-				legend pos=outer north east]
-				\addplot table {data/preprocessing/fullsearch.csv};
-	            \addlegendentry{Full Search}
-	            \addplot table {data/preprocessing/orchards.csv};
-	            \addlegendentry{Orchard}
-				\addplot table {data/preprocessing/orchardsmb.csv};
-				\addlegendentry{Orchard MarkBits}
-	            \addplot table {data/preprocessing/annulus.csv};
-	            \addlegendentry{Annulus}
-	            \addplot table {data/preprocessing/aesa.csv};
-	            \addlegendentry{AESA}
-			\end{axis}
-		\end{tikzpicture}
-	\end{center}
-	\caption{The average calls of the distance function $D$ during preprocessing depending on the size of the test data
-		set $S$ visualized with graphs.}
-	\label{fig:preprocessing:graph}
-\end{figure}
+	\label{tab:preprocessing}
+\end{table}
 
@@
 
-Figure~\ref{fig:queryprocessing:tabular} and figure~\ref{fig:queryprocessing:graph} show the results of the query
+Table~\ref{tab:queryprocessing} and figure~\ref{fig:queryprocessing} show the results of the query
 processing for all algorithms.
 
-\begin{figure}
-	\begin{center}
+\begin{table}[H]
+	\begin{center}{\tiny
 		\begin{tabular}{| l | c | c | c | c | c |}
@@
 		  	& Full Search & Orchard & Orchard MarkBits & Annulus & AESA \\ \hline
-		  	100 & 100 & 29 & 20 & 46 & 4 \\ \hline
-			200 & 200 & 39 &26 & 82 & 4 \\ \hline
-			300 & 300 & 46 & 30 & 117 & 4 \\ \hline
-			400 & 400 & 53 & 35 & 160 & 4 \\ \hline
-			500 & 500 & 57 & 40 & 189 & 4 \\ \hline
-			600 & 600 & 63 & 42 & 228 & 4 \\ \hline
-			700 & 700 & 68 & 44 & 263 & 4 \\ \hline
-			800 & 800 & 73 & 46 & 303 & 4 \\ \hline
-			900 & 900 & 78 & 50 & 341 & 4 \\ \hline
-			1000 & 1000 & 79 & 51 & 367 & 4 \\ \hline
-			1100 & 1100 & 84 & 56 & 409 & 4 \\ \hline
-			1200 & 1200 & 86 & 56 & 442 & 4 \\ \hline
-			1300 & 1300 & 89 & 59 & 466 & 4 \\ \hline
-			1400 & 1400 & 90 & 60 & 510 & 4 \\ \hline
-			1500 & 1500 & 97 & 63 & 541 & 4 \\ \hline
-			1600 & 1600 & 100 & 66 & 573 & 4 \\ \hline
-			1700 & 1700 & 102 & 67 & 624 & 4 \\ \hline
-			1800 & 1800 & 104 & 69 & 660 & 4 \\ \hline
-			1900 & 1900 & 109 & 71 & 664 & 4 \\ \hline
-			2000 & 2000 & 113 & 73 & 740 & 4 \\ \hline
-		\end{tabular}
+		  	100 & 100 ($\pm$0) & 29 ($\pm$13) & 20 ($\pm$8) & 46 ($\pm$23) & 4 ($\pm$1) \\ \hline
+			200 & 200 ($\pm$0) & 39 ($\pm$17) & 26 ($\pm$11) & 82 ($\pm$46) & 4 ($\pm$1) \\ \hline
+			300 & 300 ($\pm$0) & 46 ($\pm$21) & 30 ($\pm$13) & 117 ($\pm$69) & 4 ($\pm$1) \\ \hline
+			400 & 400 ($\pm$0) & 53 ($\pm$25) & 35 ($\pm$15) & 160 ($\pm$94) & 4 ($\pm$1) \\ \hline
+			500 & 500 ($\pm$0) & 57 ($\pm$27) & 40 ($\pm$17) & 189 ($\pm$119) & 4 ($\pm$1) \\ \hline
+			600 & 600 ($\pm$0) & 63 ($\pm$29) & 42 ($\pm$19) & 228 ($\pm$144) & 4 ($\pm$1) \\ \hline
+			700 & 700 ($\pm$0) & 68 ($\pm$32) & 44 ($\pm$19) & 263 ($\pm$162) & 4 ($\pm$1) \\ \hline
+			800 & 800 ($\pm$0) & 73 ($\pm$33) & 46 ($\pm$21) & 303 ($\pm$190) & 4 ($\pm$1) \\ \hline
+			900 & 900 ($\pm$0) & 78 ($\pm$36) & 50 ($\pm$22) & 341 ($\pm$213) & 4 ($\pm$1) \\ \hline
+			1000 & 1000 ($\pm$0) & 79 ($\pm$37) & 51 ($\pm$23) & 367 ($\pm$232) & 4 ($\pm$1) \\ \hline
+			1100 & 1100 ($\pm$0) & 84 ($\pm$38) & 56 ($\pm$24) & 409 ($\pm$264) & 4 ($\pm$1) \\ \hline
+			1200 & 1200 ($\pm$0) & 86 ($\pm$40) & 56 ($\pm$26) & 442 ($\pm$277) & 4 ($\pm$1) \\ \hline
+			1300 & 1300 ($\pm$0) & 89 ($\pm$43) & 59 ($\pm$27) & 466 ($\pm$301) & 4 ($\pm$1) \\ \hline
+			1400 & 1400 ($\pm$0) & 90 ($\pm$43) & 60 ($\pm$27) & 510 ($\pm$339) & 4 ($\pm$1) \\ \hline
+			1500 & 1500 ($\pm$0) & 97 ($\pm$47) & 63 ($\pm$27) & 541 ($\pm$350) & 4 ($\pm$1) \\ \hline
+			1600 & 1600 ($\pm$0) & 100 ($\pm$46) & 66 ($\pm$29) & 573 ($\pm$374) & 4 ($\pm$1) \\ \hline
+			1700 & 1700 ($\pm$0) & 102 ($\pm$48) & 67 ($\pm$29) & 624 ($\pm$401) & 4 ($\pm$1) \\ \hline
+			1800 & 1800 ($\pm$0) & 104 ($\pm$49) & 69 ($\pm$31) & 660 ($\pm$429) & 4 ($\pm$1) \\ \hline
+			1900 & 1900 ($\pm$0) & 109 ($\pm$52) & 71 ($\pm$32) & 664 ($\pm$442) & 4 ($\pm$1) \\ \hline
+			2000 & 2000 ($\pm$0) & 113 ($\pm$52) & 73 ($\pm$33) & 740 ($\pm$487) & 4 ($\pm$1) \\ \hline
+		\end{tabular}}
 	\end{center}
-	\caption{The average calls of the distance function $D$ during query processing depending on the size of the test
+	\caption{The average calls of the distance function $d$ during query processing depending on the size of the test
 		data set $S$.}
-	\label{fig:queryprocessing:tabular}
-\end{figure}
+	\label{tab:queryprocessing}
+\end{table}
 
-\begin{figure}
+\begin{figure}[H]
 	\begin{center}
 		\begin{tikzpicture}
-			\begin{axis}[
-				ymin=0,
-				xmin=0,
-				xmax=2000,
-				xlabel=size of test data set $S$,
-				ylabel=average calls of distance function $D$,
-				legend pos=outer north east]
-				\addplot table {data/queryprocessing/fullsearch.csv};
-	            \addlegendentry{Full Search}
-	            \addplot table {data/queryprocessing/orchards.csv};
+			\begin{groupplot}[group style={group size=2 by 3},height=6cm,width=6cm, legend pos=north west, ymin=0, xmin=0]
+				\nextgroupplot
+				\addplot+[error bars/.cd, y dir=both,y explicit]
+					coordinates {
+						(100,29)	+- (13,13)
+						(200,39) 	+- (17,17)
+						(300,46) 	+- (21,21)
+						(400,53) 	+- (25,25)
+						(500,57)	+- (27,27)
+						(600,63)	+- (29,29)
+						(700,68) 	+- (32,32)
+						(800,73) 	+- (33,33)
+						(900,78) 	+- (36,36)
+						(1000,79)	+- (37,37)
+						(1100,84)	+- (38,38)
+						(1200,86) 	+- (40,40)
+						(1300,89) 	+- (43,43)
+						(1400,90) 	+- (43,43)
+						(1500,97)	+- (47,47)
+						(1600,100)	+- (46,46)
+						(1700,102) 	+- (48,48)
+						(1800,104) 	+- (49,49)
+						(1900,109) 	+- (52,52)
+						(2000,113)	+- (52,52)
+						};
 				\addlegendentry{Orchard}
-				\addplot table {data/queryprocessing/orchardsmb.csv};
+				\nextgroupplot
+				\addplot+[error bars/.cd, y dir=both,y explicit]
+					coordinates {
+						(100,20)	+- (8,8)
+						(200,26) 	+- (11,11)
+						(300,30) 	+- (13,13)
+						(400,35) 	+- (15,15)
+						(500,40)	+- (17,17)
+						(600,42)	+- (19,19)
+						(700,44) 	+- (19,19)
+						(800,46) 	+- (21,21)
+						(900,50) 	+- (22,22)
+						(1000,51)	+- (23,23)
+						(1100,56)	+- (24,24)
+						(1200,56) 	+- (26,26)
+						(1300,59) 	+- (27,27)
+						(1400,60) 	+- (27,27)
+						(1500,63)	+- (27,27)
+						(1600,66)	+- (29,29)
+						(1700,67) 	+- (29,29)
+						(1800,69) 	+- (31,31)
+						(1900,71) 	+- (32,32)
+						(2000,73)	+- (33,33)
+						};
 				\addlegendentry{Orchard MarkBits}
-	            \addplot table {data/queryprocessing/annulus.csv};
+				\nextgroupplot
+				\addplot+[error bars/.cd, y dir=both,y explicit]
+					coordinates {
+						(100,46)	+- (23,23)
+						(200,82) 	+- (46,46)
+						(300,117) 	+- (69,69)
+						(400,160) 	+- (94,94)
+						(500,189)	+- (119,119)
+						(600,228)	+- (144,144)
+						(700,263) 	+- (162,162)
+						(800,303) 	+- (190,190)
+						(900,341) 	+- (213,213)
+						(1000,367)	+- (232,232)
+						(1100,409)	+- (264,264)
+						(1200,442) 	+- (277,277)
+						(1300,466) 	+- (301,301)
+						(1400,510) 	+- (339,339)
+						(1500,541)	+- (350,350)
+						(1600,573)	+- (374,374)
+						(1700,624) 	+- (401,401)
+						(1800,660) 	+- (429,429)
+						(1900,664) 	+- (442,442)
+						(2000,740)	+- (487,487)
+						};
 				\addlegendentry{Annulus}
-	            \addplot table {data/queryprocessing/aesa.csv};
+				\nextgroupplot
+				\addplot+[error bars/.cd, y dir=both,y explicit]
+					coordinates {
+						(100,4)	+- (1,1)
+						(200,4) +- (1,1)
+						(300,4) +- (1,1)
+						(400,4) +- (1,1)
+						(500,4)	+- (1,1)
+						(600,4)	+- (1,1)
+						(700,4)	+- (1,1)
+						(800,4) +- (1,1)
+						(900,4) +- (1,1)
+						(1000,4)	+- (1,1)
+						(1100,4)	+- (1,1)
+						(1200,4) 	+- (1,1)
+						(1300,4) 	+- (1,1)
+						(1400,4) 	+- (1,1)
+						(1500,4)	+- (1,1)
+						(1600,4)	+- (1,1)
+						(1700,4) 	+- (1,1)
+						(1800,4) 	+- (1,1)
+						(1900,4) 	+- (1,1)
+						(2000,4)	+- (1,1)
+						};
 				\addlegendentry{AESA}
-			\end{axis}
+			\end{groupplot}
 		\end{tikzpicture}
 	\end{center}
-	\caption{The average calls of the distance function $D$ during query processing depending on the size of the test
-		data set $S$ visualized with graphs.}
-	\label{fig:queryprocessing:graph}
-\end{figure}
-
-\paragraph{Standard deviation}
-
-Some of the algorithms needed more and more tries to stabilize the average result of the query processing.
-Figure~\ref{fig:standarddeviation:tabular} and figure~\ref{fig:standarddeviation:graph} show the standard deviation of
-the results for every algorithm depending on the size of set $S$.
-
-\begin{figure}
-	\begin{center}
-		\begin{tabular}{| l | c | c | c | c | c |}
-			\hline
-		  	& Full Search & Orchard & Orchard MarkBits & Annulus & AESA \\ \hline
-		  	100 & 0 & 13 & 8 & 23 & 1 \\ \hline
-			200 & 0 & 17 & 11 & 46 & 1 \\ \hline
-			300 & 0 & 21 & 13 & 69 & 1 \\ \hline
-			400 & 0 & 25 & 15 & 94 & 1 \\ \hline
-			500 & 0 & 27 & 17 & 119 & 1 \\ \hline
-			600 & 0 & 29 & 19 & 144 & 1 \\ \hline
-			700 & 0 & 32 & 19 & 162 & 1 \\ \hline
-			800 & 0 & 33 & 21 & 190 & 1 \\ \hline
-			900 & 0 & 36 & 22 & 213 & 1 \\ \hline
-			1000 & 0 & 37 & 23 & 232 & 1 \\ \hline
-			1100 & 0 & 38 & 24 & 264 & 1 \\ \hline
-			1200 & 0 & 40 & 26 & 277 & 1 \\ \hline
-			1300 & 0 & 43 & 27 & 301 & 1 \\ \hline
-			1400 & 0 & 43 & 27 & 339 & 1 \\ \hline
-			1500 & 0 & 47 & 27 & 350 & 1 \\ \hline
-			1600 & 0 & 46 & 29 & 374 & 1 \\ \hline
-			1700 & 0 & 48 & 29 & 401 & 1 \\ \hline
-			1800 & 0 & 49 & 31 & 429 & 1 \\ \hline
-			1900 & 0 & 52 & 32 & 442 & 1 \\ \hline
-			2000 & 0 & 52 & 33 & 487 & 1 \\ \hline
-		\end{tabular}
-	\end{center}
-	\caption{The standard deviation of the calls of the distance function $D$ during query processing depending on the
-		size of the test data set $S$.}
-	\label{fig:standarddeviation:tabular}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\begin{tikzpicture}
-			\begin{axis}[
-				ymin=0,
-				xmin=0,
-				xmax=2000,
-				xlabel=size of test data set $S$,
-				ylabel=standard deviation of calls of distance function $D$,
-				legend pos=outer north east]
-				\addplot table {data/standarddeviation/fullsearch.csv};
-	            \addlegendentry{Full Search}
-	            \addplot table {data/standarddeviation/orchards.csv};
-	            \addlegendentry{Orchard}
-				\addplot table {data/standarddeviation/orchardsmb.csv};
-				\addlegendentry{Orchard MarkBits}
-	            \addplot table {data/standarddeviation/annulus.csv};
-	            \addlegendentry{Annulus}
-	            \addplot table {data/standarddeviation/aesa.csv};
-	            \addlegendentry{AESA}
-			\end{axis}
-		\end{tikzpicture}
-	\end{center}
-	\caption{The standard deviation of the calls of the distance function $D$ during query processing depending on the
-		size of the test data set $S$ visualized with graphs.}
-	\label{fig:standarddeviation:graph}
+	\caption{The average amount of distance function calls depending on the size of set $S$ for Orchards Algorithm
+		with and without MarkBits, Annulus Method and AESA. The error bars are representing the standard deviation
+		of the amount of distance function calls.}
+	\label{fig:queryprocessing}
 \end{figure}
@@
 
-The LAESA algorithm and Metric Trees are missing in the benchmarks above. Both approaches are promising and their
-results compared to algorithms of this paper would be interesting.
+The LAESA\cite{Vidal} algorithm and Metric Trees\cite{Clarkson} are missing in the benchmarks above. These two
+algorithms are not parameter free and a optimal implementation for the given domain is not obvious. But both approaches
+are promising and their results compared to algorithms of this paper would be interesting.
 
 \begin{thebibliography}{4}
-	\bibitem{url} Kenneth L. Clarkson, "Nearest-Neighbor Searching and Metric Space Dimensions" (October 2005), \url{http://kenclarkson.org/nn_survey/p.pdf}
+	\bibitem{Clarkson} Clarkson, Kenneth L. "Nearest-neighbor searching and metric space dimensions." Nearest-neighbor
+		methods for learning and vision: theory and practice (2006): 15-59.
+	\bibitem{Orchard} Orchard, Michael T. "A fast nearest-neighbor search algorithm." Acoustics, Speech, and Signal
+		Processing, 1991. ICASSP-91., 1991 International Conference on. IEEE, 1991.
+	\bibitem{Ruiz} Ruiz, Enrique Vidal. "An algorithm for finding nearest neighbours in (approximately) constant average
+		time." Pattern Recognition Letters 4.3 (1986): 145-157.
+	\bibitem{Vidal} Micó, María Luisa, José Oncina, and Enrique Vidal. "A new version of the nearest-neighbour
+		approximating and eliminating search algorithm (AESA) with linear preprocessing time and memory requirements."
+		Pattern Recognition Letters 15.1 (1994): 9-17.
 \end{thebibliography}

### 2016-06-22 paper/paper.tex
translate pres

@@
 Lecturer: Stefan Fricke\\\vspace{2\baselineskip}
-May 2016\\
+June 2016\\
 Supervisor: Stephan Spiegel\\\vspace{1\baselineskip}}}}
@@
 
-\author{Gordon Lesti\\313249\\Course of studies: Bachelor of Computer Science\\gordon.lesti@campus.tu-berlin.de\\\vspace{5\baselineskip}}
+\author{Gordon Lesti\\Course of studies: Bachelor of Computer Science\\gordon.lesti@campus.tu-berlin.de\\\vspace{5\baselineskip}}
 

### 2016-06-22 presentation/presentation.tex
started annulus
translate pres

--- 2015-07-16 presentation.tex
@@
-\documentclass{beamer}
+\documentclass[handout]{beamer}
 
@@
 \author{Gordon Lesti}
-\date{17.07.2015}
+\date{July 17, 2015}
 
 \frame{\titlepage}
-\frame{\frametitle{Inhaltsverzeichnis}\tableofcontents}
-
-\section{Einleitung}
+\frame{\frametitle{Structure}\tableofcontents}
+
+\section{Introduction}
 
@@
 \begin{frame}
- \frametitle{Nearest-Neighbor Searching}
- \begin{block}{Gegeben}
-   \begin{itemize}
-    \item Menge $\mathbb{U}$
-    \pause
-    \item Abstandsmaß $d$ auf $\mathbb{U}$, mit $d: \mathbb{U} \times \mathbb{U} \to \mathbb{R}$
-    \pause
-    \item Menge $S \subset \mathbb{U}$ der Größe $n$
-    \pause
-    \item Anfragepunkt $q \in \mathbb{U}$
-  \end{itemize}
- \end{block}
- \pause
- \begin{block}{Gesucht}
-    \begin{itemize}
-     \item $a \in S$, mit $d(q, a) \le d(q, x)$ f\"ur alle $x \in S$
-    \end{itemize}
- \end{block}
-\end{frame}
-
-\subsection{Anwendung}
+ \frametitle{Nearest-Neighbour Searching}
+ \begin{block}{Input}
+   \begin{itemize}
+    \item Set $\mathbb{U}$
+    \pause
+    \item Distance function $d$ on $\mathbb{U}$, with $d: \mathbb{U} \times \mathbb{U} \to \mathbb{R}$
+    \pause
+    \item Set $S \subset \mathbb{U}$ of size $n$
+    \pause
+    \item Query item $q \in \mathbb{U}$
+  \end{itemize}
+ \end{block}
+ \pause
+ \begin{block}{Output}
+    \begin{itemize}
+     \item Item $a \in S$, with $d(q, a) \le d(q, x)$ for all $x \in S$
+    \end{itemize}
+ \end{block}
+\end{frame}
+
+\subsection{Use}
 \begin{frame}
- \frametitle{Anwendung}
- \begin{itemize}
- \item density estimation
- \item pattern recognition
- \item object recognition
- \item data clustering
- \item function approximation
- \item vector quantization
-\end{itemize}
-\end{frame}
-
-\section{L\"osungen}
-
-\subsection{Vollsuche}
+ \frametitle{Use}
+ \begin{itemize}
+ \item Pattern recognition
+ \item Statistical classification
+ \item Image editing
+ \item Coding theory
+ \item Data compression
+ \item Recommender system
+ \item $\dots$
+\end{itemize}
+\end{frame}
+
+\section{Solutions}
+
+\subsection{Full Search}
 \begin{frame}
- \frametitle{Vollsuche}
- \begin{itemize}
-  \item Berechne $d(q, x)$ f\"ur alle $x \in S$
-  \pause
-  \item W\"ahle $a \in S$, mit $d(q, a) \le d(q, x)$ f\"ur alle $x \in S$
+ \frametitle{Full Search}
+ \begin{itemize}
+  \item Calculate $d(q, x)$ for all $x \in S$
+  \pause
+  \item Return $a \in S$, with $d(q, a) \le d(q, x)$ for all $x \in S$
  \end{itemize}
@@
 % Beispiel1 Datenpunkte
-\begin{frame}{Vollsuche}{Beispiel}
+\begin{frame}<handout:0>{Full Search}{Example}
  \begin{columns}[T]
@@
     $\mathbb{U} = \mathbb{R}^2$
-    \begin{block}{Datenpunkte}
+    \begin{block}{Items}
       $x_1 = (3, 3)$\\
@@
 % Beispiel1 Anfragepunkt
-\begin{frame}{Vollsuche}{Beispiel}
+\begin{frame}{Full Search}{Example}
  \begin{columns}[T]
@@
     \end{block}
-    \begin{block}{Anfragepunkt}
+    \begin{block}{Query item}
       $q = (2, 1)$
@@
 % Beispiel1 Abstand x1
-\begin{frame}{Vollsuche}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{block}{Ergebnis}
+\begin{frame}<handout:0>{Full Search}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{block}{Result}
       $d(q, x_1) \approx 2.236$
@@
 % Beispiel1 Abstand x2
-\begin{frame}{Vollsuche}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{block}{Ergebnis}
+\begin{frame}<handout:0>{Full Search}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{block}{Result}
       $d(q, x_1) \approx 2.236$\\
@@
 % Beispiel1 Abstand x3
-\begin{frame}{Vollsuche}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{block}{Ergebnis}
+\begin{frame}<handout:0>{Full Search}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{block}{Result}
       $d(q, x_1) \approx 2.236$\\
@@
 % Beispiel1 Abstand x4
-\begin{frame}{Vollsuche}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{block}{Ergebnis}
+\begin{frame}<handout:0>{Full Search}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{block}{Result}
       $d(q, x_1) \approx 2.236$\\
@@
 % Beispiel1 Abstand x5
-\begin{frame}{Vollsuche}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{block}{Ergebnis}
+\begin{frame}<handout:0>{Full Search}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{block}{Result}
       $d(q, x_1) \approx 2.236$\\
@@
 % Beispiel1 Ergebnis
-\begin{frame}{Vollsuche}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{block}{Ergebnis}
+\begin{frame}{Full Search}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{block}{Result}
       \textcolor{green}{$d(q, x_1) \approx 2.236$}\\
@@
 % Vor- und Nachteile
-\begin{frame}{Vollsuche}{Vor- und Nachteile}
- \begin{block}{Vorteile}
-  \begin{itemize}
-   \item Einfache Implementierung
-   \pause
-   \item Funktioniert auch in Nicht-Metrischen R\"aumen
-  \end{itemize}
- \end{block}
- \pause
- \begin{block}{Nachteile}
-  \begin{itemize}
-   \item Hohe Laufzeiten gerade bei großen Datenmengen und h\"oherdimensionalen R\"aumen
-  \end{itemize}
- \end{block}
-\end{frame}
-
-\begin{frame}{Metrik}
-  Sei $X$ ein Menge. Unter einer \textit{Metrik} auf $X$ versteht man eine Abbildung\\
+\begin{frame}{Full Search}{Advantages and disadvantages}
+ \begin{block}{Advantages}
+  \begin{itemize}
+   \item Easy implementation
+   \pause
+   \item Works in none metric spaces
+  \end{itemize}
+ \end{block}
+ \pause
+ \begin{block}{Disadvantages}
+  \begin{itemize}
+   \item Large runtime on big data sets and in higher multidimensional spaces
+  \end{itemize}
+ \end{block}
+\end{frame}
+
+\begin{frame}{Metric}
+  Given a set $X$. A \textit{Metric} on $X$ is a function\\
   $d:X \times X \to \mathbb{R}$, $(x, y) \mapsto d(x, y)$\\
-  mit folgenden Eigenschaften:
+  with:
  \begin{enumerate}
  \pause
-  \item $d(x, y) = 0$ genau dann, wenn $x=y$.
-  \pause
-  \item Symmetrie: F\"ur alle $x, y \in X$ gilt $d(x, y) = d(y, x)$.
-  \pause
-  \item Dreiecksungleichung: F\"ur alle $x, y, z \in X$ gilt $d(x, z) \le d(x, y) + d(y,z)$
+  \item $d(x, y) = 0$ exactly when $x=y$.
+  \pause
+  \item Symmetry: For all $x, y \in X$ is true $d(x, y) = d(y, x)$.
+  \pause
+  \item Triangle inequality: For all $x, y, z \in X$ is true $d(x, z) \le d(x, y) + d(y,z)$
  \end{enumerate}
@@
 
-\begin{frame}{Dreiecksungleichung}
+\begin{frame}{Triangle inequality}
   \begin{center}
@@
 
- \textbf{Lemma} F\"ur beliebige $q, s, p \in \mathbb{U}$, $r \in \mathbb{R}$ und $P \subset \mathbb{U}$ gilt:
+ \textbf{Lemma} For any $q, s, p \in \mathbb{U}$, $r \in \mathbb{R}$ and $P \subset \mathbb{U}$ is true:
  \begin{enumerate}
@@
 
-\subsection{Orchard’s Algorithmus}
-\begin{frame}{Orchard’s Algorithmus}
- \begin{itemize}
-  \item Erstelle Liste f\"ur alle Punkte $p \in S$ mit allen Punkten $x \in S$, aufsteigend nach ihrer Distanz
-  \pause
-  \item W\"ahle zufälligen Punkt $c \in S$ als initialen Kandidaten
-  \pause
-  \item Berechne $d(c, q)$
-  \pause
-  \item Gehe Liste von $c$ entlange
-  \pause
-  \item Wenn aktueller Punkt näher an $q$ als $c$, nimm aktuellen Punkt für $c$
-  \pause
-  \item Abbruch, wenn
-    \begin{itemize}
-      \item die Liste komplett abgelaufen ist, oder
-      \item $d(c, s) > 2 \cdot d(c, q)$ f\"ur aktuelles Element aus der Liste (Dreiecksungleichung~\ref{ineq:4})
-    \end{itemize}
-   \pause
-   \item Sonst ist $c$ nächster Nachbar
+\subsection{Orchards Algorithm}
+\begin{frame}{Orchards Algorithm}
+ \begin{itemize}
+  \item Create a list for every item $p \in S$ with all items $x \in S$, ordered ascending to the distance
+  \pause
+  \item Choose random item $c \in S$ as initial candidate
+  \pause
+  \item Calculate $d(c, q)$
+  \pause
+  \item Go along the list of $c$
+  \pause
+  \item If the current item has smaller distance to $q$ as $c$, choose current item as $c$
+  \pause
+  \item Abort, if
+    \begin{itemize}
+      \item at the end of the current list or
+      \item $d(c, s) > 2 \cdot d(c, q)$ for the current item of the list (Triangle inequality~\ref{ineq:4})
+    \end{itemize}
+   \pause
+   \item Else $c$ is nearest neighbour
  \end{itemize}
@@
 %Beispiel2
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
+\begin{frame}{Orchards Algorithm}{Example}
  \begin{columns}[T]
@@
 %Beispiel2 Abstand
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
-  \begin{block}{Abst\"ande}
+\begin{frame}{Orchards Algorithm}{Example}
+  \begin{block}{Distances}
   \begin{center}
@@
 %Beispiel2 Listen
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{block}{Listen}
+\begin{frame}{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{block}{Lists}
     $L(x_1) = \{x_2, x_4, x_5, x_3\}$\\
@@
 
-%Beispiel2 Wähle c=x_3 und s=x_4
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:=x_3$ und $s:= x_4$
+\begin{frame}<handout:0>{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:=x_3$ and $s:= x_4$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_3 und s=x_4
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:=x_3$ und $s:= x_4$
-     \item Da $7.810 \approx d(c, q) > d(s, q) \approx 2.828$, setze $c:=s$
+\begin{frame}{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:=x_3$ and $s:= x_4$
+     \item As $7.810 \approx d(c, q) > d(s, q) \approx 2.828$, set $c:=s$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_4 und s=x_2
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:=x_4$ und $s:= x_2$
+\begin{frame}<handout:0>{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:=x_4$ and $s:= x_2$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_4 und s=x_2
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:=x_4$ und $s:= x_2$
-     \item Da $2.828 \approx d(c, q) < d(s, q) \approx 3.162$, kein neues $c$
+\begin{frame}<handout:0>{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:=x_4$ and $s:= x_2$
+     \item As $2.828 \approx d(c, q) < d(s, q) \approx 3.162$, no new $c$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_4 und s=x_2
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:=x_4$ und $s:= x_2$
-     \item Da $2.828 \approx d(c, q) < d(s, q) \approx 3.162$, kein neues $c$
-     \item Da $3.162 \approx d(c, s) < 2 \cdot d(c, q) \approx 5.656$, kein Abbruch
+\begin{frame}{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:=x_4$ and $s:= x_2$
+     \item As $2.828 \approx d(c, q) < d(s, q) \approx 3.162$, no new $c$
+     \item As $3.162 \approx d(c, s) < 2 \cdot d(c, q) \approx 5.656$, no abort
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_4 und s=x_5
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:= x_5$
+\begin{frame}<handout:0>{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:= x_5$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_4 und s=x_5
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:= x_5$
-     \item Da $2.828 \approx d(c, q) < d(s, q) \approx 4.472$, kein neues $c$
+\begin{frame}<handout:0>{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:= x_5$
+     \item As $2.828 \approx d(c, q) < d(s, q) \approx 4.472$, no new $c$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_4 und s=x_5
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:= x_5$
-     \item Da $2.828 \approx d(c, q) < d(s, q) \approx 4.472$, kein neues $c$
-     \item Da $4.472 \approx d(c, s) < 2 \cdot d(c, q) \approx 5.656$, kein Abbruch
+\begin{frame}{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:= x_5$
+     \item As $2.828 \approx d(c, q) < d(s, q) \approx 4.472$, no new $c$
+     \item As $4.472 \approx d(c, s) < 2 \cdot d(c, q) \approx 5.656$, no abort
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_4 und s=x_1
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:= x_1$
+\begin{frame}<handout:0>{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:= x_1$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_4 und s=x_1
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:= x_1$
-     \item Da $2.828 \approx d(c, q) > d(s, q) \approx 2.236$, setze $c:=s$
+\begin{frame}{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:= x_1$
+     \item As $2.828 \approx d(c, q) > d(s, q) \approx 2.236$, set $c:=s$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_1 und s=x_2
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:= x_1$ und $s:=x_2$
+\begin{frame}<handout:0>{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:= x_1$ and $s:=x_2$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_1 und s=x_2
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:= x_1$ und $s:=x_2$
-     \item Da $2.236 \approx d(c, q) < d(s, q) \approx 3.162$, kein neues $c$
+\begin{frame}<handout:0>{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:= x_1$ and $s:=x_2$
+     \item As $2.236 \approx d(c, q) < d(s, q) \approx 3.162$, no new $c$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_1 und s=x_2
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:= x_1$ und $s:=x_2$
-     \item Da $2.236 \approx d(c, q) < d(s, q) \approx 3.162$, kein neues $c$
-     \item Da $4.123 \approx d(c, s) < 2 \cdot d(c, q) \approx 4.472$, kein Abbruch
+\begin{frame}{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:= x_1$ and $s:=x_2$
+     \item As $2.236 \approx d(c, q) < d(s, q) \approx 3.162$, no new $c$
+     \item As $4.123 \approx d(c, s) < 2 \cdot d(c, q) \approx 4.472$, no abort
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_1 und s=x_4
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:=x_4$
+\begin{frame}<handout:0>{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:=x_4$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_1 und s=x_4
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:=x_4$
-     \item Da $2.236 \approx d(c, q) < d(s, q) \approx 2.828$, kein neues $c$
+\begin{frame}<handout:0>{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:=x_4$
+     \item As $2.236 \approx d(c, q) < d(s, q) \approx 2.828$, no new $c$
     \end{itemize}
@@
 %Beispiel2 Wähle c=x_1 und s=x_4
-\begin{frame}{Orchard’s Algorithmus}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:=x_4$
-     \item Da $2.236 \approx d(c, q) < d(s, q) \approx 2.828$, kein neues $c$
-     \item Da $5 \approx d(c, s) > 2 \cdot d(c, q) \approx 4.472$, \textcolor{green}{Abbruch}
+\begin{frame}{Orchards Algorithm}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:=x_4$
+     \item As $2.236 \approx d(c, q) < d(s, q) \approx 2.828$, no new $c$
+     \item As $5 \approx d(c, s) > 2 \cdot d(c, q) \approx 4.472$, \textcolor{green}{abort}
     \end{itemize}
@@
 % Vor- und Nachteile
-\begin{frame}{Orchard’s Algorithmus}{Vor- und Nachteile}
- \begin{block}{Vorteile}
-  \begin{itemize}
-   \item Schneller als Vollsuche
-  \end{itemize}
- \end{block}
- \pause
- \begin{block}{Nachteile}
-  \begin{itemize}
-   \item Vorverarbeitung kostet viel Speicher und Rechenaufwand
-  \end{itemize}
- \end{block}
- \pause
- \begin{block}{Verfeinerung}
-  \begin{itemize}
-   \item Schon durchwanderte Punkte sollten übersprungen werden
-  \end{itemize}
- \end{block}
-\end{frame}
-
-\subsection{Annulus Verfahren}
-\begin{frame}{Annulus Verfahren}
- \begin{itemize}
-  \item Erstelle eine Liste für beliebigen Punkt $p^* \in S$ mit allen Punkten $x \in S$, aufsteigend nach ihrer Distanz
-  \pause
-  \item Wähle beliebigen Kandidaten $c \in S$
-  \pause
-  \item Bewege dich alternierend von $p^*$ weg und wieder hin
-  \pause
-  \item Wenn aktueller Punkt $s$ näher an $q$ als $c$, setze $c:= s$
-  \pause
-  \item Aktueller Punkt $s$ unter $c$:
-  \begin{itemize}
-   \item Wenn $d(p^*, s) < d(p^*, q) - d(c, q)$, können alle Punkte unter $s$ ignoriert werden (Dreiecksungleichung~\ref{ineq:3})
-  \end{itemize}
-  \pause
-  \item Aktueller Punkt $s$ über $c$:
-  \begin{itemize}
-   \item Wenn $d(p^*, s) > d(p*, q) + d(c, q)$, können alle Punkte über $s$ ignoriert werden (Dreiecksungleichung~\ref{ineq:3})
-  \end{itemize}
-  \pause
-  \item Wenn ganze Liste durchlaufen, ist $c$ nächster Nachbar
+\begin{frame}{Orchards Algorithm}{Advantages and disadvantages}
+ \begin{block}{Advantages}
+  \begin{itemize}
+   \item Faster as Full Search
+  \end{itemize}
+ \end{block}
+ \pause
+ \begin{block}{Disadvantages}
+  \begin{itemize}
+   \item Preprocessing needs large memory and runtime
+  \end{itemize}
+ \end{block}
+ \pause
+ \begin{block}{Improvement}
+  \begin{itemize}
+   \item Use MarkBits to ensure that no distance is calculated twice
+  \end{itemize}
+ \end{block}
+\end{frame}
+
+\subsection{Annulus Method}
+\begin{frame}{Annulus Method}
+ \begin{itemize}
+  \item Create a list for a random item $p^* \in S$ with all items $x \in S$, ordered ascending to the distance
+  \pause
+  \item Choose random item $c \in S$
+  \pause
+  \item Walk alternating away from $p^*$ and back to it in the list
+  \pause
+  \item If current item $s$ has smaller distance to $q$ as $c$, set $c:= s$
+  \pause
+  \item Current item $s$ is under $c$:
+  \begin{itemize}
+   \item If $d(p^*, s) < d(p^*, q) - d(c, q)$, ignore all items under $s$ (Triangle inequality~\ref{ineq:3})
+  \end{itemize}
+  \pause
+  \item Current item $s$ is above $c$:
+  \begin{itemize}
+   \item If $d(p^*, s) > d(p*, q) + d(c, q)$, ignore all items above $s$ (Triangle inequality~\ref{ineq:3})
+  \end{itemize}
+  \pause
+  \item $c$ is the nearest neighbour if the entire list is traversed
  \end{itemize}
@@
 %Beispiel3
-\begin{frame}{Annulus Verfahren}{Beispiel}
+\begin{frame}{Annulus Method}{Example}
  \begin{columns}[T]
@@
 %Beispiel3 Abstand
-\begin{frame}{Annulus Verfahren}{Beispiel}
-  \begin{block}{Abst\"ande}
+\begin{frame}{Annulus Method}{Example}
+  \begin{block}{Distances}
   \begin{center}
@@
 %Beispiel3 Listen
-\begin{frame}{Annulus Verfahren}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    $p^*:=x_5$ mit $d(p^*, q) \approx 4.472$
-    \begin{block}{Liste}
+\begin{frame}{Annulus Method}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    $p^*:=x_5$ with $d(p^*, q) \approx 4.472$
+    \begin{block}{List}
     $L(x_5) = \{x_5, x_4, x_1, x_2, x_3\}$\\
@@
 %Beispiel3 c:=x_2
-\begin{frame}{Annulus Verfahren}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:=x_2$ mit $d(c,q) \approx 3.162$
+\begin{frame}<handout:0>{Annulus Method}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:=x_2$ with $d(c,q) \approx 3.162$
     \end{itemize}
@@
 %Beispiel3 c:=x_2
-\begin{frame}{Annulus Verfahren}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:=x_2$ mit $d(c, q) \approx 3.162$
-     \item Setze $s:=x_3$ mit $d(s, q) \approx 7.810$
+\begin{frame}<handout:0>{Annulus Method}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:=x_2$ with $d(c, q) \approx 3.162$
+     \item Set $s:=x_3$ with $d(s, q) \approx 7.810$
     \end{itemize}
@@
 %Beispiel3 c:=x_2
-\begin{frame}{Annulus Verfahren}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:=x_2$ mit $d(c, q) \approx 3.162$
-     \item Setze $s:=x_3$ mit $d(s, q) \approx 7.810$
-     \item $8.062 \approx d(p^*, s) > d(p^*, q) + d(c,q) \approx 7.634 \Rightarrow$ alle Knoten über $x_3$ ignorieren
+\begin{frame}{Annulus Method}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:=x_2$ with $d(c, q) \approx 3.162$
+     \item Set $s:=x_3$ with $d(s, q) \approx 7.810$
+     \item $8.062 \approx d(p^*, s) > d(p^*, q) + d(c,q) \approx 7.634 \Rightarrow$ ignore items above $x_3$
     \end{itemize}
@@
 %Beispiel3 c:=x_2
-\begin{frame}{Annulus Verfahren}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:=x_1$ mit $d(s, q) \approx 2.236$
+\begin{frame}<handout:0>{Annulus Method}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:=x_1$ with $d(s, q) \approx 2.236$
     \end{itemize}
@@
 %Beispiel3 c:=x_2
-\begin{frame}{Annulus Verfahren}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:=x_1$ mit $d(s, q) \approx 2.236$
-     \item Da $d(s, q) < d(c, q)$, setze $c:=s$
+\begin{frame}{Annulus Method}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:=x_1$ with $d(s, q) \approx 2.236$
+     \item As $d(s, q) < d(c, q)$, set $c:=s$
     \end{itemize}
@@
 %Beispiel3 c:=x_1
-\begin{frame}{Annulus Verfahren}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:=x_1$ mit $d(s, q) \approx 2.236$
+\begin{frame}<handout:0>{Annulus Method}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:=x_1$ with $d(c, q) \approx 2.236$
     \end{itemize}
@@
 %Beispiel3 c:=x_1
-\begin{frame}{Annulus Verfahren}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:=x_1$ mit $d(c, q) \approx 2.236$
-     \item Setze $s:=x_4$ mit $d(s, q) \approx 2.828$
+\begin{frame}<handout:0>{Annulus Method}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:=x_1$ with $d(c, q) \approx 2.236$
+     \item Set $s:=x_4$ with $d(s, q) \approx 2.828$
     \end{itemize}
@@
 %Beispiel3 c:=x_1
-\begin{frame}{Annulus Verfahren}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $c:=x_1$ mit $d(c, q) \approx 2.236$
-     \item Setze $s:=x_4$ mit $d(s, q) \approx 2.828$
-     \item $4.472 \approx d(p^*, s) > d(p^*, q) - d(c,q) \approx 2.236 \Rightarrow$ keine Knoten ignorieren
+\begin{frame}{Annulus Method}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $c:=x_1$ with $d(c, q) \approx 2.236$
+     \item Set $s:=x_4$ with $d(s, q) \approx 2.828$
+     \item $4.472 \approx d(p^*, s) > d(p^*, q) - d(c,q) \approx 2.236 \Rightarrow$ ignore no items
     \end{itemize}
@@
 %Beispiel3 c:=x_1
-\begin{frame}{Annulus Verfahren}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:=x_5$ mit $d(s, q) \approx 4.472 < 2.236 \approx d(c, q)$
+\begin{frame}<handout:0>{Annulus Method}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:=x_5$ with $d(s, q) \approx 4.472 < 2.236 \approx d(c, q)$
     \end{itemize}
@@
 %Beispiel3 c:=x_1
-\begin{frame}{Annulus Verfahren}{Beispiel}
- \begin{columns}[T]
-  \begin{column}{.35\textwidth}
-    \begin{itemize}
-     \item Setze $s:=x_5$ mit $d(s, q) \approx 4.472 < 2.236 \approx d(c, q)$
-     \item Da Liste am Ende, $c = x_1$ nächster Nachbar von $q$
+\begin{frame}{Annulus Method}{Example}
+ \begin{columns}[T]
+  \begin{column}{.35\textwidth}
+    \begin{itemize}
+     \item Set $s:=x_5$ with $d(s, q) \approx 4.472 < 2.236 \approx d(c, q)$
+     \item End of list, $c = x_1$ nearest neighbour of $q$
     \end{itemize}
@@
 % Vor- und Nachteile
-\begin{frame}{Annulus Verfahren}{Vor- und Nachteile}
- \begin{block}{Vorteile}
-  \begin{itemize}
-   \item Schneller als Vollsuche
-   \item Weniger Speicherverbrauch als Orchard’s Algorithmus
-  \end{itemize}
- \end{block}
-\end{frame}
-
-\section{Quellen}
+\begin{frame}{Annulus Method}{Advantages and disadvantages}
+ \begin{block}{Advantages}
+  \begin{itemize}
+   \item Faster as Full Search
+   \item Less memory usage than Orchards Algorithm
+  \end{itemize}
+ \end{block}
+\end{frame}
+
+\subsection{AESA}
+\begin{frame}{AESA}{Approximating and Eliminating Search Algorithm}
+ \begin{itemize}
+  \item Create matrix with all distances $d(x, y)$, with $x, y \in S$
+  \pause
+  \item Every item is always in one status
+  \begin{itemize}
+   \item \textit{Known}, $d(x, q)$ is known
+   \pause
+   \item \textit{Unknown}, only $d_P(x, q)$ is known
+   \pause
+   \item \textit{Rejected}, $d_P(x, q)$ is bigger as smallest known distance $r$
+  \end{itemize}
+  \pause
+  \item All $x \in S$ are \textit{Unknown} and $d_P(x, q) = -\infty$
+  \pause
+  \item Repeat until all $x \in S$ \textit{Known} oder \textit{Rejected}
+  \begin{enumerate}
+   \item Choose \textit{Unknown} item $x \in S$ with smallest $d_P(x, q)$
+   \pause
+   \item Calculate $d(x,q)$, so that $x$ gets \textit{Known}
+   \pause
+   \item Refresh the smallest known distance $r$
+   \pause
+   \item Set $P:= P \cup \{x\}$, refresh $d_P(x', q)$, if $x'$ is \textit{Unknown} mark $x'$ as \textit{Rejected}, if
+    $d_P(x', q) > r$
+  \end{enumerate}
+ \end{itemize}
+\end{frame}
+
+\begin{frame}{LAESA}{\textit{Linear} Approximating and Eliminating Search Algorithm}
+ \begin{itemize}
+  \item Works with a set of \textit{pivot} items instead of a matrix
+  \pause
+  \item Works best if \textit{pivot} items are strongly separated
+ \end{itemize}
+\end{frame}
+
+\section{Outlook}
+\begin{frame}{Outlook}
+ \begin{itemize}
+  \item Metric trees
+  \item \dots
+ \end{itemize}
+\end{frame}
+
+\section{Resources}
 \begin{frame}
- \frametitle{Quellen}
+ \frametitle{Resources}
  \begin{itemize}
